### 2019-04-04 paper.tex
yay thesis!

\documentclass[12pt]{article}
\usepackage{amsmath}
\usepackage{fancyhdr}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{graphicx}
\usepackage{varioref}
\usepackage{verbatim} 
\usepackage{multicol}
\usepackage{enumerate}
\usepackage[normalem]{ulem}
%\usepackage[margin=1in]{geometry}
\usepackage{caption}
\usepackage{subcaption}
\usepackage[T1]{fontenc}
\usepackage[margin=1in]{geometry}
\usepackage{thm-restate}
\usepackage{enumitem}

%\usepackage{cite}
\usepackage{cite}

\usepackage{mathrsfs}

\usepackage{url}\urlstyle{same}
\usepackage{xspace}
\usepackage{thm-restate}

% Nicer font
\usepackage{mathpazo}

% Microtype
\usepackage{microtype}

% TikZ
\usepackage{tikz}
\usetikzlibrary{calc}
\usetikzlibrary{decorations.pathmorphing}
\usetikzlibrary{decorations.markings}
\usetikzlibrary{graphs,graphs.standard,quotes}

% Support eps figures
\usepackage{epstopdf}

% Hypertext package
\usepackage[colorlinks = true]{hyperref}
% Title and authors
%\hypersetup{
%  pdftitle = {},
%  pdfauthor = {}
%}
% Color definitions
\usepackage{xcolor}
\definecolor{darkred}  {rgb}{0.5,0,0}
\definecolor{darkblue} {rgb}{0,0,0.5}
\definecolor{darkgreen}{rgb}{0,0.5,0}
% Color links
\hypersetup{
  urlcolor   = blue,         % color of external links
  linkcolor  = darkblue,     % color of internal links
  citecolor  = darkgreen,    % color of links to bibliography
  filecolor  = darkred       % color of file links
}

% Clever references
\usepackage{cleveref}%[nameinlink]
\crefname{lemma}{Lemma}{Lemmas}
\crefname{proposition}{Proposition}{Propositions}
\crefname{definition}{Definition}{Definitions}
\crefname{theorem}{Theorem}{Theorems}
\crefname{conjecture}{Conjecture}{Conjectures}
\crefname{corollary}{Corollary}{Corollaries}
\crefname{section}{Section}{Sections}
%\crefname{property}{Property}{Properties}
\crefname{appendix}{Appendix}{Appendices}
\crefname{figure}{Fig.}{Figs.}
\crefname{equation}{Eq.}{Eqs.}
\crefname{table}{Table}{Tables}
\crefname{claim}{Claim}{Claims}
%\crefname{item}{Property}{Properties}

%%%%%%%%%%%%%%%%%%%%%%%%%
%  N E W T H E O R E M  %
%%%%%%%%%%%%%%%%%%%%%%%%%

\newtheorem{theorem}{Theorem}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{conjecture}[theorem]{Conjecture}
\newtheorem{property}[theorem]{Property}
\newtheorem*{conjecture*}{Conjecture}
\newtheorem*{problem}{Problem}
\newtheorem{claim}[theorem]{Claim}
\theoremstyle{definition}
\newtheorem*{remark}{Remark}
\newtheorem*{example}{Example}

\DeclareMathOperator{\E}{\mathrm{E}}		% expected value
\DeclareMathOperator{\pr}{\mathrm{P}}		% expected value
\DeclareMathOperator{\cov}{t_\textrm{cov}}  % cover time
\DeclareMathOperator{\hit}{t_{\textrm{hit}}}% hitting time

\newcommand{\todo}[1]{{\color{blue}{[{\bf TODO:} #1]}}}

\begin{document}

%+Title
\title{Cover Times of Random Walks}

\author{R. Teal Witter}

\date{\today}
%\date{\today}

\maketitle
%-Title

\abstract{abstract}

\newpage
\tableofcontents

\newpage
\section{Introduction and Background}

"white screen" problem
numerous applications
many mathematical tools

\subsection{Motivation}
universal travel sequences
graph connectivity
protocol testing

\subsection{Definitions}
We consider an undirected graph $G$ without self loops or multi-edges.
Let $V(G)$ be the set of vertices and let $E(G)$ be the set of edges on $G$.
Then $n$ is the number of vertices $|V(G)|$.
%Without loss of generality, we label the vertices $\{1, 2, 3, ..., n\}$.

We say $i\sim j$ for $i$ and $j$ in the vertex set $V(G)$ if $(i,j)$ in $E(G)$.
Let $c(i,j)$ be the non-negative weight of the edge between vertices $i$ and $j$.
If the graph is unweighted then $c(i,j) = 1$ if $i \sim j$.

Define the weight of vertex $i$ 
\begin{align}
c(i) &= \sum_{j:i \sim j} c(i,j). \nonumber
\end{align}

We consider a random walk $(X_t)$ on $G$.
Call $X_t$ the vertex that the walk is on at time $t$.
The random walker begins at vertex $X_0$.
At each step, the walker at vertex $i$ moves to neighboring vertex
$j$ with probability $\frac{c(i,j)}{c(i)}$.

Let $T_{j}$ be the number of steps until the first visit to $j$.
Formally,
\begin{align}
T_{j} &= \textrm{min} \left\{t : X_t = j \right\}. \nonumber
\end{align}
Let the hitting time $\hit$ be the maximum expected time between two vertices on $G$.
Formally, 
\begin{align}
\hit &= \max_{i,j \in V(G)} \E_i[T_j]. \nonumber
\end{align}
Note that $\E_i[T_j] = \E[T_j | X_0 = i]$.
Let the cover time $\cov$ be the expected time until all vertices have been
visited by the random walk $(X_t)$.
Formally,
\begin{align}
\cov &= \E [ \max_{j \in V(G)} T_j ]. \nonumber
\end{align}

\subsection{Outline}

\section{Cover Times of Structured Graphs}

\subsection{Small Example}
Always possible to calculate exactly but the number of equations grows exponentially
Special graph \cite{BH94} full cover time from vertex 1
In symmetric cases, we can calculate it
In other cases, we have to rely on bounds

\subsection{Complete Graph}
We call the graph with $n$ vertices and ${n \choose 2}$ edges the complete graph.

\begin{figure}[ht]
	\centering
	\begin{tikzpicture}[scale=.1]
	  \graph[circular placement, radius=3cm,
	         empty nodes, nodes={circle,draw,fill=black,scale=.7}] {
	    \foreach \x in {a,...,f} {
	      \foreach \y in {\x,...,f} {
	        \x -- \y;
	      };
	    };
	  };
	  \foreach \x [count=\idx from 0] in {a,...,f} {
	    \pgfmathparse{90 + \idx * (360 / 6)}
	    \node at (\pgfmathresult:4.4cm) {};
	  };
	\end{tikzpicture}
    \caption{The complete graph with six vertices (and ten edges).}\label{fig:complete}	
\end{figure}

Our goal is to find the expected number of steps until we have visited all
$n$ vertices in the complete graph.
Observe that the random walk can start at any vertex without loss of generality
because the graph is symmetric.
The strategy is to write the cover time $\cov$ in terms of the expected
value of more simple random variables.
Let $X_i$ be the random variable that represents the number of steps to go
from $i-1$ to $i$ unique vertices (excluding the current vertex).

We write the cover time in terms of $X_i$ and use linearity of expectation.
\begin{align}
\cov&= \E[X_1+X_2+X_3+...+X_{n+1}] = \sum_{i=1}^n \E[X_i] \nonumber
\end{align}

The random variable $X_i$ takes value $k$ when $k-1$ steps lead us to
already visited vertices and the $k^{th}$ step is to previously unvisited vertex.
It follows that $X_i$ is geometric with distribution
\begin{align}
\pr(X_i = k) = (1-p_i)^{k-1}p_i, \nonumber
\end{align}
where $p_i$ is the probability of moving to a previously unvisited vertex.
Then $\E[X_i] = \frac{1}{p_i}$. We now find $p_i$:
the probability that we go to a previously unvisited vertex is $\frac{n-i}{n-1}$.
This is because there are $n-i$ unvisited vertices and a total of $n-1$ adjacent vertices.
It follows that $\E[X_i] = \frac{n-1}{n-i}$.
Then
\begin{align}
\cov&=   \sum_{i=1}^n \frac{n-1}{n-i} \nonumber \\
&=  (n-1) \left(\frac{1}{n-1}+\frac{1}{n-2}+...+1\right). \nonumber
\end{align}

A natural interpretation of the cover time on a complete graph is 
the so-called coupon collecting problem.
There are $r$ different coupons that are randomly packaged in cereal boxes.
An avid fan buys a box of cereal every day.
We want to know how many days until the fan has collected each coupon.
The strategy is to think of every coupon as a vertex on the complete graph.
We then move from vertex to vertex with uniform probability.
The difference between the coupon collecting problem and the complete graph
is that we now have self-edges.
Before, we had to leave our current vertex at each step.
Now, we can stay in the same vertex (provided our collector found the same coupon
two days in a row).
We apply our approach to the complete graph and substitute the $r$ possible coupons
we can find for the $n-1$ vertices we could move to.
Then
\begin{align}
\cov&=  r \left(\frac{1}{r}+\frac{1}{r-1}+...+1\right). \nonumber
\end{align}

Another more subtle application of the cover time on a complete graph
is the cover time on an $n$-star.

\begin{figure}[ht]
	\centering
	\begin{tikzpicture}[scale = 2]
	    \tikzstyle{vertex}=[draw, circle,fill=black, scale=.7]
	    \tikzstyle{edge}=[draw,line width = .5pt,-,black!100]
	    \node[vertex] (0) at (0,0) {};
	    \node[vertex] (1) at (1,0) {};
	    \node[vertex] (2) at (.7,-.7) {};
	    \node[vertex] (3) at (0,-1) {};
	    \node[vertex] (4) at (-.7,-.7) {};
	    \node[vertex] (5) at (-1,0) {};
	    \node[vertex] (6) at (-.7,.7) {};
	    \node[vertex] (7) at (0,1) {};
	    \node[vertex] (8) at (.7,.7) {};
	    \draw[edge] (1) -- (0);
	    \draw[edge] (2) -- (0);
	    \draw[edge] (3) -- (0);
	    \draw[edge] (4) -- (0);
	    \draw[edge] (5) -- (0);
	    \draw[edge] (6) -- (0);
	    \draw[edge] (7) -- (0);
	    \draw[edge] (8) -- (0);
	\end{tikzpicture}
	\caption{The nine-star.}\label{fig:n-star}
\end{figure}

An $n$-star is a graph with one central vertex and $n-1$ adjacent vertices each with a single
edge to the center.
A random walk begins at the central vertex and moves with uniform probability to
one of the $n-1$ adjacent vertices.
Whereas in the complete graph and coupon collecting problems we 
restarted in one step, a random walk on the $n$-star probabilistically restarts
in two steps: one step to each leaf and one step back.
We apply our approach to the complete graph and conclude that

\begin{align}
\cov&= 2(n-1) \left(\frac{1}{n-1}+\frac{1}{n-2}+...+1\right). \nonumber
\end{align}

\subsection{Simple Cycle}

A simple cycle is a connected graph where
each vertex has an edge to exactly two other vertices.
(\cref{fig:cycle} is an example.)

Our goal is to determine the cover time of a simple cycle.
However, we begin by considering the cover time of a subset
of the integers on the number line from $0$ to $N$.
We then use our analysis to build our way up to a simple cycle.

Consider a random walk on the finite linear graph.
(For the finite linear graph in \cref{fig:line}, note that $n=N+1$.)
From $X_t=i$, we move with equal probability to $i+1$
and $i-1$ until we reach either $0$ or $N$.

\begin{figure}[ht]
	\centering
	\begin{tikzpicture}
  		\pgfmathsetmacro{\N}{5}
		\tikzstyle{vertex}=[draw, circle,fill=black, scale=.7]
	    \tikzstyle{edge}=[draw,line width = .5pt,-,black!100]
		\tikzstyle{label}=[scale=.7]
		\draw[edge] (-\N,0) -- (\N,0);

		\node[label] (0) at (-\N,.5) {$0$};	
		\node[label] (N) at (\N,.5) {$N$};	
		\node[label] (0) at (-\N/5,.5) {$i$};

		\draw (-\N/5,0.1) -- (-\N/5,-0.1);
		\draw (\N,0.1) -- (\N,-0.1);
		\draw (-\N,0.1) -- (-\N,-0.1);

		\draw[edge] (-\N,0) -- (\N,0);
	\end{tikzpicture}
	\caption{A finite linear graph with a vertex at each integer from $0$ to $N$.}\label{fig:line}
\end{figure}

Call $e_i$ the expected number of steps until we reach either
end of our random walk from state $i$.
Our strategy is to write and solve a recurrence relation that
uses what we know about the random walk.
If $i=0,N$, we are already at the end point and $e_i=0$.
Otherwise, we take a step.
There's a half probability our step is to the right and
a half probability it is to the left.

\begin{align}
e_i &= 1 + \frac{1}{2} \left(e_{i+1}\right) + \frac{1}{2}\left(e_{i-1}\right) \nonumber \\
2 e_i &= 2 + e_{i+1} - e_{i-1} \nonumber \\
\left(e_{i+1} - e_i\right) &=\left( e_i - e_{i-1}\right) - 2 \nonumber
\end{align}

While the final line may look unnecessarily complicated,
notice that the structure of the equality lends itself to telescoping.

To solve the telescoping equations, notice that the walk is symmetric:
we could flip the walk over the vertical axis without changing $e_i$.
This makes sense because our intuition tells us that the only 
identifying feature of $i$ is its respective distances to the endpoints.
The logical conclusion is that $e_i=e_{N-i}$.
In particular, we have already seen that $e_0=e_N=0$ and it
naturally follows that $e_1=e_{N_1}$.
We use these observations to find $e_1$.

\begin{align}
\left(e_{2} - e_1\right) &= \left(e_1 - e_{0}\right) - 2 \nonumber \\
\left(e_{3} - e_2\right) &= \left(e_2 - e_{1}\right) - 2 = \left(e_1 - e_{0}\right) - 4\nonumber \\
\left(e_{4} - e_3\right) &= \left(e_3 - e_{2}\right) - 2 = \left(e_1 - e_{0}\right) - 6\nonumber \\
&\;\;\vdots \nonumber\\
\left(e_N - e_{N-1}\right) &= \left(e_1 - e_0\right) - 2 (N-1) \nonumber \\
\left(0 - e_1\right) &= \left(e_1 - 0\right) - 2 (N-1) \nonumber \\
e_1 &= N-1. \nonumber
\end{align}

(Note that the vertical dots denote inductive reasoning.)
We now know $e_1$.
However, our goal is to find the expected number of steps
from an arbitrary point $i$.
We use $e_1$ to find the general solution.

\begin{align}
e_2  &= e_1 + (e_1 - e_0) - 2 = 2 (N - 2) \nonumber\\
e_3  &= e_2 + (e_2 - e_1) - 2 = 2 \left[2 (N-2) \right] - (N-1) -2 = 3 (N - 3) \nonumber\\
&\;\;\vdots \nonumber\\
e_i &= i (N-i) \label{eq:line}
\end{align}

\cref{thm:line} follows from \cref{eq:line} and the observation that any
linear finite graph can be shifted so that the left end point
is at $0$ and the right end point is at $N$.

\begin{theorem}
The expected number of steps from a state to either end of a finite linear graph
is the product of the distances from that state to each end point.
\label{thm:line}
\end{theorem}

We now return to cover times.
Consider a random walk on a simple cycle as in \cref{fig:cycle}.
(Note that the starting vertex is arbitrary since the graph is symmetric.)
Think of $(X_t)$ as the walk on the number line (between $-n$ and $n$)
where $X_0 = 0$.
The cover time $\cov$ of the simple cycle is the expected number of steps 
until we visit $n$ distinct integers.

\begin{figure}[ht]
	\centering
	\begin{tikzpicture}
	\draw[line width=.5pt] circle (2cm);
	\foreach \a in {1,2,...,11} {
		\draw (\a*360/11: 2cm) node [circle, fill=black, scale=.7] (\a) {};
	}
	\end{tikzpicture}
	\caption{A cycle graph with $n=11$ vertices.}\label{fig:cycle}
\end{figure}

Let $\{a, a+1, \dots, b-1, b\}$ 
denote the set of vertices we have visited.
Since the walk is on a line, we can write $[a,b]$ for the range
of the walk where $a$ is the smallest 
and $b$ is the largest vertex we have visited.
Notice that if $a \leq -n$ or $b \geq n$, we have covered all $n$ vertices
on the simple cycle and conclude the random walk.

In a slight abuse of notation, let $T_k$ be the 
number of steps until we reach $k$ distinct vertices.
Formally, $T_k = \min{t: b-a+1 = k}$.
Then by telescoping,
\begin{align}
\cov &= \E[T_n] = \E[(T_2 - T_1) + (T_3 - T_2) + \dots + 
(T_k - T_{k-1}) + \dots + (T_n - T_{n-1})] \nonumber
\end{align}

At time $T_{k}$, we are either at integer $a$ or $b$.
Then $\E[T_{k+1}-T_{k}]$ is the expected time until we reach $a-1$ or $b+1$.
Notice that we can shift our end points to 0 and $b+1-(a-1) = b-a + 2 = k+1$.
The expected number of steps to either $a-1$ or $b+1$
is $1\dot (k+1-1) = k$ by \cref{thm:line}.

By linearity of expectation,
\begin{align}
\cov &=  (\E[T_2] - \E[T_1]) + \dots +
(\E[T_{k+1}] - \E[T_{k}]) + \dots + (\E[T_n] - \E[T_{n-1}]) \nonumber\\
&= 1 + 2 + \dots + k-1 + \dots + n-1  = \frac{1}{2}n(n-1). \nonumber
\end{align}

\subsection{Finite Linear Graph}
We have already seen a finite linear graph.
(For the finite linear graph in \cref{fig:line}, note that $n=N+1$).
\cref{thm:line} tells us the expected time from an arbitrary point to
one of the end points but we do not yet know the cover time.

Observe that the cover time is the earliest time that both end points 
have been visited.
We can use our earlier result to find the time to one of the end points
from an arbitrary position but we still need to find the expected time
from that end point to the other.

Consider $\E_i[T_N]$ the expected time to $N$ from vertex $i$.
We want to find $\E_0[T_N]$. By symmetry, $\E_0[T_N] = \E_N[T_0]$.

\section{Bounds}
\subsection{Matthews Method}

$\hit \leq \cov$

\begin{theorem}
Let $(X_t)$ be a random walk on a graph with $n$ vertices. Then \label{thm:matthews}
\end{theorem}
\begin{align}
\cov &\leq \hit \left(1 + \frac{1}{2} + \frac{1}{3} + ... + \frac{1}{n-1} \right). \nonumber
\end{align}

\begin{proof}
Without loss of generality, we may assume that the walk started at vertex $n$.
Let $\sigma$ be a uniform permutation of the unvisited $n-1$ vertices.
The strategy is to look for the vertices in order $\sigma$.
We call $\sigma_i$ the $i^{th}$ vertex we visit.
Let $T_k$ be the first time that vertices $\sigma_1, \sigma_2, ..., \sigma_k$
have all been visited.
For $1 \leq s \leq n-1$,
\begin{align}
\E_n[T_1 | \sigma_1 = s] = t_{n,s} \leq \hit \nonumber
\end{align}
\end{proof}

\subsection{Spanning Tree Argument}

\section{Distributional Aspects}
\subsection{Complete Graph}

\section{Electrical Networks}
\subsection{Definitions}
\subsection{Commute Times}
\subsection{Balanced Trees}

\section{Simulation}

\cite{AF14}
\cite{BH94}
\cite{Bo98}
\cite{DS84}
\cite{Du11}
\cite{Gr10}
\cite{LP17}

\newpage
\bibliography{mybib}{}
\bibliographystyle{plain}
\begin{comment}
\begin{thebibliography}{9}

\bibitem{AF14}
	Aldous, D. and J. Fill.
	2014.
	\textit{Reversible Markov Chains and Random Walks on Graphs}.

\bibitem{BH94}
	Blom, G., L. Holst and D. Sandell.
	\textit{Problems and Snapshots from the World of Probability},
	Springer Science \& Business Media, 1994.

\bibitem{Bo13}
	Bollobás, B.
	2013.
	\textit{Modern Graph Theory},
	Vol. 184,
	Springer Science \& Business Media.

\bibitem{DS84}
	Doyle, P. G. and J. L. Snell.
	1984.
	\textit{Random Walks and Electric Networks},
	Mathematical Association of America.

\bibitem{Gr10}
	Grimmett, G.
	2010.
	\textit{Probability on Graphs : Random Processes on Graphs and Lattices},
	Vol. 8,
	Cambridge University Press.

\bibitem{LP08}
	Levin, D. A. and Y. Peres.
	2017.
	\textit{Markov Chains and Mixing Times},
	Vol. 107,
	American Mathematical Society.

\end{thebibliography}
\end{comment}

\end{document}

### 2019-04-05 paper.tex
finished first section

@@
 Note that $\E_i[T_j] = \E[T_j | X_0 = i]$.
-Let the cover time $\cov$ be the expected time until all vertices have been
+Let the cover time $\cov$ be the until all vertices have been
 visited by the random walk $(X_t)$.
+We typically refer to the expected cover time $\cov$.
 Formally,
@@
 \subsection{Small Example}
-Always possible to calculate exactly but the number of equations grows exponentially
-Special graph \cite{BH94} full cover time from vertex 1
-In symmetric cases, we can calculate it
-In other cases, we have to rely on bounds
+In general, it is always possible to find the exact cover time
+of a graph using first step analysis.
+We demonstrate the strategy on a small graph suggested by \cite{BH94}.
+
+\cref{fig:example} shows our small graph and the first step analysis
+for the random walk $(X_t)$ started from the top left vertex.
+The black vertex indicates the current vertex of the random walk
+and the empty vertices indicate the visited nodes.
+
+For a graph with $n$ vertices, there are $n$ possible choices for the current
+vertex and $2^{n-1}$ possible combinations of visited and unvisited vertices
+for each one.
+Of course, some states are inaccessible.
+But even on \cref{fig:example} where we exploit symmetry,
+there are almost a prohibitive number of cases.
+It follows from our combinatorial analysis that the number of states
+grows exponentially with the number of vertices.
+
+\begin{figure}[ht]
+	\centering
+		\begin{tikzpicture} [
+            > = stealth, % arrow head style
+            shorten > = 1pt, % don't touch arrow head to node
+            %auto,
+            node distance = 3cm, % distance between nodes
+            semithick % line style
+        ]
+
+			\tikzstyle{edge}=[draw,line width = .5pt,-,black!100]
+
+			\node (m) at (-1.2,1.75) {
+				\begin{tikzpicture}[scale = 3]
+				    \tikzstyle{edge}=[draw,line width = .5pt,-,black!100]
+				    \tikzstyle{current}=[draw,circle,fill=black,scale=.5]
+				    \tikzstyle{visited}=[draw,circle,fill=white,scale=.5]
+				    \draw[edge] (0,0) -- (0,1);
+				    \draw[edge] (0,0) -- (1,0);
+				    \draw[edge] (0,1) -- (1,0);
+				    \draw[edge] (0,1) -- (1,1);
+				    \draw[edge] (1,1) -- (1,0);
+				    \node (l) at (.5, 1.1) {$\cov$};
+				    \node (bl) at (0,0) {};
+				    \node[current] (tl) at (0,1) {};
+				    \node (br) at (1,0) {};
+				    \node (tr) at (1,1) {};;
+				\end{tikzpicture}
+			};
+			\node (a) at (2,3) {
+				\begin{tikzpicture}[scale = 1]
+				    \tikzstyle{edge}=[draw,line width = .5pt,-,black!100]
+				    \tikzstyle{current}=[draw,circle,fill=black,scale=.5]
+				    \tikzstyle{visited}=[draw,circle,fill=white,scale=.5]
+				    \draw[edge] (0,0) -- (0,1);
+				    \draw[edge] (0,0) -- (1,0);
+				    \draw[edge] (0,1) -- (1,0);
+				    \draw[edge] (0,1) -- (1,1);
+				    \draw[edge] (1,1) -- (1,0);
+				    \node (l) at (.5, 1.3) {a};
+				    \node (bl) at (0,0) {};
+				    \node[visited] (tl) at (0,1) {};
+				    \node[current] (br) at (1,0) {};
+				    \node (tr) at (1,1) {};;
+				\end{tikzpicture}
+			};
+			\node (b) at (2,0) {
+				\begin{tikzpicture}[scale = 1]
+				    \tikzstyle{edge}=[draw,line width = .5pt,-,black!100]
+				    \tikzstyle{current}=[draw,circle,fill=black,scale=.5]
+				    \tikzstyle{visited}=[draw,circle,fill=white,scale=.5]
+				    \draw[edge] (0,0) -- (0,1);
+				    \draw[edge] (0,0) -- (1,0);
+				    \draw[edge] (0,1) -- (1,0);
+				    \draw[edge] (0,1) -- (1,1);
+				    \draw[edge] (1,1) -- (1,0);
+				    \node (l) at (.5, -.3) {b};
+				    \node (bl) at (0,0) {};
+				    \node[visited] (tl) at (0,1) {};
+				    \node (br) at (1,0) {};
+				    \node[current] (tr) at (1,1) {};;
+				\end{tikzpicture}
+			};
+			\node (c) at (4,3) {
+				\begin{tikzpicture}[scale = 1]
+				    \tikzstyle{edge}=[draw,line width = .5pt,-,black!100]
+				    \tikzstyle{current}=[draw,circle,fill=black,scale=.5]
+				    \tikzstyle{visited}=[draw,circle,fill=white,scale=.5]
+				    \draw[edge] (0,0) -- (0,1);
+				    \draw[edge] (0,0) -- (1,0);
+				    \draw[edge] (0,1) -- (1,0);
+				    \draw[edge] (0,1) -- (1,1);
+				    \draw[edge] (1,1) -- (1,0);
+				    \node (l) at (.5, 1.3) {c};
+				    \node (bl) at (0,0) {};
+				    \node[visited] (tl) at (0,1) {};
+				    \node[visited] (br) at (1,0) {};
+				    \node[current] (tr) at (1,1) {};;
+				\end{tikzpicture}
+			};
+			\node (d) at (4,0) {
+				\begin{tikzpicture}[scale = 1]
+				    \tikzstyle{edge}=[draw,line width = .5pt,-,black!100]
+				    \tikzstyle{current}=[draw,circle,fill=black,scale=.5]
+				    \tikzstyle{visited}=[draw,circle,fill=white,scale=.5]
+				    \draw[edge] (0,0) -- (0,1);
+				    \draw[edge] (0,0) -- (1,0);
+				    \draw[edge] (0,1) -- (1,0);
+				    \draw[edge] (0,1) -- (1,1);
+				    \draw[edge] (1,1) -- (1,0);
+				    \node (l) at (.5, -.3) {d};
+				    \node (bl) at (0,0) {};
+				    \node[current] (tl) at (0,1) {};
+				    \node (br) at (1,0) {};
+				    \node[visited] (tr) at (1,1) {};;
+				\end{tikzpicture}
+			};
+			\node (e) at (6,3) {
+				\begin{tikzpicture}[scale = 1]
+				    \tikzstyle{edge}=[draw,line width = .5pt,-,black!100]
+				    \tikzstyle{current}=[draw,circle,fill=black,scale=.5]
+				    \tikzstyle{visited}=[draw,circle,fill=white,scale=.5]
+				    \draw[edge] (0,0) -- (0,1);
+				    \draw[edge] (0,0) -- (1,0);
+				    \draw[edge] (0,1) -- (1,0);
+				    \draw[edge] (0,1) -- (1,1);
+				    \draw[edge] (1,1) -- (1,0);
+				    \node (l) at (.5, 1.3) {e};
+				    \node (bl) at (0,0) {};
+				    \node[current] (tl) at (0,1) {};
+				    \node[visited] (br) at (1,0) {};
+				    \node[visited] (tr) at (1,1) {};;
+				\end{tikzpicture}
+			};		
+			\node (f) at (6, 0) {
+				\begin{tikzpicture}[scale = 1]
+				    \tikzstyle{edge}=[draw,line width = .5pt,-,black!100]
+				    \tikzstyle{current}=[draw,circle,fill=black,scale=.5]
+				    \tikzstyle{visited}=[draw,circle,fill=white,scale=.5]
+				    \draw[edge] (0,0) -- (0,1);
+				    \draw[edge] (0,0) -- (1,0);
+				    \draw[edge] (0,1) -- (1,0);
+				    \draw[edge] (0,1) -- (1,1);
+				    \draw[edge] (1,1) -- (1,0);
+				    \node (l) at (.5, -.3) {f};
+				    \node[current] (bl) at (0,0) {};
+				    \node[visited] (tl) at (0,1) {};
+				    \node (br) at (1,0) {};
+				    \node[visited] (tr) at (1,1) {};;
+				\end{tikzpicture}
+			};
+			\node (done) at (8, 3) {
+				\begin{tikzpicture}[scale = 1]
+				    \tikzstyle{edge}=[draw,line width = .5pt,-,black!100]
+				    \tikzstyle{current}=[draw,circle,fill=black,scale=.5]
+				    \tikzstyle{visited}=[draw,circle,fill=white,scale=.5]
+				    \draw[edge] (0,0) -- (0,1);
+				    \draw[edge] (0,0) -- (1,0);
+				    \draw[edge] (0,1) -- (1,0);
+				    \draw[edge] (0,1) -- (1,1);
+				    \draw[edge] (1,1) -- (1,0);
+				    \node (l) at (.5, 1.3) {0};
+				    \node[visited] (bl) at (0,0) {};
+				    \node[visited] (tl) at (0,1) {};
+				    \node[visited] (br) at (1,0) {};
+				    \node[visited] (tr) at (1,1) {};;
+				\end{tikzpicture}
+			};
+			\node (g) at (8, 0) {
+				\begin{tikzpicture}[scale = 1]
+				    \tikzstyle{edge}=[draw,line width = .5pt,-,black!100]
+				    \tikzstyle{current}=[draw,circle,fill=black,scale=.5]
+				    \tikzstyle{visited}=[draw,circle,fill=white,scale=.5]
+				    \draw[edge] (0,0) -- (0,1);
+				    \draw[edge] (0,0) -- (1,0);
+				    \draw[edge] (0,1) -- (1,0);
+				    \draw[edge] (0,1) -- (1,1);
+				    \draw[edge] (1,1) -- (1,0);
+				    \node (l) at (.5, -.3) {g};
+				    \node[visited] (bl) at (0,0) {};
+				    \node[current] (tl) at (0,1) {};
+				    \node (br) at (1,0) {};
+				    \node[visited] (tr) at (1,1) {};;
+				\end{tikzpicture}
+			};
+			\begin{comment}
+		    \path[->] (m) edge node[above] {$\frac{1}{3}$} (a);	
+		    \path[->] (m) edge node[below] {$\frac{2}{3}$} (b); 
+		    \path[->] (a) edge[loop above] node[below] {$\frac{1}{3}$} (a);
+		    \path[->] (a) edge node[above] {$\frac{2}{3}$} (c);
+		    \path[->] (b) edge[bend left] node[below] {$\frac{1}{2}$} (d);
+		    \path[->] (b) edge node[below] {$\frac{1}{2}$} (e);
+		    \path[->] (c) edge[bend left] node[above] {$1$} (e);
+		    \path[->] (d) edge node[below] {$\frac{1}{3}$} (e);
+		    \path[->] (d) edge[bend left] node[below] {$\frac{1}{3}$} (b); 
+		    \path[->] (d) edge node[below] {$\frac{1}{3}$} (f);
+		    \path[->] (e) edge[bend left] node[above] {$\frac{1}{3}$} (c);
+		    \path[->] (e) edge[loop above] node[below] {$\frac{1}{3}$} (e);
+		    \path[->] (f) edge[bend left] node[below] {$\frac{1}{2}$} (g);
+		    \path[->] (g) edge[bend left] node[below] {$\frac{2}{3}$} (f);
+			\path[->] (e) edge node[above] {$\frac{1}{3}$} (done);
+			\path[->] (f) edge node[below] {$\frac{1}{2}$} (done);
+			\path[->] (g) edge node[right] {$\frac{1}{3}$} (done);
+			\end{comment}
+			\path[->] (m) edge (a);
+			\path[->] (m) edge (b);
+			\path[->] (a) edge[loop above] (a);
+			\path[->] (a) edge (c);
+			\path[->] (b) edge[bend left] (d);
+			\path[->] (b) edge (e);
+			\path[->] (c) edge[bend left] (e);
+			\path[->] (d) edge (e);
+			\path[->] (d) edge[bend left] (b);
+			\path[->] (d) edge (f);
+			\path[->] (e) edge[bend left] (c);
+			\path[->] (e) edge[loop above] (e);
+			\path[->] (f) edge[bend left] (g);
+			\path[->] (g) edge[bend left] (f);
+			\path[->] (e) edge (done);
+			\path[->] (f) edge (done);
+			\path[->] (g) edge (done);
+	\end{tikzpicture}
+	\caption{First step analysis applied to an asymmetric graph with $n=4$.}\label{fig:example}
+\end{figure}
+
+If we let the label of each graph in \cref{fig:example}
+denote the expected cover time from that graph, we have the following system
+of equations:
+\begin{align}
+\cov &= 1 + \frac{1}{3}\textrm{a} + \frac{2}{3}\textrm{b} \nonumber \\
+\textrm{a} &= 1 + \frac{1}{3}\textrm{a} + \frac{2}{3}\textrm{c} \nonumber \\
+\textrm{b} &= 1 + \frac{1}{2}\textrm{b} + \frac{1}{2}\textrm{e} \nonumber \\
+\textrm{c} &= 1 + 1\textrm{e} \nonumber\\
+\textrm{d} &= 1 + \frac{1}{3}\textrm{a} + \frac{1}{3}\textrm{e} + \frac{1}{3}\textrm{f} \nonumber \\
+\textrm{e} &= 1 + \frac{1}{3}\textrm{c} + \frac{1}{3}\textrm{e} + \frac{1}{3}\dot 0\nonumber \\
+\textrm{f} &= 1 + \frac{1}{2}\textrm{g} + \frac{1}{2}\dot 0\nonumber \\
+\textrm{g} &= 1 + \frac{2}{3}\textrm{f} + \frac{1}{3}\dot 0\nonumber \\
+\end{align}
+
+With a little linear algebra, we find that $\cov = \frac{43}{6}$.
+
+For large graphs, the first step analysis as an approach to finding the expected
+cover time is obviously intractable.
+The rest of this section deals with particularly symmetric graphs
+for which it is possible find a solution for an arbitrary $n$.
+However, we must rely on expected cover time bounds for the vast majority of cases.
 
@@
 
-\subsection{Simple Cycle}
+\subsection{Line Graph}
+A line graph is a set of vertices connected in a line.
+(\cref{fig:line} is an example with $n=N+1$.)
 
-A simple cycle is a connected graph where
-each vertex has an edge to exactly two other vertices.
-(\cref{fig:cycle} is an example.)
+Our goal is to determine the cover time of a line graph.
+Let $(X_t)$ be the random walk started at vertex $i$.
+Notice that a random walk will have covered all vertices
+exactly when it has visited both endpoints.
+We can use this observation to break up the cover time into the time it takes
+to reach one of the endpoints and the time it takes to reach 
+the other endpoint.
 
-Our goal is to determine the cover time of a simple cycle.
-However, we begin by considering the cover time of a subset
-of the integers on the number line from $0$ to $N$.
-We then use our analysis to build our way up to a simple cycle.
+We will begin by considering the time $(X_t)$ takes to
+visit either one of the endpoints from vertex $i$.
 
-Consider a random walk on the finite linear graph.
-(For the finite linear graph in \cref{fig:line}, note that $n=N+1$.)
 From $X_t=i$, we move with equal probability to $i+1$
@@
 	\end{tikzpicture}
-	\caption{A finite linear graph with a vertex at each integer from $0$ to $N$.}\label{fig:line}
+	\caption{A   line graph with a vertex at each integer from $0$ to $N$.}\label{fig:line}
 \end{figure}
@@
 uses what we know about the random walk.
-If $i=0,N$, we are already at the end point and $e_i=0$.
+If $i=0,N$, we are already at the endpoint and $e_i=0$.
 Otherwise, we take a step.
@@
 
-While the final line may look unnecessarily complicated,
+While the final line may look more complicated than what we started with,
 notice that the structure of the equality lends itself to telescoping.
 
-To solve the telescoping equations, notice that the walk is symmetric:
+To solve the telescoping equations, observe that the walk is symmetric:
 we could flip the walk over the vertical axis without changing $e_i$.
@@
 \cref{thm:line} follows from \cref{eq:line} and the observation that any
-linear finite graph can be shifted so that the left end point
-is at $0$ and the right end point is at $N$.
+line graph can be shifted so that the left endpoint
+is at $0$ and the right endpoint is at $N$.
 
 \begin{theorem}
-The expected number of steps from a state to either end of a finite linear graph
-is the product of the distances from that state to each end point.
+The expected number of steps from a state to either end of a line graph
+is the product of the distances from that state to each endpoint.
 \label{thm:line}
@@
 
-We now return to cover times.
+We have the expected time until we reach one endpoint of our line graph.
+Now we want to find the expected time from one endpoint to the other $\E_0[T_N]$.
+By symmetry, $\E_0[T_N] = \E_N[T_0]$.
+
+We write
+\begin{align}
+\E_0[T_N] &= \E_0[T_1] + \E_1[T_2] + ... + \E_{i}[T_{i+1}] + ... + \E_{N-1}[T_N]. \nonumber
+\end{align}
+
+where $\E_{i}[T_{i+1}]$ is the expected time from state $i$ to $i+1$.
+Since there is only one edge incident to 0, we always move from 0 to 1.
+From state $i\neq0$, we take one step in each direction with equal probability.
+In half the cases, we have arrived at $i+1$.
+In the other half of cases, we are in $i-1$.
+It will take us $\E_{i-1}[T_i]$ steps back to $i$ and then another
+$\E_i[T_{i+1}]$ steps to $i+1$.
+Formally,
+\begin{align}
+\E_{i}[T_{i+1}] &= 1 + \frac{1}{2}(\E_{i-1}[T_i]+\E_i[T_{i+1}]) \nonumber \\
+ &= 2 + \E_{i-1}[T_{i}]. \nonumber
+\end{align}
+
+We can use $\E_0[T_1] = 1$ to solve for $E_i[T_{i+1}]$:
+\begin{align}
+E_i[T_{i+1}] &= E_{i-1}[T_{i}] + 2 = E_{i-2}[T_{i-1}] + 4 \nonumber\\
+ &= E_0[T_1] + 2(i-1) = 2i - 1. \nonumber
+\end{align}
+
+Then
+\begin{align}
+\E_0[T_N] &= 1 + 3 + ... + 2i - 1 + ... + 2(N-1) -1 \nonumber \\
+&= N^2 \nonumber
+\end{align}
+
+Then, by \cref{thm:line}, for the random walk from state $i$ on the line graph,
+\begin{align}
+\cov = i(N-i) + N^2. \nonumber
+\end{align}
+
+\subsection{Simple Cycle}
+
+A simple cycle is a connected graph where
+each vertex has an edge to exactly two other vertices.
+(\cref{fig:cycle} is an example.)
+
 Consider a random walk on a simple cycle as in \cref{fig:cycle}.
 (Note that the starting vertex is arbitrary since the graph is symmetric.)
-Think of $(X_t)$ as the walk on the number line (between $-n$ and $n$)
+Let $(X_t)$ be the walk on the number line (between $-n$ and $n$)
 where $X_0 = 0$.
@@
 Then $\E[T_{k+1}-T_{k}]$ is the expected time until we reach $a-1$ or $b+1$.
-Notice that we can shift our end points to 0 and $b+1-(a-1) = b-a + 2 = k+1$.
+Notice that we can shift our endpoints to 0 and $b+1-(a-1) = b-a + 2 = k+1$.
 The expected number of steps to either $a-1$ or $b+1$
@@
 \end{align}
-
-\subsection{Finite Linear Graph}
-We have already seen a finite linear graph.
-(For the finite linear graph in \cref{fig:line}, note that $n=N+1$).
-\cref{thm:line} tells us the expected time from an arbitrary point to
-one of the end points but we do not yet know the cover time.
-
-Observe that the cover time is the earliest time that both end points 
-have been visited.
-We can use our earlier result to find the time to one of the end points
-from an arbitrary position but we still need to find the expected time
-from that end point to the other.
-
-Consider $\E_i[T_N]$ the expected time to $N$ from vertex $i$.
-We want to find $\E_0[T_N]$. By symmetry, $\E_0[T_N] = \E_N[T_0]$.
 
@@
 \cite{AF14}
-\cite{BH94}
+
 \cite{Bo98}

### 2019-04-08 paper.tex
typo fixes

@@
 Note that $\E_i[T_j] = \E[T_j | X_0 = i]$.
-Let the cover time $\cov$ be the until all vertices have been
+Let the cover time be the time until all vertices have been
 visited by the random walk $(X_t)$.
@@
 for the random walk $(X_t)$ started from the top left vertex.
-The black vertex indicates the current vertex of the random walk
-and the empty vertices indicate the visited nodes.
+The black circle indicates the current vertex of the random walk
+and the empty circles indicate the visited vertices.
 
@@
 there are almost a prohibitive number of cases.
-It follows from our combinatorial analysis that the number of states
+It is easy to see that the number of states
 grows exponentially with the number of vertices.
@@
 	\end{tikzpicture}
-	\caption{First step analysis applied to an asymmetric graph with $n=4$.}\label{fig:example}
+	\caption{First step analysis applied to a small, asymmetric graph with $n=4$.}\label{fig:example}
 \end{figure}
@@
 \subsection{Complete Graph}
-We call the graph with $n$ vertices and ${n \choose 2}$ edges the complete graph.
+We call the graph with an edge between each pair of vertices the
+complete graph.
+Note that a complete graph with $n$ vertices has ${n \choose 2}$ edges.
 
@@
 The random variable $X_i$ takes value $k$ when $k-1$ steps lead us to
-already visited vertices and the $k^{th}$ step is to previously unvisited vertex.
+already visited vertices and the $k^{th}$ step is to a previously unvisited vertex.
 It follows that $X_i$ is geometric with distribution
@@
 where $p_i$ is the probability of moving to a previously unvisited vertex.
-Then $\E[X_i] = \frac{1}{p_i}$. We now find $p_i$:
-the probability that we go to a previously unvisited vertex is $\frac{n-i}{n-1}$.
+Then $\E[X_i] = \frac{1}{p_i}$. We now find the probability $p_i$ that 
+we go to a previously unvisited vertex is $\frac{n-i}{n-1}$.
 This is because there are $n-i$ unvisited vertices and a total of $n-1$ adjacent vertices.
@@
 naturally follows that $e_1=e_{N_1}$.
-We use these observations to find $e_1$.
+We use these observations to find $e_1$:
 
@@
 number of steps until we reach $k$ distinct vertices.
-Formally, $T_k = \min{t: b-a+1 = k}$.
+Formally, $T_k = \min\{t: b-a+1 = k\}$.
 Then by telescoping,

### 2019-04-09 paper.tex
matthews method

@@
 \textrm{f} &= 1 + \frac{1}{2}\textrm{g} + \frac{1}{2}\dot 0\nonumber \\
-\textrm{g} &= 1 + \frac{2}{3}\textrm{f} + \frac{1}{3}\dot 0\nonumber \\
+\textrm{g} &= 1 + \frac{2}{3}\textrm{f} + \frac{1}{3}\dot 0\nonumber
 \end{align}
@@
 
-\subsection{Complete Graph}
+\subsection{Complete Graph \label{sec:complete}}
 We call the graph with an edge between each pair of vertices the
@@
 \subsection{Matthews Method}
+We have seen that it is in general very hard
+to calculate the expected cover time of a random walk
+on a graph.
+The exceptions are symmetric or small graphs.
+In lieu of an exact solution, we want to 
+bound the expected cover time.
 
-$\hit \leq \cov$
+The Matthews Method is an example of a remarkably good bound.
+In fact, it is tight for the complete graph:
+the expected time between any two vertices
+is $n-1$ so $\hit = n-1$ and \cref{thm:matthews} gives
+us the main result of \cref{sec:complete}.
+
+In addition, the proof uses strategies we employed on the
+simple cycle and follows an intuitive structure.
 
@@
 \begin{proof}
-Without loss of generality, we may assume that the walk started at vertex $n$.
+Without loss of generality, label the vertices $\{1, 2, ..., n\}$.
+We may assume that the walk started at vertex $n$.
 Let $\sigma$ be a uniform permutation of the unvisited $n-1$ vertices.
 The strategy is to look for the vertices in order $\sigma$.
-We call $\sigma_i$ the $i^{th}$ vertex we visit.
+
 Let $T_k$ be the first time that vertices $\sigma_1, \sigma_2, ..., \sigma_k$
 have all been visited.
-For $1 \leq s \leq n-1$,
+For ease of notation, set $L_k = X_{T_k}$ to be the last state among 
+$\sigma_1, \sigma_2, ..., \sigma_k$ to be visited (the first
+time they are all visited).
+
+We begin by writing the expected cover time in a clever way
+(similar to the strategy we employed on the cycle graph):
 \begin{align}
-\E_n[T_1 | \sigma_1 = s] = t_{n,s} \leq \hit \nonumber
+\cov &= \E_n[{T_{n-1}}]  \nonumber \\
+&= \E_n[T_1 + (T_2 - T_1) + ... + 
+(T_k - T_{k-1}) + ... + (T_{n-1} - T_{n-2})] . \nonumber
 \end{align}
+
+Our goal is to bound the cover time in terms of the hitting time.
+
+Consider the first term of the sum.
+Recall that the hitting time $\hit$ is the maximum
+expected time from any vertex to any other.
+It follows that for any choice of $\sigma_1$,
+the expected time from $n$ to $\sigma_1$ is less than or equal to $\hit$.
+Formally for $s$ an arbitrary state such that $1\leq s \leq n-1$,
+$\E_n[T_1] = \E_n[T_s] \leq \hit$.
+
+Now consider the $k^{th}$ term of the sum for $1 < k \leq n-1$.
+By conditional expectation,
+
+\begin{align}
+\E_n[T_k - T_{k-1}] &=
+\sum_{i=1}^k \E_n[T_k - T_{k-1} | L(k) = \sigma_i]
+P(L_k = \sigma_i). \nonumber 
+\end{align}
+
+Assume that the last vertex $L_k$ to be visted among the first
+$k$ vertices is not $\sigma_k$.
+Then the first time we visit the first $k-1$ vertices
+is also the first time we visit the first $k$ vertices
+(since we must have already visited $\sigma_k$).
+Formally, $\E_n[T_k-T_{k-1}|L(k) \neq \sigma_k] = 0$.
+Then
+
+\begin{align}
+\E_n[T_k - T_{k-1}] &= 0 +
+\E_n[T_k - T_{k-1} | L(k) = \sigma_k]
+P(L_k = \sigma_k). \nonumber 
+\end{align}
+
+Since $\sigma$ is a random permutation, the probability that
+we visit $\sigma_k$ last is $\frac{1}{k}$.
+Formally, $P(L_k = \sigma_k) = \frac{1}{k}$.
+
+Finally, consider the expected time between $T_{k-1}$ and $T_{k}$
+given that last vertex we visit is $\sigma_k$.
+Certainly there exist $r$ and $s$ where $1 \leq r \neq s \leq n-1$
+such that $L_{k-1} = r$ and $L_k = s$.
+Then $\E_n[T_k - T_{k-1} | L(k) = \sigma_k] = \E_r[T_s] \leq \hit$.
+So
+\begin{align}
+\E_n[T_k - T_{k-1}] &\leq
+\hit \frac{1}{k}. \nonumber 
+\end{align}
+
+Putting it all together,
+\begin{align}
+\cov \leq \hit \left( 1+ \frac{1}{2} + ... + \frac{1}{k} 
++ ... + \frac{1}{n-1} \right). \nonumber
+\end{align}
+
 \end{proof}
@@
 \subsection{Spanning Tree Argument}
+\cite{AF14} 3.2
+
+Edge commute inequality
+
+spanning trees
 
@@
 \subsection{Complete Graph}
+\cite{Du11}
+Theorem 2.2.4 -> Example 2.2.5 -> Theorem 3.6.5 -> Example 3.6.6
 
@@
 \subsection{Definitions}
-\subsection{Commute Times}
+\cite{AF14} 3.3
+\subsection{Commute Time}
+\cite{AF14} Proposition 2.3 -> Corollary 2.8 -> Corollary 3.11
+
+\url{https://ocw.mit.edu/courses/mathematics/18-445-introduction-to-stochastic-processes-spring-2015/lecture-notes/MIT18_445S15_lecture8.pdf}
+
 \subsection{Balanced Trees}
+\cite{LP17} 11.3
 
@@
 \cite{AF14}
-
 \cite{Bo98}

### 2019-04-11 paper.tex
electrical network section

@@
 \usepackage{enumitem}
-
+\usepackage{upgreek}
 %\usepackage{cite}
@@
 \DeclareMathOperator{\pr}{\mathrm{P}}		     % expected value
-\DeclareMathOperator{\cov}{t_\textrm{cov}}  % cover time
-\DeclareMathOperator{\hit}{t_{\textrm{hit}}}% hitting time
+\DeclareMathOperator{\cov}{\uptau_\textrm{cov}}  % cover time variable
+\DeclareMathOperator{\tcov}{t_\textrm{cov}}      % cover time
+\DeclareMathOperator{\hit}{t_{\textrm{hit}}}     % hitting time
+\DeclareMathOperator{\Ceff}{C_\textrm{eff}}      % effective conductance
+\DeclareMathOperator{\Reff}{R_{\textrm{eff}}}     % effective resistance
 
@@
 We say $i\sim j$ for $i$ and $j$ in the vertex set $V(G)$ if $(i,j)$ in $E(G)$.
-Let $c(i,j)$ be the non-negative weight of the edge between vertices $i$ and $j$.
-If the graph is unweighted then $c(i,j) = 1$ if $i \sim j$.
+Let $C_{i,j}$ be the non-negative weight of the edge between vertices $i$ and $j$.
+We will mostly consider unweighted graphs
+with $C_{i,j} = 1$ if $i \sim j$ and $C_{i,j} = 0$ otherwise.
 
@@
 \begin{align}
-c(i) &= \sum_{j:i \sim j} c(i,j). \nonumber
+C_i &= \sum_{j:i \sim j} C_{i,j}. \nonumber
 \end{align}
+In the unweighted case, $C_i$ is the degree of vertex $i$.
 
@@
 At each step, the walker at vertex $i$ moves to neighboring vertex
-$j$ with probability $\frac{c(i,j)}{c(i)}$.
+$j$ with probability $c(i,j)/c(i)$.
 
@@
 \begin{align}
-T_{j} &= \textrm{min} \left\{t : X_t = j \right\}. \nonumber
+T_{j} &= \textrm{min} \left\{t > 0 : X_t = j \right\}. \nonumber
 \end{align}
 Let the hitting time $\hit$ be the maximum expected time between two vertices on $G$.
+Note that $\E_i[T_j] = \E[T_j | X_0 = i]$.
 Formally, 
@@
 \end{align}
-Note that $\E_i[T_j] = \E[T_j | X_0 = i]$.
-Let the cover time be the time until all vertices have been
+Let the cover time variable $\cov$ be the first time all vertices have been
 visited by the random walk $(X_t)$.
-We typically refer to the expected cover time $\cov$.
+Formally, $\cov$ is the minimum time that for all $i \in V(G)$
+there exists $t \leq \cov$ such that $X_t = i$.
+We also define the cover time as the expected value of $\cov$ from
+the worst initial vertex.
 Formally,
 \begin{align}
-\cov &= \E [ \max_{j \in V(G)} T_j ]. \nonumber
+\tcov &= \max_{j \in V(G)} \E_j[\cov] . \nonumber
 \end{align}
@@
 for each one.
-Of course, some states are inaccessible.
+Of course, some cases are inaccessible by a random walk.
 But even on \cref{fig:example} where we exploit symmetry,
-there are almost a prohibitive number of cases.
-It is easy to see that the number of states
+there are almost a prohibitive number.
+It is easy to see that the number of cases 
 grows exponentially with the number of vertices.
@@
 				    \draw[edge] (1,1) -- (1,0);
-				    \node (l) at (.5, 1.1) {$\cov$};
+				    \node (l) at (.5, 1.1) {$\tcov$};
 				    \node (bl) at (0,0) {};
@@
 	\end{tikzpicture}
-	\caption{First step analysis applied to a small, asymmetric graph with $n=4$.}\label{fig:example}
+	\caption{First step analysis applied to a small graph with $n=4$.}\label{fig:example}
 \end{figure}
@@
 If we let the label of each graph in \cref{fig:example}
-denote the expected cover time from that graph, we have the following system
+denote the cover time from that case, we have the following system
 of equations:
 \begin{align}
-\cov &= 1 + \frac{1}{3}\textrm{a} + \frac{2}{3}\textrm{b} \nonumber \\
+\tcov &= 1 + \frac{1}{3}\textrm{a} + \frac{2}{3}\textrm{b} \nonumber \\
 \textrm{a} &= 1 + \frac{1}{3}\textrm{a} + \frac{2}{3}\textrm{c} \nonumber \\
@@
 
-With a little linear algebra, we find that $\cov = \frac{43}{6}$.
+With a little linear algebra, we find that $\tcov = 43/6$.
 
@@
 The rest of this section deals with particularly symmetric graphs
-for which it is possible find a solution for an arbitrary $n$.
-However, we must rely on expected cover time bounds for the vast majority of cases.
+for which it is possible to find a solution for an arbitrary $n$.
+However, we must rely on cover time bounds for the vast majority of cases.
 
@@
 because the graph is symmetric.
-The strategy is to write the cover time $\cov$ in terms of the expected
+The strategy is to write the cover time $\tcov$ in terms of the expected
 value of more simple random variables.
@@
 \begin{align}
-\cov&= \E[X_1+X_2+X_3+...+X_{n+1}] = \sum_{i=1}^n \E[X_i] \nonumber
+\tcov&= \E[X_1+X_2+X_3+...+X_{n+1}] = \sum_{i=1}^n \E[X_i] \nonumber
 \end{align}
@@
 already visited vertices and the $k^{th}$ step is to a previously unvisited vertex.
+Then $X_i$ is certainly geometric and $\E[X_i] = 1/p_i$.
+
+\begin{comment}
 It follows that $X_i$ is geometric with distribution
@@
 where $p_i$ is the probability of moving to a previously unvisited vertex.
-Then $\E[X_i] = \frac{1}{p_i}$. We now find the probability $p_i$ that 
-we go to a previously unvisited vertex is $\frac{n-i}{n-1}$.
+\end{comment}
+We now find the probability $p_i$ that 
+we go to a previously unvisited vertex is $(n-i)/(n-1)$.
 This is because there are $n-i$ unvisited vertices and a total of $n-1$ adjacent vertices.
-It follows that $\E[X_i] = \frac{n-1}{n-i}$.
+It follows that $\E[X_i] = (ln-1)(n-i)$.
 Then
 \begin{align}
-\cov&=   \sum_{i=1}^n \frac{n-1}{n-i} \nonumber \\
+\tcov&=   \sum_{i=1}^n \frac{n-1}{n-i} \nonumber \\
 &=  (n-1) \left(\frac{1}{n-1}+\frac{1}{n-2}+...+1\right). \nonumber
@@
 \begin{align}
-\cov&=  r \left(\frac{1}{r}+\frac{1}{r-1}+...+1\right). \nonumber
+\tcov&=  r \left(\frac{1}{r}+\frac{1}{r-1}+...+1\right). \nonumber
 \end{align}
@@
 Whereas in the complete graph and coupon collecting problems we 
-restarted in one step, a random walk on the $n$-star probabilistically restarts
+visited a (possibly) new vertex in one step,
+a random walk on the $n$-star visits a (possibly) new vertex
 in two steps: one step to each leaf and one step back.
@@
 \begin{align}
-\cov&= 2(n-1) \left(\frac{1}{n-1}+\frac{1}{n-2}+...+1\right). \nonumber
+\tcov&= 2(n-1) \left(\frac{1}{n-1}+\frac{1}{n-2}+...+1\right). \nonumber
 \end{align}
@@
 \begin{align}
-\left(e_{2} - e_1\right) &= \left(e_1 - e_{0}\right) - 2 \nonumber \\
-\left(e_{3} - e_2\right) &= \left(e_2 - e_{1}\right) - 2 = \left(e_1 - e_{0}\right) - 4\nonumber \\
-\left(e_{4} - e_3\right) &= \left(e_3 - e_{2}\right) - 2 = \left(e_1 - e_{0}\right) - 6\nonumber \\
+(e_2 - e_1) &= (e_1-e_0) -2 \nonumber\\
+(e_3 - e_2) &= (e_1-e_0) -4 \nonumber\\
 &\;\;\vdots \nonumber\\
@@
 
+\begin{comment}
 \begin{align}
@@
 e_i &= i (N-i) \label{eq:line}
+\end{align}
+\end{comment}
+
+\begin{align}
+(e_2 - e_1) &= (e_1-e_0) -2 \nonumber\\
+(e_3 - e_2) &= (e_1-e_0) -4 \nonumber\\
+&\;\;\vdots \nonumber\\
+(e_i-e_{i-1}) &= (e_1 - e_0) - 2(i-1) \nonumber
+\end{align}
+
+Remember that $e_0=0$, $e_1=N-1$, and 
+$\sum_{i}^{i-1} i = (i-1)i/2$.
+We add all $i-1$ equations:
+
+\begin{align}
+(e_i - e_1) &= (i-1) e_1 - 2[1+2+...+i-1] \nonumber \\
+e_i &= i(N-1) - 2 \frac{(i-1)i}{2} \nonumber\\
+&= i(N-1 - i + 1) = i(N-i)
+\label{eq:line}
 \end{align}
@@
 \begin{align}
-\cov = i(N-i) + N^2. \nonumber
+\tcov = i(N-i) + N^2. \nonumber
 \end{align}
@@
 where $X_0 = 0$.
-The cover time $\cov$ of the simple cycle is the expected number of steps 
+The cover time $\tcov$ of the simple cycle is the expected number of steps 
 until we visit $n$ distinct integers.
@@
 denote the set of vertices we have visited.
-Since the walk is on a line, we can write $[a,b]$ for the range
+Since the walk is on a line, we can $[a,b]$ for the range
 of the walk where $a$ is the smallest 
@@
 \begin{align}
-\cov &= \E[T_n] = \E[(T_2 - T_1) + (T_3 - T_2) + \dots + 
+\tcov &= \E[T_n] = \E[(T_2 - T_1) + (T_3 - T_2) + \dots + 
 (T_k - T_{k-1}) + \dots + (T_n - T_{n-1})] \nonumber
@@
 At time $T_{k}$, we are either at integer $a$ or $b$.
-Then $\E[T_{k+1}-T_{k}]$ is the expected time until we reach $a-1$ or $b+1$.
+Then $\E[T_{k+1}-T_{k}]$ is the first time we reach $a-1$ or $b+1$.
 Notice that we can shift our endpoints to 0 and $b+1-(a-1) = b-a + 2 = k+1$.
@@
 \begin{align}
-\cov &=  (\E[T_2] - \E[T_1]) + \dots +
+\tcov &=  (\E[T_2] - \E[T_1]) + \dots +
 (\E[T_{k+1}] - \E[T_{k}]) + \dots + (\E[T_n] - \E[T_{n-1}]) \nonumber\\
 &= 1 + 2 + \dots + k-1 + \dots + n-1  = \frac{1}{2}n(n-1). \nonumber
+\end{align}
+
+\section{Electrical Networks}
+\cite{DS84}
+There are many connections between electrical networks
+and random walks.
+Physical properties like voltage, current, and resistance
+all have probabilistic interpretations.
+In this section, we explore electrical networks to build intuition about 
+random walks and motivate a result we use to bound cover times.
+
+So that the reader may more easily distinguish between
+vertices, consider $x$ and $y$ in $V(G)$.
+Recall that $C_{x,y}$ is the weight of the edge
+between vertices $x$ and $y$, $C_x$ is the sum
+of all $C_{x,y}$ where $x \sim y$, and the probability $\pr_{x,y}$
+that we go from $x$ to $y$ is $C_{x,y}/C_x$.
+For the rest of this section, we will call $C_{x,y}$
+the conductance between $x$ and $y$.
+Define the resistance $R_{x,y}$ between $x$ and $y$
+as $1/ C_{x,y}$.
+
+We now consider the distribution of the random
+walk on the vertices of our graph.
+Define the proportion $\pi_x$ of time we spend in $x$
+as $C_x/C$ where $C=\sum_y C_y$.
+
+We verify that $\pi$ is the stationary distribution
+of $(X_t)$.
+To begin,
+\begin{align}
+C_x \pr_{x,y} &= C_x \frac{C_{x,y}}{C_x} = C_{x,y} = C_{y,x} 
+= C_y \frac{C_{y,x}}{C_y} = C_y \pr_{y,x}. \nonumber
+\end{align}
+Dividing by $C$ gives $\pi_x \pr_{x,y} = \pi_y \pr_{y,x}$.
+(So $\pi$ satisfies detailed balance.)
+Summing over $x$,
+\begin{align}
+\sum_x \pi_x \pr_{x,y} = \pi_y . \nonumber
+\end{align}
+Then $\pi \pr = \pi$ where $\pr$ is the matrix of transition probabilities.
+It follows that $\pi$ is indeed the stationary distribution of $(X_t)$.
+
+We now introduce voltage, current, and effective resistance.
+Consider $a$ and $b$ in $V(G)$.
+Set the voltage to be 1 at $a$ and 0 at $b$.
+We may think of voltage as the probability we get to $a$ before $b$.
+Probabilistically, of course $v_a = 1$ and $v_b=0$.
+Voltage is a harmonic function so the voltage at every vertex $x$ in 
+$V(G) \textbackslash \{a,b\}$ is determined by the boundary values
+(at $a$ and $b$).
+
+The current between two vertices is the product of the
+difference in their voltages and the conductance of their edge.
+We may think of current as the net number of movements through an edge.
+Kirchoff's Current Law says that the sum of current on any vertex is 0.
+Probabilistically, of course every time we enter a vertex we must also leave it.
+Using Kirchoff's Current Law and the definition of current,
+we justify the probabilistic interpretation of voltage
+\begin{align}
+\sum_y i_{x,y} &= 0 = \sum_y (v_x - v_y)C_{x,y} \nonumber \\
+v_x \sum_y C_{x,y} &= \sum_y C_{x,y} v_y \nonumber \\
+v_x &= \sum_y \frac{C_{x,y}}{C_x} v_y = \sum_y \pr_{x,y} v_y. \nonumber
+\end{align}
+We can probabilistically verify that $v_x = \sum_y \pr_{x,y} v_y$
+using first step analysis on the probability of reaching $a$ before $b$.
+
+We now have the requisite background to prove a result
+we will use to bound cover times.
+Define the probability $\pr_a(T_b < T_a)$ that starting at $a$
+we reach $b$ before returning to $a$.
+(Recall that $T_a>0$.)
+Now define the effective conductance $\Ceff$ as $i_a/v_a$.
+
+With a voltage of 1 at $a$ and 0 at $b$,
+\begin{align}
+\Ceff &= i_a/1 =
+\sum_y (v_a - v_y) C_{a,y} =
+\sum_y (v_a - v_y) \frac{C_{a,y}}{C_a} C_a \nonumber \\
+&= C_a (\frac{v_a}{C_a} \sum_y C_{a,y} - \sum_y \frac{C_{a,y}}{C_a} v_y)=
+C_a(1-\sum_y\pr_{a,y}v_y).\nonumber
+\end{align}
+
+Recall $\sum_y P_{a,y} v_y$ is the probability we reach $a$ before $b$
+so 1 minus that is the probability we reach $b$ before returning to $a$.
+
+Then
+\begin{align}
+\Ceff = C_a \pr_a(T_b < T_a) \nonumber
+\end{align}
+and
+\begin{align}
+\Reff = \frac{1}{C_a \pr_a(T_b < T_a)}. \nonumber
+\end{align}
+
+We use the fact that $\pi_a = C_a / C$ and multiply by $C$,
+\begin{align}
+\Reff C = \frac{1}{\pi_a \pr_a(T_b < T_a)}. \nonumber
+\end{align}
+
+Now our job is to interpret $\Reff C$.
+Recall that $\pr_a(T_b < T_a)$ is the probability, starting from $a$,
+that we get to $b$ before returning to $a$.
+We do independent trials, starting from $a$, until we reach $b$ before $a$.
+Each ``failure'' resets the process so $\pr_a(T_b < T_a)$ is geometrically distributed.
+Then the expected value $1/\pr_a(T_b < T_a)$ is the expected number of times
+we return to $a$ before we finally reach $b$ (and again return to $a$).
+
+Recall that $\pi_a$ is the probability that $(X_t) = a$.
+By the same argument, $1/\pi_a$ is the expected return time to $a$.
+
+Thus the expected time from $a$ to $b$ and back is
+the product of the expected number of times we return to $a$ before reaching $b$
+and the expected return time to $a$.
+The commute time identity follows
+\begin{align}
+E_a[T_b] + E_b[T_a] = \frac{1}{\pi_a}\frac{1}{\pr_a(T_b < T_a)} = \Reff C.
+\label{eqn:commute}
 \end{align}
@@
 We have seen that it is in general very hard
-to calculate the expected cover time of a random walk
+to calculate the cover time of a random walk
 on a graph.
@@
 In lieu of an exact solution, we want to 
-bound the expected cover time.
+bound the cover time.
 
@@
 \begin{align}
-\cov &\leq \hit \left(1 + \frac{1}{2} + \frac{1}{3} + ... + \frac{1}{n-1} \right). \nonumber
+\tcov &\leq \hit \left(1 + \frac{1}{2} + \frac{1}{3} + ... + \frac{1}{n-1} \right). \nonumber
 \end{align}
@@
 For ease of notation, set $L_k = X_{T_k}$ to be the last state among 
-$\sigma_1, \sigma_2, ..., \sigma_k$ to be visited (the first
-time they are all visited).
+$\sigma_1, \sigma_2, ..., \sigma_k$ to be visited the first
+time they are all visited.
 
-We begin by writing the expected cover time in a clever way
+We begin by writing the cover time in a clever way
 (similar to the strategy we employed on the cycle graph):
 \begin{align}
-\cov &= \E_n[{T_{n-1}}]  \nonumber \\
+\tcov &= \E_n[{T_{n-1}}]  \nonumber \\
 &= \E_n[T_1 + (T_2 - T_1) + ... + 
@@
 Since $\sigma$ is a random permutation, the probability that
-we visit $\sigma_k$ last is $\frac{1}{k}$.
-Formally, $P(L_k = \sigma_k) = \frac{1}{k}$.
+we visit $\sigma_k$ last is $1/k$.
+Formally, $P(L_k = \sigma_k) = 1/k$.
 
@@
 \begin{align}
-\cov \leq \hit \left( 1+ \frac{1}{2} + ... + \frac{1}{k} 
+\tcov \leq \hit \left( 1+ \frac{1}{2} + ... + \frac{1}{k} 
 + ... + \frac{1}{n-1} \right). \nonumber
@@
 \end{proof}
+
+\subsubsection{Balanced Trees}
+\cite{LP17} 11.3
 
@@
 
-\section{Electrical Networks}
-\subsection{Definitions}
-\cite{AF14} 3.3
-\subsection{Commute Time}
-\cite{AF14} Proposition 2.3 -> Corollary 2.8 -> Corollary 3.11
-
-\url{https://ocw.mit.edu/courses/mathematics/18-445-introduction-to-stochastic-processes-spring-2015/lecture-notes/MIT18_445S15_lecture8.pdf}
-
-\subsection{Balanced Trees}
-\cite{LP17} 11.3
-
 \section{Simulation}
 
-\cite{AF14}
 \cite{Bo98}
-\cite{DS84}
-\cite{Du11}
 \cite{Gr10}
-\cite{LP17}
 

### 2019-04-13 paper.tex
rearrange electrical networks section and citations

@@
 \end{align}
+
+\subsection{Electrical Networks \label{sec:electric}}
+
+There are many connections between electrical networks
+and random walks \cite{DS84}.
+Physical properties like voltage, current, and resistance
+all have probabilistic interpretations.
+In this section, we explore electrical networks to build intuition about 
+random walks.
+
+So that the reader may more easily distinguish between
+vertices, consider $x$ and $y$ in $V(G)$.
+Recall that $C_{x,y}$ is the weight of the edge
+between vertices $x$ and $y$, $C_x$ is the sum
+of all $C_{x,y}$ where $x \sim y$, and the probability $\pr_{x,y}$
+that we go from $x$ to $y$ is $C_{x,y}/C_x$.
+For the rest of this section, we will call $C_{x,y}$
+the conductance between $x$ and $y$.
+Define the resistance $R_{x,y}$ between $x$ and $y$
+as $1/ C_{x,y}$.
+
+We now consider the distribution of the random
+walk on the vertices of our graph.
+Define the proportion $\pi_x$ of time we spend in $x$
+as $C_x/C$ where $C=\sum_y C_y$.
+
+We verify that $\pi$ is the stationary distribution
+of $(X_t)$.
+To begin,
+\begin{align}
+C_x \pr_{x,y} &= C_x \frac{C_{x,y}}{C_x} = C_{x,y} = C_{y,x} 
+= C_y \frac{C_{y,x}}{C_y} = C_y \pr_{y,x}. \nonumber
+\end{align}
+Dividing by $C$ gives $\pi_x \pr_{x,y} = \pi_y \pr_{y,x}$.
+(So $\pi$ satisfies detailed balance.)
+Summing over $x$,
+\begin{align}
+\sum_x \pi_x \pr_{x,y} = \pi_y . \nonumber
+\end{align}
+Then $\pi \pr = \pi$ where $\pr$ is the matrix of transition probabilities.
+It follows that $\pi$ is indeed the stationary distribution of $(X_t)$.
+
+We now introduce voltage, current, and effective resistance.
+Consider $a$ and $b$ in $V(G)$.
+Set the voltage to be 1 at $a$ and 0 at $b$.
+We may think of voltage as the probability we get to $a$ before $b$.
+Probabilistically, of course $v_a = 1$ and $v_b=0$.
+Voltage is a harmonic function so the voltage at every vertex $x$ in 
+$V(G) \textbackslash \{a,b\}$ is determined by the boundary values
+(at $a$ and $b$).
+
+The current between two vertices is the product of the
+difference in their voltages and the conductance of their edge.
+We may think of current as the net number of movements through an edge.
+Kirchoff's Current Law says that the sum of current on any vertex is 0.
+Probabilistically, of course every time we enter a vertex we must also leave it.
+Using Kirchoff's Current Law and the definition of current,
+we justify the probabilistic interpretation of voltage
+\begin{align}
+\sum_y i_{x,y} &= 0 = \sum_y (v_x - v_y)C_{x,y} \nonumber \\
+v_x \sum_y C_{x,y} &= \sum_y C_{x,y} v_y \nonumber \\
+v_x &= \sum_y \frac{C_{x,y}}{C_x} v_y = \sum_y \pr_{x,y} v_y. \nonumber
+\end{align}
+We can probabilistically verify that $v_x = \sum_y \pr_{x,y} v_y$
+using first step analysis on the probability of reaching $a$ before $b$.
 
@@
 
-\section{Electrical Networks}
-\cite{DS84}
-There are many connections between electrical networks
-and random walks.
-Physical properties like voltage, current, and resistance
-all have probabilistic interpretations.
-In this section, we explore electrical networks to build intuition about 
-random walks and motivate a result we use to bound cover times.
-
-So that the reader may more easily distinguish between
-vertices, consider $x$ and $y$ in $V(G)$.
-Recall that $C_{x,y}$ is the weight of the edge
-between vertices $x$ and $y$, $C_x$ is the sum
-of all $C_{x,y}$ where $x \sim y$, and the probability $\pr_{x,y}$
-that we go from $x$ to $y$ is $C_{x,y}/C_x$.
-For the rest of this section, we will call $C_{x,y}$
-the conductance between $x$ and $y$.
-Define the resistance $R_{x,y}$ between $x$ and $y$
-as $1/ C_{x,y}$.
-
-We now consider the distribution of the random
-walk on the vertices of our graph.
-Define the proportion $\pi_x$ of time we spend in $x$
-as $C_x/C$ where $C=\sum_y C_y$.
-
-We verify that $\pi$ is the stationary distribution
-of $(X_t)$.
-To begin,
-\begin{align}
-C_x \pr_{x,y} &= C_x \frac{C_{x,y}}{C_x} = C_{x,y} = C_{y,x} 
-= C_y \frac{C_{y,x}}{C_y} = C_y \pr_{y,x}. \nonumber
-\end{align}
-Dividing by $C$ gives $\pi_x \pr_{x,y} = \pi_y \pr_{y,x}$.
-(So $\pi$ satisfies detailed balance.)
-Summing over $x$,
-\begin{align}
-\sum_x \pi_x \pr_{x,y} = \pi_y . \nonumber
-\end{align}
-Then $\pi \pr = \pi$ where $\pr$ is the matrix of transition probabilities.
-It follows that $\pi$ is indeed the stationary distribution of $(X_t)$.
-
-We now introduce voltage, current, and effective resistance.
-Consider $a$ and $b$ in $V(G)$.
-Set the voltage to be 1 at $a$ and 0 at $b$.
-We may think of voltage as the probability we get to $a$ before $b$.
-Probabilistically, of course $v_a = 1$ and $v_b=0$.
-Voltage is a harmonic function so the voltage at every vertex $x$ in 
-$V(G) \textbackslash \{a,b\}$ is determined by the boundary values
-(at $a$ and $b$).
-
-The current between two vertices is the product of the
-difference in their voltages and the conductance of their edge.
-We may think of current as the net number of movements through an edge.
-Kirchoff's Current Law says that the sum of current on any vertex is 0.
-Probabilistically, of course every time we enter a vertex we must also leave it.
-Using Kirchoff's Current Law and the definition of current,
-we justify the probabilistic interpretation of voltage
-\begin{align}
-\sum_y i_{x,y} &= 0 = \sum_y (v_x - v_y)C_{x,y} \nonumber \\
-v_x \sum_y C_{x,y} &= \sum_y C_{x,y} v_y \nonumber \\
-v_x &= \sum_y \frac{C_{x,y}}{C_x} v_y = \sum_y \pr_{x,y} v_y. \nonumber
-\end{align}
-We can probabilistically verify that $v_x = \sum_y \pr_{x,y} v_y$
-using first step analysis on the probability of reaching $a$ before $b$.
-
-We now have the requisite background to prove a result
-we will use to bound cover times.
-Define the probability $\pr_a(T_b < T_a)$ that starting at $a$
-we reach $b$ before returning to $a$.
-(Recall that $T_a>0$.)
-Now define the effective conductance $\Ceff$ as $i_a/v_a$.
-
-With a voltage of 1 at $a$ and 0 at $b$,
-\begin{align}
-\Ceff &= i_a/1 =
-\sum_y (v_a - v_y) C_{a,y} =
-\sum_y (v_a - v_y) \frac{C_{a,y}}{C_a} C_a \nonumber \\
-&= C_a (\frac{v_a}{C_a} \sum_y C_{a,y} - \sum_y \frac{C_{a,y}}{C_a} v_y)=
-C_a(1-\sum_y\pr_{a,y}v_y).\nonumber
-\end{align}
-
-Recall $\sum_y P_{a,y} v_y$ is the probability we reach $a$ before $b$
-so 1 minus that is the probability we reach $b$ before returning to $a$.
-
-Then
-\begin{align}
-\Ceff = C_a \pr_a(T_b < T_a) \nonumber
-\end{align}
-and
-\begin{align}
-\Reff = \frac{1}{C_a \pr_a(T_b < T_a)}. \nonumber
-\end{align}
-
-We use the fact that $\pi_a = C_a / C$ and multiply by $C$,
-\begin{align}
-\Reff C = \frac{1}{\pi_a \pr_a(T_b < T_a)}. \nonumber
-\end{align}
-
-Now our job is to interpret $\Reff C$.
-Recall that $\pr_a(T_b < T_a)$ is the probability, starting from $a$,
-that we get to $b$ before returning to $a$.
-We do independent trials, starting from $a$, until we reach $b$ before $a$.
-Each ``failure'' resets the process so $\pr_a(T_b < T_a)$ is geometrically distributed.
-Then the expected value $1/\pr_a(T_b < T_a)$ is the expected number of times
-we return to $a$ before we finally reach $b$ (and again return to $a$).
-
-Recall that $\pi_a$ is the probability that $(X_t) = a$.
-By the same argument, $1/\pi_a$ is the expected return time to $a$.
-
-Thus the expected time from $a$ to $b$ and back is
-the product of the expected number of times we return to $a$ before reaching $b$
-and the expected return time to $a$.
-The commute time identity follows
-\begin{align}
-E_a[T_b] + E_b[T_a] = \frac{1}{\pi_a}\frac{1}{\pr_a(T_b < T_a)} = \Reff C.
-\label{eqn:commute}
-\end{align}
-
 \section{Bounds}
@@
 
-The Matthews Method is an example of a remarkably good bound.
+The Matthews Method is an example of a remarkably good bound \cite{LP17}.
 In fact, it is tight for the complete graph:
 the expected time between any two vertices
-is $n-1$ so $\hit = n-1$ and \cref{thm:matthews} gives
+is $n-1 = \hit$ and \cref{thm:matthews} gives
 us the main result of \cref{sec:complete}.
 
-In addition, the proof uses strategies we employed on the
+An added benefit is that the proof uses strategies we employed on the
 simple cycle and follows an intuitive structure.
@@
 
-\subsubsection{Balanced Trees}
+\subsection{Commute Time Identity}
+Recall \cref{sec:electric}.
+Define the probability $\pr_a(T_b < T_a)$ that starting at $a$
+we reach $b$ before returning to $a$.
+(Recall that $T_a>0$.)
+Now define the effective conductance $\Ceff$ as $i_a/v_a$
+and the effective resistance $\Reff$ as $1/\Ceff$.
+
+With a voltage of 1 at $a$ and 0 at $b$,
+\begin{align}
+\Ceff &= i_a/1 =
+\sum_y (v_a - v_y) C_{a,y} =
+\sum_y (v_a - v_y) \frac{C_{a,y}}{C_a} C_a \nonumber \\
+&= C_a (\frac{v_a}{C_a} \sum_y C_{a,y} - \sum_y \frac{C_{a,y}}{C_a} v_y)=
+C_a(1-\sum_y\pr_{a,y}v_y).\nonumber
+\end{align}
+
+Recall $\sum_y P_{a,y} v_y$ is the probability we reach $a$ before $b$
+so 1 minus that is the probability we reach $b$ before returning to $a$.
+
+Then
+\begin{align}
+\Ceff = C_a \pr_a(T_b < T_a) \nonumber
+\end{align}
+and
+\begin{align}
+\Reff = \frac{1}{C_a \pr_a(T_b < T_a)}. \nonumber
+\end{align}
+
+We use the fact that $\pi_a = C_a / C$ and multiply by $C$,
+\begin{align}
+\Reff C = \frac{1}{\pi_a \pr_a(T_b < T_a)}. \nonumber
+\end{align}
+
+Recall that $\pr_a(T_b < T_a)$ is the probability, starting from $a$,
+that we get to $b$ before returning to $a$.
+We do independent trials, starting from $a$, until we reach $b$ before $a$.
+Each ``failure'' resets the process so $\pr_a(T_b < T_a)$ is geometrically distributed.
+Then the expected value $1/\pr_a(T_b < T_a)$ is the expected number of times
+we return to $a$ before we finally reach $b$ (and again return to $a$).
+
+Recall that $\pi_a$ is the probability that $(X_t) = a$.
+By a similar argument, $1/\pi_a$ is the expected return time to $a$.
+
+Thus the expected time from $a$ to $b$ and back is
+the expected number of returns to $a$ before we reach $b$ times
+the expected number of steps for each return to $a$.
+The commute time identity follows
+\begin{align}
+E_a[T_b] + E_b[T_a] = \frac{1}{\pi_a}\frac{1}{\pr_a(T_b < T_a)} = \Reff C.
+\label{eqn:commute}
+\end{align}
+
+\subsection{Matthews Method on Balanced Trees}
 \cite{LP17} 11.3

### 2019-04-15 paper.tex
matthews lower bound

@@
 \DeclareMathOperator{\hit}{t_{\textrm{hit}}}     % hitting time
+\DeclareMathOperator{\tmina}{t_\textrm{min}^A}   % minimum time on A
 \DeclareMathOperator{\Ceff}{C_\textrm{eff}}      % effective conductance
@@
 \section{Bounds}
+
+\subsection{Commute Time Identity}
+We use the electrical network analysis in \cref{sec:electric} to 
+prove the commute time identity so we may use it to help us bound
+cover times.
+
+Define the probability $\pr_a(T_b < T_a)$ that starting at $a$
+we reach $b$ before returning to $a$.
+(Recall that $T_a>0$.)
+Now define the effective conductance $\Ceff$ as $i_a/v_a$
+and the effective resistance $\Reff$ as $1/\Ceff$.
+
+With a voltage of 1 at $a$ and 0 at $b$,
+\begin{align}
+\Ceff &= i_a/1 =
+\sum_y (v_a - v_y) C_{a,y} =
+\sum_y (v_a - v_y) \frac{C_{a,y}}{C_a} C_a \nonumber \\
+&= C_a (\frac{v_a}{C_a} \sum_y C_{a,y} - \sum_y \frac{C_{a,y}}{C_a} v_y)=
+C_a(1-\sum_y\pr_{a,y}v_y).\nonumber
+\end{align}
+
+Recall $\sum_y P_{a,y} v_y$ is the probability we reach $a$ before $b$
+so 1 minus that is the probability we reach $b$ before returning to $a$.
+
+Then
+\begin{align}
+\Ceff = C_a \pr_a(T_b < T_a) \nonumber
+\end{align}
+and
+\begin{align}
+\Reff = \frac{1}{C_a \pr_a(T_b < T_a)}. \nonumber
+\end{align}
+
+We use the fact that $\pi_a = C_a / C$ and multiply by $C$,
+\begin{align}
+\Reff C = \frac{1}{\pi_a \pr_a(T_b < T_a)}. \nonumber
+\end{align}
+
+Recall that $\pr_a(T_b < T_a)$ is the probability, starting from $a$,
+that we get to $b$ before returning to $a$.
+We do independent trials, starting from $a$, until we reach $b$ before $a$.
+Each ``failure'' resets the process so $\pr_a(T_b < T_a)$ is geometrically distributed.
+Then the expected value $1/\pr_a(T_b < T_a)$ is the expected number of times
+we return to $a$ before we finally reach $b$ (and again return to $a$).
+
+Recall that $\pi_a$ is the probability that $(X_t) = a$.
+By a similar argument, $1/\pi_a$ is the expected return time to $a$.
+
+Thus the expected time from $a$ to $b$ and back is
+the expected number of returns to $a$ before we reach $b$ times
+the expected number of steps for each return to $a$.
+The commute time identity follows
+\begin{align}
+E_a[T_b] + E_b[T_a] = \frac{1}{\pi_a}\frac{1}{\pr_a(T_b < T_a)} = \Reff C.
+\label{eqn:commute}
+\end{align}
+
 \subsection{Matthews Method}
@@
 the expected time between any two vertices
-is $n-1 = \hit$ and \cref{thm:matthews} gives
+is $n-1 = \hit$ and \cref{thm:matthews_up} gives
 us the main result of \cref{sec:complete}.
@@
 
-\begin{theorem}
-Let $(X_t)$ be a random walk on a graph with $n$ vertices. Then \label{thm:matthews}
+\begin{theorem}[Matthews Upper Bound]
+Let $(X_t)$ be a random walk on a graph with $n$ vertices. Then \label{thm:matthews_up}
 \end{theorem}
@@
 
-Finally, consider the expected time between $T_{k-1}$ and $T_{k}$
+Finally, we find the expected time between $T_{k-1}$ and $T_{k}$
 given that last vertex we visit is $\sigma_k$.
-Certainly there exist $r$ and $s$ where $1 \leq r \neq s \leq n-1$
+Consider $r$ and $s$ where $1 \leq r \neq s \leq n-1$
 such that $L_{k-1} = r$ and $L_k = s$.
@@
 \end{align}
-
 \end{proof}
 
-\subsection{Commute Time Identity}
-Recall \cref{sec:electric}.
-Define the probability $\pr_a(T_b < T_a)$ that starting at $a$
-we reach $b$ before returning to $a$.
-(Recall that $T_a>0$.)
-Now define the effective conductance $\Ceff$ as $i_a/v_a$
-and the effective resistance $\Reff$ as $1/\Ceff$.
-
-With a voltage of 1 at $a$ and 0 at $b$,
-\begin{align}
-\Ceff &= i_a/1 =
-\sum_y (v_a - v_y) C_{a,y} =
-\sum_y (v_a - v_y) \frac{C_{a,y}}{C_a} C_a \nonumber \\
-&= C_a (\frac{v_a}{C_a} \sum_y C_{a,y} - \sum_y \frac{C_{a,y}}{C_a} v_y)=
-C_a(1-\sum_y\pr_{a,y}v_y).\nonumber
-\end{align}
-
-Recall $\sum_y P_{a,y} v_y$ is the probability we reach $a$ before $b$
-so 1 minus that is the probability we reach $b$ before returning to $a$.
-
+The same strategy for the Matthews upper bound can be used
+to find a lower bound.
+Instead of looking for all $n$ vertices, we search
+for $A \subseteq V(G)$.
+When the hitting time is large between any two vertices in $A$,
+the time to visit all of $A$ is a good lower bound on the cover time
+of $V(G)$.
+
+\begin{theorem}[Matthews Lower Bound]
+Let $A \subseteq V(G)$. Define $\tmina = \min_{a,b\in A, a \neq b} \E_b[T_a]$.
+Let $(X_t)$ be a random walk on a graph with $n$ vertices. Then \label{thm:matthews_low}
+\end{theorem}
+\begin{align}
+\tcov &\geq \tmina \left(1 + \frac{1}{2} + \frac{1}{3} + ... +
+\frac{1}{|A| -1} \right). \nonumber
+\end{align}
+
+\begin{proof}
+Without loss of generality, label the vertices $\{1, 2, ..., n\}$.
+We may assume that the walk started at vertex $x \in A$.
+Let $\sigma$ be a uniform permutation of the vertices in $A$.
+The strategy is to look for the vertices in order $\sigma$.
+
+Let $T_k$ be the first time that vertices $\sigma_1, \sigma_2, ..., \sigma_k$
+have all been visited.
+For ease of notation, set $L_k = X_{T_k}$.
+
+We again write the cover time in a clever way:
+\begin{align}
+\tcov &\geq \E_x[T_1 + (T_2 - T_1) + ... + 
+(T_k - T_{k-1}) + ... + (T_{|A|} - T_{|A|-1})] . \nonumber
+\end{align}
+
+Our goal is to bound the cover time in terms of $\tmina$.
+
+Consider the first term of the sum.
+With probability $1/|A|$, $\sigma_1 = x$ and $T_1=0$.
+Otherwise, the expected time from $x$ to $T_1$ is less than or equal to
+$\tmina$.
 Then
 \begin{align}
-\Ceff = C_a \pr_a(T_b < T_a) \nonumber
-\end{align}
-and
-\begin{align}
-\Reff = \frac{1}{C_a \pr_a(T_b < T_a)}. \nonumber
-\end{align}
-
-We use the fact that $\pi_a = C_a / C$ and multiply by $C$,
-\begin{align}
-\Reff C = \frac{1}{\pi_a \pr_a(T_b < T_a)}. \nonumber
-\end{align}
-
-Recall that $\pr_a(T_b < T_a)$ is the probability, starting from $a$,
-that we get to $b$ before returning to $a$.
-We do independent trials, starting from $a$, until we reach $b$ before $a$.
-Each ``failure'' resets the process so $\pr_a(T_b < T_a)$ is geometrically distributed.
-Then the expected value $1/\pr_a(T_b < T_a)$ is the expected number of times
-we return to $a$ before we finally reach $b$ (and again return to $a$).
-
-Recall that $\pi_a$ is the probability that $(X_t) = a$.
-By a similar argument, $1/\pi_a$ is the expected return time to $a$.
-
-Thus the expected time from $a$ to $b$ and back is
-the expected number of returns to $a$ before we reach $b$ times
-the expected number of steps for each return to $a$.
-The commute time identity follows
-\begin{align}
-E_a[T_b] + E_b[T_a] = \frac{1}{\pi_a}\frac{1}{\pr_a(T_b < T_a)} = \Reff C.
-\label{eqn:commute}
-\end{align}
+\E_x[T_1] \geq \frac{1}{|A|}0 + \frac{|A| -1}{|A|} \tmina
+= \left(1 - \frac{1}{|A|} \right) \tmina \nonumber
+\end{align}
+
+Now consider the $k^{th}$ term of the sum for $k > 1$.
+By conditional expectation,
+\begin{align}
+\E_x[T_k - T_{k-1}] &=
+\sum_{i=1}^k \E_x[T_k - T_{k-1} | L(k) = \sigma_i]
+P(L_k = \sigma_i). \nonumber 
+\end{align}
+
+Assume that the last vertex $L_k$ to be visted among the first
+$k$ vertices is not $\sigma_k$.
+Then $\E_x[T_k-T_{k-1}|L(k) \neq \sigma_k] = 0$.
+It follows that
+\begin{align}
+\E_x[T_k - T_{k-1}] &= 0 +
+\E_x[T_k - T_{k-1} | L(k) = \sigma_k]
+P(L_k = \sigma_k). \nonumber 
+\end{align}
+
+Since $\sigma$ is a random permutation, $P(L_k = \sigma_k) = 1/k$.
+
+Now find the expected time between $T_{k-1}$ and $T_{k}$
+given that last vertex we visit is $\sigma_k$.
+Consider $r, s \in A$ such that $L_{k-1} = r$ and $L_k = s$.
+Then $\E_x[T_k - T_{k-1} | L(k) = \sigma_k] = \E_r[T_s] \geq \tmina$.
+So
+\begin{align}
+\E_x[T_k - T_{k-1}] &\geq
+\tmina \frac{1}{k}. \nonumber 
+\end{align}
+
+Putting it all together,
+\begin{align}
+\tcov &\geq \tmina \left( 1 - \frac{1}{|A|}+ \frac{1}{2} + ... + \frac{1}{k} 
++ ... + \frac{1}{|A|-1} + \frac{1}{|A|}\right). \nonumber \\
+&= \tmina \left( 1 + \frac{1}{2} + ... + \frac{1}{k} 
++ ... + \frac{1}{|A|-1} \right). \nonumber
+\end{align}
+\end{proof}
 

### 2019-04-20 paper.tex
spanning tree argument and binary trees

@@
 \DeclareMathOperator{\Reff}{R_{\textrm{eff}}}    % effective resistance
-
-\newcommand{\todo}[1]{{\color{blue}{[{\bf TODO:} #1]}}}
+\DeclareMathOperator{\Rxy}{R_{\textrm{x,y}}}     % effective resistance between x,y
+\DeclareMathOperator{\T}{\mathcal{T}}            % spanning tree
+
+\newcommand{\todo}[1]{{\color{blue}{[{\bf todo:} #1]}}}
 
@@
 \subsection{Definitions}
-We consider an undirected graph $G$ without self loops or multi-edges.
+We consider an undirected, connected graph $G$ without self loops or multi-edges.
 Let $V(G)$ be the set of vertices and let $E(G)$ be the set of edges on $G$.
 Then $n$ is the number of vertices $|V(G)|$.
+We say $i\sim j$ for $i$ and $j$ in the vertex set $V(G)$ if $(i,j)$ in $E(G)$.
+Assume that each vertex is accessible from every other vertex.
+That is, there is a set of edges from any $x$ to any $y$.
 %Without loss of generality, we label the vertices $\{1, 2, 3, ..., n\}$.
 
-We say $i\sim j$ for $i$ and $j$ in the vertex set $V(G)$ if $(i,j)$ in $E(G)$.
 Let $C_{i,j}$ be the non-negative weight of the edge between vertices $i$ and $j$.
@@
 
-\subsection{Commute Time Identity}
+\subsection{Commute Time Identity} \label{sec:commute}
 We use the electrical network analysis in \cref{sec:electric} to 
@@
 
-\subsection{Matthews Method on Balanced Trees}
-\cite{LP17} 11.3
+\subsection{Matthews Method on Binary Trees}
+\todo{graph example of binary tree}
+
+\cite{LP17}
+Consider a complete unweighted binary tree with a single root $\rho$.
+Each vertex has two children if it is distance less than $k$
+from the root and no children if it is a leaf (at distance $k$ from the root).
+There are $n = 1 + 2 + 4 + ... + 2^k = 2^{k+1} - 1$ vertices.
+
+By \cref{eqn:commute}, the commute time between the root  and a leaf $a$ is
+\begin{align}
+C R_{\rho, a} = 2 (n-1) k \nonumber
+\end{align}
+Note that the resistance adds in series so $\Rxy = i$ where $i$
+is the length of the single path between $x$ and $y$.
+
+The maximum hitting distance is between two vertices whose 
+mose recent common ancestor is the root.
+For this pair, the hitting time is the same as the commute time
+to the root by symmetry.
+Consider $a$ and $b$ two leaves whose most recent common ancestor
+is the root.
+Then
+\begin{align}
+\E_a [T_b] = \E_a [T_\rho] + \E_\rho [T_a] = 2 (n-1) k \nonumber
+\end{align}
+
+and \cref{thm:matthews_up} gives
+\begin{align}
+\tcov \leq 2(n-1)k\left(1 + \frac{1}{2} + ... + \frac{1}{n} \right). \nonumber
+\end{align}
+
+\todo{add lower bound}
 
 \subsection{Spanning Tree Argument}
-\cite{AF14} 3.2
-
-Edge commute inequality
-
-spanning trees
+\cite{AF14}
+We introduce the concept of a spanning tree to create
+another upper bound for the cover time of a random walk.
+
+\todo{graph example of spanning tree}
+
+A spanning tree $\T$ is a subset of a graph with all edges
+in $V(G)$ connected by the minimum number of edges in $E(G)$.
+For the connected graphs we consider, the minimum number of edges
+needed to connect all vertices is $n-1$.
+Formally, $V(\T) = V(G)$ and $E(\T) \subseteq E(G)$
+such that $|E(\T)| = n-1$ and $\T$ is connected.
+
+In \cref{sec:commute}, we fixed vertices $a$ and $b$ and called
+the effective resistance between them $\Reff$.
+We now consider $\Rxy$ the effective resistance between vertices $x$ and $y$.
+
+\begin{theorem}[Spanning Tree Upper Bound] \label{thm:span}
+For any spanning tree $\T$ on a weighted graph,
+\begin{align}
+\tcov \leq C \sum_{x,y \in E(\T)} \Rxy \leq C \sum_{x,y \in E(\T)} 1 / C_{x,y}. \nonumber
+\end{align}
+In particular for an unweighted graph,
+\begin{align}
+\tcov \leq 2 |E(G)| (n-1). \nonumber 
+\end{align}
+\end{theorem}
+
+\begin{proof}
+Given a spanning tree $\T$, there exists a vertex $v$ with only one edge.
+Consider the path $v_0, v_1, ..., v_{2n-2}$ where $v=v_0=v_{2n-2}$
+that traverses each edge in the spanning once in each direction
+and covers every vertex.
+We construct this path by starting at $v$ and walking along all $n-1$ edges to the
+other vertex with only one edge and then coming back to $v$.
+
+The expected time of this particular path on the original graph is certainly less than
+or equal to the cover time. Thus
+\begin{align}
+\tcov &\leq \sum_{i=0}^{2n-3} \E_{v_i}[T_{v_{i+1}}]. \nonumber
+\end{align}
+
+We rewrite the sum in terms of commute times,
+\begin{align}
+\tcov &\leq \sum_{x,y \in E(\T)} \E_x[T_y] + \E_y[T_x]. \nonumber
+\end{align}
+
+Using \cref{eqn:commute}, $E_x[T_y] + \E_y[T_x] = C \Rxy$,
+\begin{align}
+\tcov &\leq C \sum_{x,y \in E(\T)} \Rxy. \nonumber
+\end{align}
+
+Observe that if $x \sim y$,
+the effective conductance between $x$ and $y$ is at least $C_{x,y}$
+since each additional path only increases the flow.
+It follows that the effective resistance between $x$ and $y$ is at most $1 / C_{x,y}$ so
+\begin{align}
+\tcov &\leq C \sum_{x,y \in E(\T)} 1 / C_{x,y}. \nonumber
+\end{align}
+
+If the graph is unweighted, then $C_{x,y} = 1$ and $C = 2 |E(G)|$.
+Thus
+\begin{align}
+\tcov \leq 2 |E(G)| (n-1). \nonumber
+\end{align}
+
+\end{proof}
 
@@
 Theorem 2.2.4 -> Example 2.2.5 -> Theorem 3.6.5 -> Example 3.6.6
+
+\todo{Theorem 2.2.4}
+
+\todo{Example 2.2.5}
+
+\todo{Theorem 3.6.5}
+
+\todo{Example 3.6.6}
 

### 2019-04-20 paper.tex
change wording
distribution

@@
 \DeclareMathOperator{\E}{\mathrm{E}}		     % expected value
+\DeclareMathOperator{\Var}{\mathrm{Var}}         % variance
+\DeclareMathOperator{\I}{\mathbb{1}}         % variance
 \DeclareMathOperator{\pr}{\mathrm{P}}		     % expected value
@@
 there exists $t \leq \cov$ such that $X_t = i$.
-We also define the cover time as the expected value of $\cov$ from
+We define the cover time as the expected value of $\cov$ from
 the worst initial vertex.
@@
 \section{Distributional Aspects}
-\subsection{Complete Graph}
 \cite{Du11}
-Theorem 2.2.4 -> Example 2.2.5 -> Theorem 3.6.5 -> Example 3.6.6
-
-\todo{Theorem 2.2.4}
-
-\todo{Example 2.2.5}
-
-\todo{Theorem 3.6.5}
-
-\todo{Example 3.6.6}
+Consider a random walk on the complete graph with self-edges.
+Call $r$ the number of steps since we began the random walk.
+Let $A_i$ be the event that vertex $i$ is not visited and
+$N_n$ the number of unvisited vertices.
+Then
+\begin{align}
+P(A_i) = (1-1/n)^r \nonumber
+\end{align}
+and
+\begin{align}
+\E[N_n] = n(1-1/n)^r. \nonumber
+\end{align}
+
+If $r/n \rightarrow c$, then
+\begin{align}
+\E[N_n]/n &= (1-1/n)^r = [(1-1/n)^n]^{r/n} \rightarrow (e^{-1})^c \nonumber \\
+\E[N_n]/n &\rightarrow e^{-c}. \nonumber
+\end{align}
+
+We compute the variance of $N_n$.
+Let $\I_m$ be the indicator random variable for $A_m$.
+First find $E[N_n^2]$,
+\begin{align}
+\E[N_n^2] &= \E \left[ \left(\sum_{m=1}^n \I_m \right) ^2 \right] =
+\E \left[ \sum_{m=1}^n \sum_{k=1}^n \I_m \I_k \right] =
+\sum_{1 \leq k, m \leq n} \pr(A_k \cap A_m). \nonumber
+\end{align}
+
+Then
+\begin{align}
+\Var[N_n] &= \E[N_n^2] - \E[N_n]^2 \nonumber \\
+&= \sum_{1 \leq k, m \leq n} \pr(A_k \cap A_m) - P(A_k)P(A_m) \nonumber \\
+&= n(n-1) \{ \pr(A_k \cap A_m) - P(A_k)P(A_m) \} + 
+n \{ \pr(A_k \cap A_m) - P(A_k)P(A_m) \} \nonumber \\
+&= n(n-1) \{ (1-2/n)^r - (1-1/n)^{2r} \} + 
+n \{ (1-1/n)^r  - (1-1/n)^{2r} \}. \nonumber
+\end{align}
+where $k\neq m$ in the first term and $k=m$ in the second.
+
+As $n \rightarrow \infty$,
+\begin{align}
+\Var(N_n/n) &= \Var(N_n) / n^2 \nonumber\\
+&\rightarrow (1-2/n)^r - (1-1/n)^{2r} = e^{-2c} - (e^{-c})^2 = 0. \nonumber
+\end{align}
+
+By Chebyshev's Inequality,
+\begin{align}
+\pr \left( |N_n/n - \E[N_n/n]| \geq \epsilon \right) &\leq \Var(N_n/n) / \epsilon^2
+\rightarrow 0. \nonumber
+\end{align}
+
+Thus we conclude $N_n/n \rightarrow \E[N_n/n] = e^{-c}$ in probability.
+
+The Poisson approximation of the binomial implies that if $n \rightarrow \infty$
+and $r/n \rightarrow c$, then the number of visits to each vertex will approach
+a Poisson distribution with mean $c$.
+Then it intuitively follows that the proportion of visits to each vertex
+approaches $e^{-c}$.
+
+\begin{theorem}\label{thm:pois}
+If $ne^{-r/n} \rightarrow \lambda \in [0, \infty)$, then the number of unvisited
+vertices approaches a Poisson distribution with mean $\lambda$.
+\end{theorem}
+
+\begin{proof}
+Observe that the probability that there are $k$ unvisited vertices
+\begin{align}
+(1-k/n)^r \nonumber.
+\end{align}
+
+Define $p_m(r,n)$ as the probability that exactly $m$ vertices are unvisited
+when $r$ steps have been taken.
+Then the probability that all vertices have been visited is the complement
+of the probability that at least one vertex has not been visited.
+
+By the principle of inclusion-exclusion,
+\begin{align}
+p_0(r,n) &= {n \choose 0} 1^r - {n \choose 1} (1-1/n)^r + ... \nonumber\\
+&= \sum_{k=0}^n (-1)^k {n \choose k} (1-k/n)^r. \nonumber
+\end{align}
+
+If we consider the locations of the unvisited vertices,
+\begin{align}
+p_m(r,n) = {n \choose m} \left(1-\frac{m}{n}\right)^r p_0(r, n-m). \nonumber
+\end{align}
+
+We want to show that 
+\begin{align}
+{n \choose m} \left(1-\frac{m}{n}\right)^r \rightarrow \lambda ^m /m! \nonumber
+\end{align}
+
+We begin with the more straightforward upper bound.
+Notice that $(1-x) \leq e^{-x}$ and recall our assumption that
+$ne^{r/n} \rightarrow \lambda$.
+Then
+\begin{align}
+{n \choose m} \left(1-\frac{m}{n}\right)^r &\leq \frac{n^m}{m!} e^{mr/n} \nonumber \\
+&= \frac{(n e^{r/n})^m} {m!} \nonumber \\
+&\rightarrow \lambda ^m / m! \nonumber
+\end{align}
+
+We now turn to the more tricky lower bound.
+Notice that ${n \choose m} \geq (n-m)^m / m!$
+\todo{why?}
+Then
+\begin{align}
+{n \choose m} \left(1-\frac{m}{n}\right)^r &\geq \left(1-\frac{m}{n}\right)^r (n-m)^m / m! \nonumber\\
+&\geq n^m (1 - \frac{m}{n})^r (1- \frac{m}{n})^m  / m! \nonumber
+\end{align}
+
+As $n \rightarrow \infty$, $\left(1-\frac{m}{n}\right)^m \rightarrow 1$ and $1/m!$ is constant.
+We use the Taylor series of $\log(1-t)$ for $0 \leq t \leq 1/2$
+to bound the rest.
+So
+\begin{align}
+\log(1-t) &= 0 - t - t^2/2 -t^3/3 - ... \nonumber\\
+&\geq -t -t^2/2(1 + 1/2 + 1/4 + ...) = -t - t^2 \nonumber
+\end{align}
+and we have
+\begin{align}
+\log \left(n^m\left(1-\frac{m}{n}\right)^r \right)
+&= m \log n + r \log\left(1-\frac{m}{n}\right) \nonumber \\
+& \geq m \log n - r m /n - r m/n^2. \nonumber
+\end{align}
+
+\todo{why?}
+Our assumption that $ne^{r/n} \rightarrow \lambda$ implies that
+\begin{align}
+r = n \log n - n \log \lambda + o(n) \nonumber
+\end{align}
+so $r(m/n)^2 \rightarrow 0$.
+Then
+\begin{align}
+rm/n &=m \log n - m \log \lambda + o(n)m/n \nonumber \\
+m \log \lambda &\rightarrow m \log n - rm/n \nonumber
+\end{align}
+and
+\begin{align}
+\log \left(n^m\left(1-\frac{m}{n}\right)^r \right)
+&\geq m \log n - rm/n \nonumber
+\end{align}
+so
+\begin{align}
+\lim_{n\rightarrow \infty} n^m\left(1-\frac{m}{n}\right)^r
+&\geq \lambda^m. \nonumber
+\end{align}
+
+Now we piece together the pieces.
+To begin,
+\begin{align}
+{ n \choose m } (1-\frac{m}{n})^r \rightarrow \lambda^m /m! \nonumber
+\end{align}
+so
+\begin{align}
+p_0(r,n) \rightarrow \sum_{k=0}^\infty \lambda^k /k! = e^{-\lambda}. \nonumber
+\end{align}
+
+The result holds
+\begin{align}
+p_0(r,n-m) \rightarrow e^{-\lambda} \nonumber
+\end{align}
+for fixed $m$ since $(n-m)e^{r/(n-m)} \rightarrow \lambda$.
+
+Finally,
+\begin{align}
+p_m(r,n) &= {n \choose m} (1-\frac{m}{n})^r p_0(r, n-m) \nonumber \\
+&\rightarrow \frac{\lambda^m}{ m!} e^{-\lambda} \nonumber
+\end{align}
+so we have that $N_n \rightarrow \textrm{Pois}(\lambda)$ as claimed.
+
+\end{proof}
+
+Set $r = n \log n + nx$.
+Then 
+\begin{align}
+ne^{-r/n} &= n e ^{- \log n - x} \nonumber \\
+&= n e {- \log n} e^ {- x} = e^{-x}\nonumber
+\end{align}
+
+Consider the cover time variable $\cov$.
+Since $\cov \leq m$ if and only if the first $m$ steps
+of the random walk visit all $n$ vertices, then by \cref{thm:pois},
+\begin{align}
+\pr(\cov \leq r) &\rightarrow e^{-e^{-x}} \nonumber \\
+\pr(\cov - n \log n\leq nx) &\rightarrow e^{-e^{-x}} \nonumber
+\end{align}
 

### 2019-04-21 paper.tex
figures

@@
 \subsection{Matthews Method on Binary Trees}
-\todo{graph example of binary tree}
+
+\begin{figure}[ht]
+	\centering
+	\begin{tikzpicture}[scale = 2]
+	    \tikzstyle{vertex}=[draw, circle,fill=black, scale=.7]
+	    \tikzstyle{edge}=[draw,line width = .5pt,-,black!100]
+	    \node[vertex] (0) at (0,3) {};
+	    \node[vertex] (1) at (1,2) {};
+	    \node[vertex] (2) at (-1,2) {};
+	    \node[vertex] (3) at (1.5,1) {};
+	    \node[vertex] (4) at (.5,1) {};
+	    \node[vertex] (5) at (-.5,1) {};
+	    \node[vertex] (6) at (-1.5,1) {};
+	    \node[vertex] (7) at (1.75,0) {};
+	    \node[vertex] (8) at (1.25,0) {};
+	    \node[vertex] (9) at (.75,0) {};
+	    \node[vertex] (10) at (.25,0) {};
+	    \node[vertex] (11) at (-.25,0) {};
+	    \node[vertex] (12) at (-.75,0) {};
+	    \node[vertex] (13) at (-1.25,0) {};
+	    \node[vertex] (14) at (-1.75,0) {};
+	    \draw[edge] (1) -- (0);
+	    \draw[edge] (2) -- (0);
+	    \draw[edge] (1) -- (3);
+	    \draw[edge] (4) -- (1);
+	    \draw[edge] (2) -- (5);
+	    \draw[edge] (6) -- (2);
+	    \draw[edge] (3) -- (7);
+	    \draw[edge] (3) -- (8);
+	    \draw[edge] (4) -- (9);
+	    \draw[edge] (4) -- (10);
+	    \draw[edge] (5) -- (11);
+	    \draw[edge] (5) -- (12);
+	    \draw[edge] (6) -- (13);
+	    \draw[edge] (6) -- (14);
+	\end{tikzpicture}
+	\caption{A binary tree with $k=3$ and $n=15$.}\label{fig:binary}
+\end{figure}
 
 \cite{LP17}
-Consider a complete unweighted binary tree with a single root $\rho$.
-Each vertex has two children if it is distance less than $k$
-from the root and no children if it is a leaf (at distance $k$ from the root).
+Consider an unweighted binary tree as in \cref{fig:binary} with a single root $\rho$.
+A vertex has two children if it is distance less than $k$
+from the root and no children if it is a leaf (distance $k$ from the root).
 There are $n = 1 + 2 + 4 + ... + 2^k = 2^{k+1} - 1$ vertices.
@@
 
-\todo{graph example of spanning tree}
+\begin{figure}[ht]
+	\centering
+	\begin{tikzpicture}[scale = 2]
+	    \tikzstyle{vertex}=[draw, circle,fill=black, scale=.7]
+	    \tikzstyle{edge}=[draw,line width = .25pt,-,black!100]
+	    \tikzstyle{span}=[draw,line width = 2pt,-,black!100]
+	    \node[vertex] (0) at (0,0) {};
+	    \node[vertex] (1) at (1,0) {};
+	    \node[vertex] (2) at (1,1) {};
+	    \node[vertex] (3) at (0,1) {};
+	    \draw[span] (0) -- (1);
+	    \draw[edge] (0) -- (2);
+	    \draw[edge] (0) -- (3);
+	    \draw[span] (1) -- (2);
+	    \draw[edge] (1) -- (3);
+	    \draw[span] (2) -- (3);
+	\end{tikzpicture}
+	\caption{A spanning tree of the complete graph with $n=4$.}\label{fig:span}
+\end{figure}
 
@@
 in $V(G)$ connected by the minimum number of edges in $E(G)$.
+\cref{fig:span} is an example where the bold edges indicate the edges in $E(\T)$
+and the light edges indicate the edges in $E(G)$ but not $E(\T)$.
 For the connected graphs we consider, the minimum number of edges
@@
 The expected time of this particular path on the original graph is certainly less than
-or equal to the cover time. Thus
+or equal to the cover time. That is,
 \begin{align}
@@
 
-Using \cref{eqn:commute}, $E_x[T_y] + \E_y[T_x] = C \Rxy$,
+Using \cref{eqn:commute}, we have $E_x[T_y] + \E_y[T_x] = C \Rxy$ and,
 \begin{align}
@@
 If the graph is unweighted, then $C_{x,y} = 1$ and $C = 2 |E(G)|$.
-Thus
+Then
 \begin{align}
@@
 \cite{Du11}
-Consider a random walk on the complete graph with self-edges.
+We consider the distribution of the cover time of a random walk
+on the complete graph with self edges.
 Call $r$ the number of steps since we began the random walk.
@@
 \begin{align}
-\E[N_n]/n &= (1-1/n)^r = [(1-1/n)^n]^{r/n} \rightarrow (e^{-1})^c \nonumber \\
-\E[N_n]/n &\rightarrow e^{-c}. \nonumber
-\end{align}
-
-We compute the variance of $N_n$.
-Let $\I_m$ be the indicator random variable for $A_m$.
-First find $E[N_n^2]$,
+\E[N_n]/n &= (1-1/n)^r = [(1-1/n)^n]^{r/n} \rightarrow (e^{-1})^c
+\rightarrow e^{-c}. \nonumber
+\end{align}
+
+We compute the variance of $N_n$ by finding $\E[N_n^2]$ and $\E[N_n]^2$.
+Let $\I_m$ be the indicator random variable for event $A_m$.
+That is, $\I_m = 1$ if vertex $m$ is unvisited 0 otherwise.
+We already know $\E[N_n]$ so we want to find $\E[N_n^2]$,
 \begin{align}
@@
 
-Then
+The second equality holds since we distribute terms.
+The third equality holds since the mean of an indicator for event $A_m$
+is the probability of $A_m$.
+Putting both terms together, we find the variance
 \begin{align}
@@
 
-Thus we conclude $N_n/n \rightarrow \E[N_n/n] = e^{-c}$ in probability.
+Thus we conclude that $N_n/n \rightarrow \E[N_n/n] = e^{-c}$ in probability.
 
@@
 a Poisson distribution with mean $c$.
-Then it intuitively follows that the proportion of visits to each vertex
+We can use this to intuite our conclusion: the proportion of visits to each vertex
 approaches $e^{-c}$.
 
+We prove the following theorem and then use it to show that $\cov \sim \textrm{Pois}(e^{-x})$.
 \begin{theorem}\label{thm:pois}
@@
 \begin{proof}
-Observe that the probability that there are $k$ unvisited vertices
+Observe that the probability that there are $k$ unvisited vertices is
 \begin{align}
@@
 
-We want to show that 
+Our strategy is to show that $p_m(r,n) \rightarrow \frac{\lambda^m}{m!}e^{-\lambda}$.
+The first step is to prove that
 \begin{align}
@@
 
-We begin with the more straightforward upper bound.
+We bound the expression from the top and the bottom and use the dominated convergence
+theorem.
+We will first show the upper bound.
 Notice that $(1-x) \leq e^{-x}$ and recall our assumption that
@@
 &= \frac{(n e^{r/n})^m} {m!} \nonumber \\
-&\rightarrow \lambda ^m / m! \nonumber
+&\rightarrow \frac{\lambda ^m} {m!} \nonumber
 \end{align}
@@
 
-As $n \rightarrow \infty$, $\left(1-\frac{m}{n}\right)^m \rightarrow 1$ and $1/m!$ is constant.
+As $n \rightarrow \infty$, $\left(1-\frac{m}{n}\right)^m \rightarrow 1$
+and $1/m!$ is constant.
 We use the Taylor series of $\log(1-t)$ for $0 \leq t \leq 1/2$
-to bound the rest.
-So
+to bound the rest of the term.
+Notice that
 \begin{align}
@@
 \end{align}
-and we have
+and so we have
 \begin{align}
@@
 \begin{align}
-rm/n &=m \log n - m \log \lambda + o(n)m/n \nonumber \\
+rm/n &=m \log n - m \log \lambda + o(n)m/n \nonumber
+\end{align}
+and in particular
+\begin{align}
 m \log \lambda &\rightarrow m \log n - rm/n \nonumber
 \end{align}
-and
+so
 \begin{align}
 \log \left(n^m\left(1-\frac{m}{n}\right)^r \right)
-&\geq m \log n - rm/n \nonumber
-\end{align}
-so
+&\geq m \log n - rm/n. \nonumber
+\end{align}
+It follows that
 \begin{align}
@@
 
-Now we piece together the pieces.
+Now we put together the pieces.
 To begin,
@@
 
-The result holds
+The result holds for
 \begin{align}
@@
 \end{align}
-for fixed $m$ since $(n-m)e^{r/(n-m)} \rightarrow \lambda$.
+since $m$ is fixed and $(n-m)e^{r/(n-m)} \rightarrow \lambda$.
 
@@
 ne^{-r/n} &= n e ^{- \log n - x} \nonumber \\
-&= n e {- \log n} e^ {- x} = e^{-x}\nonumber
+&= n e {- \log n} e^ {- x} = e^{-x}.\nonumber
 \end{align}
@@
 \begin{align}
-\pr(\cov \leq r) &\rightarrow e^{-e^{-x}} \nonumber \\
-\pr(\cov - n \log n\leq nx) &\rightarrow e^{-e^{-x}} \nonumber
+\pr(\cov \leq r) &\rightarrow e^{-e^{-x}} \nonumber
+\end{align}
+and
+\begin{align}
+\pr(\cov - n \log n\leq nx) &\rightarrow e^{-e^{-x}}. \nonumber
 \end{align}

### 2019-04-23 paper.tex
minor

@@
 
-We prove the following theorem and then use it to show that $\cov \sim \textrm{Pois}(e^{-x})$.
+We prove the following theorem and then use it to gain insight into the cover time
+variable $\cov$.
 \begin{theorem}\label{thm:pois}
@@
 We bound the expression from the top and the bottom and use the dominated convergence
-theorem.
+theorem to prove the previous limit.
 We will first show the upper bound.

### 2019-04-23 paper.tex
matthews lower on binary

--- 2019-04-21 paper.tex
@@
 
-\abstract{abstract}
+\abstract{\todo{abstract}}
 
@@
 
+\todo{write general introduction to cover times}
 "white screen" problem
@@
 \subsection{Motivation}
+\todo{write about applications}
 universal travel sequences
@@
 protocol testing
+birthday problem
+coupon collectors
 
@@
 \subsection{Outline}
+
+\todo{outline of each section and subsections}
 
@@
 \begin{align}
-\tcov&= \E[X_1+X_2+X_3+...+X_{n+1}] = \sum_{i=1}^n \E[X_i] \nonumber
+\tcov&= \E[X_1+X_2+X_3+\ldots+X_{n+1}] = \sum_{i=1}^n \E[X_i] \nonumber
 \end{align}
@@
 \tcov&=   \sum_{i=1}^n \frac{n-1}{n-i} \nonumber \\
-&=  (n-1) \left(\frac{1}{n-1}+\frac{1}{n-2}+...+1\right). \nonumber
+&=  (n-1) \left(\frac{1}{n-1}+\frac{1}{n-2}+\ldots+1\right). \nonumber
 \end{align}
@@
 \begin{align}
-\tcov&=  r \left(\frac{1}{r}+\frac{1}{r-1}+...+1\right). \nonumber
+\tcov&=  r \left(\frac{1}{r}+\frac{1}{r-1}+\ldots+1\right). \nonumber
 \end{align}
@@
 \begin{align}
-\tcov&= 2(n-1) \left(\frac{1}{n-1}+\frac{1}{n-2}+...+1\right). \nonumber
+\tcov&= 2(n-1) \left(\frac{1}{n-1}+\frac{1}{n-2}+\ldots+1\right). \nonumber
 \end{align}
@@
 \begin{align}
-(e_i - e_1) &= (i-1) e_1 - 2[1+2+...+i-1] \nonumber \\
+(e_i - e_1) &= (i-1) e_1 - 2[1+2+\ldots+i-1] \nonumber \\
 e_i &= i(N-1) - 2 \frac{(i-1)i}{2} \nonumber\\
@@
 \begin{align}
-\E_0[T_N] &= \E_0[T_1] + \E_1[T_2] + ... + \E_{i}[T_{i+1}] + ... + \E_{N-1}[T_N]. \nonumber
+\E_0[T_N] &= \E_0[T_1] + \E_1[T_2] + \ldots + \E_{i}[T_{i+1}] + \ldots + \E_{N-1}[T_N]. \nonumber
 \end{align}
@@
 \begin{align}
-\E_0[T_N] &= 1 + 3 + ... + 2i - 1 + ... + 2(N-1) -1 \nonumber \\
+\E_0[T_N] &= 1 + 3 + \ldots + 2i - 1 + \ldots + 2(N-1) -1 \nonumber \\
 &= N^2 \nonumber
@@
 \begin{align}
-\tcov &\leq \hit \left(1 + \frac{1}{2} + \frac{1}{3} + ... + \frac{1}{n-1} \right). \nonumber
+\tcov &\leq \hit \left(1 + \frac{1}{2} + \frac{1}{3} + \ldots + \frac{1}{n-1} \right). \nonumber
 \end{align}
@@
 \begin{proof}
-Without loss of generality, label the vertices $\{1, 2, ..., n\}$.
+Without loss of generality, label the vertices $\{1, 2, \ldots, n\}$.
 We may assume that the walk started at vertex $n$.
@@
 
-Let $T_k$ be the first time that vertices $\sigma_1, \sigma_2, ..., \sigma_k$
+Let $T_k$ be the first time that vertices $\sigma_1, \sigma_2, \ldots, \sigma_k$
 have all been visited.
 For ease of notation, set $L_k = X_{T_k}$ to be the last state among 
-$\sigma_1, \sigma_2, ..., \sigma_k$ to be visited the first
+$\sigma_1, \sigma_2, \ldots, \sigma_k$ to be visited the first
 time they are all visited.
@@
 \tcov &= \E_n[{T_{n-1}}]  \nonumber \\
-&= \E_n[T_1 + (T_2 - T_1) + ... + 
-(T_k - T_{k-1}) + ... + (T_{n-1} - T_{n-2})] . \nonumber
+&= \E_n[T_1 + (T_2 - T_1) + \ldots + 
+(T_k - T_{k-1}) + \ldots + (T_{n-1} - T_{n-2})] . \nonumber
 \end{align}
@@
 \begin{align}
-\tcov \leq \hit \left( 1+ \frac{1}{2} + ... + \frac{1}{k} 
-+ ... + \frac{1}{n-1} \right). \nonumber
+\tcov \leq \hit \left( 1+ \frac{1}{2} + \ldots + \frac{1}{k} 
++ \ldots + \frac{1}{n-1} \right). \nonumber
 \end{align}
@@
 \begin{align}
-\tcov &\geq \tmina \left(1 + \frac{1}{2} + \frac{1}{3} + ... +
+\tcov &\geq \tmina \left(1 + \frac{1}{2} + \frac{1}{3} + \ldots +
 \frac{1}{|A| -1} \right). \nonumber
@@
 \begin{proof}
-Without loss of generality, label the vertices $\{1, 2, ..., n\}$.
+Without loss of generality, label the vertices $\{1, 2, \ldots, n\}$.
 We may assume that the walk started at vertex $x \in A$.
@@
 
-Let $T_k$ be the first time that vertices $\sigma_1, \sigma_2, ..., \sigma_k$
+Let $T_k$ be the first time that vertices $\sigma_1, \sigma_2, \ldots, \sigma_k$
 have all been visited.
@@
 \begin{align}
-\tcov &\geq \E_x[T_1 + (T_2 - T_1) + ... + 
-(T_k - T_{k-1}) + ... + (T_{|A|} - T_{|A|-1})] . \nonumber
+\tcov &\geq \E_x[T_1 + (T_2 - T_1) + \ldots + 
+(T_k - T_{k-1}) + \ldots + (T_{|A|} - T_{|A|-1})] . \nonumber
 \end{align}
@@
 \begin{align}
-\tcov &\geq \tmina \left( 1 - \frac{1}{|A|}+ \frac{1}{2} + ... + \frac{1}{k} 
-+ ... + \frac{1}{|A|-1} + \frac{1}{|A|}\right). \nonumber \\
-&= \tmina \left( 1 + \frac{1}{2} + ... + \frac{1}{k} 
-+ ... + \frac{1}{|A|-1} \right). \nonumber
+\tcov &\geq \tmina \left( 1 - \frac{1}{|A|}+ \frac{1}{2} + \ldots + \frac{1}{k} 
++ \ldots + \frac{1}{|A|-1} + \frac{1}{|A|}\right). \nonumber \\
+&= \tmina \left( 1 + \frac{1}{2} + \ldots + \frac{1}{k} 
++ \ldots + \frac{1}{|A|-1} \right). \nonumber
 \end{align}
@@
 from the root and no children if it is a leaf (distance $k$ from the root).
-There are $n = 1 + 2 + 4 + ... + 2^k = 2^{k+1} - 1$ vertices.
+There are $n = 1 + 2 + 4 + \ldots + 2^k = 2^{k+1} - 1$ vertices.
 
@@
 \begin{align}
-C R_{\rho, a} = 2 (n-1) k \nonumber
-\end{align}
-Note that the resistance adds in series so $\Rxy = i$ where $i$
+C R_{\rho, a} = 2 (n-1) k \nonumber.
+\end{align}
+Note that effective resistance adds in series so $\Rxy = i$ where $i$
 is the length of the single path between $x$ and $y$.
 
+We first use the Matthews Upper Bound.
 The maximum hitting distance is between two vertices whose 
@@
 \begin{align}
-\tcov \leq 2(n-1)k\left(1 + \frac{1}{2} + ... + \frac{1}{n} \right). \nonumber
-\end{align}
-
-\todo{add lower bound}
+\tcov &\leq 2(n-1)k\left(1 + \frac{1}{2} + \ldots + \frac{1}{n} \right) \nonumber \\
+&\approx (2 - \frac{2}{n}) \cdot n k \log n \approx (2 - \frac{2}{n}) n k \log 2^{k+1} -1 \nonumber \\
+&\approx (2  + o(1)) \cdot n k^2 \log 2 \nonumber
+\end{align}
+
+We now use the Matthews Lower Bound.
+Choose a set $A \subseteq V(G)$ with a large hitting time between any
+pair of vertices.
+To find such a set, fix a level $h$ in our binary tree.
+Then let $A$ be a set of $2^h$ leaves so that each vertex at level $h$
+has a unique descendent in $A$.
+As $h$ increases, the distance between the leaves in $A$ decreases.
+Thus we want to choose a smaller value of $h$ so that our lower bound will be bigger
+(and better).
+
+For $a,b \in A$, the hitting time between $a$ and $b$ is the commute time
+from $a$ to their nearest common ancestor at level $h' < h$.
+By \cref{eqn:commute}, we have
+\begin{align}
+\E_a [T_b] = \E_a [T_h'] + \E_{h'} [T_a] = 2 (n-1) (k-h') \nonumber.
+\end{align}
+
+In the worst case, $h' = h-1$.
+Then by \cref{thm:matthews_low},
+\begin{align}
+\tcov &\geq 2 (n-1)(k-h+1)\left(1 + \frac{1}{2} + \ldots + \frac{1}{2^h -1} \right) \nonumber \\
+&\approx (2 + o(1)) \cdot n (k-h) h \log 2 \nonumber.
+\end{align}
+
+If $h=\lfloor k/2 \rfloor$,
+\begin{align}
+\tcov &\geq \frac{1}{4} ( 2 + o(1) )\cdot nk^2 \log 2\nonumber
+\end{align}
+then there is a factor of 4 gap between the upper bound and lower bound
+of the cover time of a binary tree!
 
@@
 	\end{tikzpicture}
-	\caption{A spanning tree of the complete graph with $n=4$.}\label{fig:span}
+	\caption{A spanning tree (in bold) of the complete graph with $n=4$.}\label{fig:span}
 \end{figure}
@@
 Given a spanning tree $\T$, there exists a vertex $v$ with only one edge.
-Consider the path $v_0, v_1, ..., v_{2n-2}$ where $v=v_0=v_{2n-2}$
+Consider the path $v_0, v_1, \ldots, v_{2n-2}$ where $v=v_0=v_{2n-2}$
 that traverses each edge in the spanning once in each direction
@@
 
-\section{Distributional Aspects}
+\section{Cover Time Distribution}
+\subsection{Complete Graph}
 \cite{Du11}
@@
 Call $r$ the number of steps since we began the random walk.
+So that the notation works out more easily,
+set $r=1$ when we begin our walk at $X_0$.
 Let $A_i$ be the event that vertex $i$ is not visited and
@@
 \Var(N_n/n) &= \Var(N_n) / n^2 \nonumber\\
-&\rightarrow (1-2/n)^r - (1-1/n)^{2r} = e^{-2c} - (e^{-c})^2 = 0. \nonumber
+&= (1-2/n)^r - (1-1/n)^{2r} + o(n) \nonumber\\
+&\rightarrow e^{-2c} - (e^{-c})^2 = 0. \nonumber
 \end{align}
@@
 
-We prove the following theorem and then use it to show that $\cov \sim \textrm{Pois}(e^{-x})$.
+We prove the following theorem and then use it to gain insight into
+the distribution of the cover time variable $\cov$.
 \begin{theorem}\label{thm:pois}
@@
 \begin{align}
-p_0(r,n) &= {n \choose 0} 1^r - {n \choose 1} (1-1/n)^r + ... \nonumber\\
-&= \sum_{k=0}^n (-1)^k {n \choose k} (1-k/n)^r. \nonumber
+p_0(r,n) &= {n \choose 0} 1^r - {n \choose 1} (1-1/n)^r + \ldots \nonumber\\
+&= \sum_{k=0}^n (-1)^k {n \choose k} (1-k/n)^r. \label{eqn:p0}
 \end{align}
@@
 \begin{align}
-{n \choose m} \left(1-\frac{m}{n}\right)^r \rightarrow \lambda ^m /m! \nonumber
-\end{align}
-
-We bound the expression from the top and the bottom and use the dominated convergence
-theorem.
+{n \choose m} \left(1-\frac{m}{n}\right)^r \rightarrow \lambda ^m /m! \label{eqn:lim}
+\end{align}
+
+We bound the expression from the top and the bottom and use the squeeze
+theorem to prove the most recent limit.
 We will first show the upper bound.
@@
 \begin{align}
-{n \choose m} \left(1-\frac{m}{n}\right)^r &\leq \frac{n^m}{m!} e^{mr/n} \nonumber \\
-&= \frac{(n e^{r/n})^m} {m!} \nonumber \\
-&\rightarrow \frac{\lambda ^m} {m!} \nonumber
+{n \choose m} \left(1-\frac{m}{n}\right)^r &\leq \frac{n^m}{m!} e^{mr/n} 
+= \frac{(n e^{r/n})^m} {m!} \nonumber \\
+&\rightarrow \frac{\lambda ^m} {m!}. \nonumber
 \end{align}
@@
 Notice that ${n \choose m} \geq (n-m)^m / m!$
-\todo{why?}
 Then
 \begin{align}
-{n \choose m} \left(1-\frac{m}{n}\right)^r &\geq \left(1-\frac{m}{n}\right)^r (n-m)^m / m! \nonumber\\
-&\geq n^m (1 - \frac{m}{n})^r (1- \frac{m}{n})^m  / m! \nonumber
+{n \choose m} \left(1-\frac{m}{n}\right)^r
+&\geq \left(1-\frac{m}{n}\right)^r \frac{(n-m)^m}{m!}
+\left( \frac{n^m}{n^m} \right) \nonumber\\
+&\geq n^m (1 - \frac{m}{n})^r (1- \frac{m}{n})^m  \frac{1}{m!}. \nonumber
 \end{align}
@@
 We use the Taylor series of $\log(1-t)$ for $0 \leq t \leq 1/2$
-to bound the rest of the term.
+to bound the rest.
 Notice that
 \begin{align}
-\log(1-t) &= 0 - t - t^2/2 -t^3/3 - ... \nonumber\\
-&\geq -t -t^2/2(1 + 1/2 + 1/4 + ...) = -t - t^2 \nonumber
+\log(1-t) &= 0 - t - t^2/2 -t^3/3 - \ldots \nonumber\\
+&\geq -t -t^2/2(1 + 1/2 + 1/4 + \ldots) = -t - t^2 \nonumber
 \end{align}
@@
 &= m \log n + r \log\left(1-\frac{m}{n}\right) \nonumber \\
-& \geq m \log n - r m /n - r m/n^2. \nonumber
-\end{align}
-
-\todo{why?}
-Our assumption that $ne^{r/n} \rightarrow \lambda$ implies that
-\begin{align}
-r = n \log n - n \log \lambda + o(n) \nonumber
-\end{align}
-so $r(m/n)^2 \rightarrow 0$.
-Then
-\begin{align}
-rm/n &=m \log n - m \log \lambda + o(n)m/n \nonumber
-\end{align}
-and in particular
-\begin{align}
-m \log \lambda &\rightarrow m \log n - rm/n \nonumber
-\end{align}
-so
+& \geq m \log n - r\frac{m}{n} - r\frac{m}{n^2}. \nonumber
+\end{align}
+
+We use our assumption that $ne^{r/n} \rightarrow \lambda$
+to solve for $r$
+\begin{align}
+e^{\log n + -r/n} &\rightarrow e^{\log \lambda} \nonumber\\
+\log n + -r/n &= \log \lambda + o(n) \nonumber \\
+r &= n \log n - n \log \lambda + o(n). \nonumber
+\end{align}
+Since $r (m/n)^2 \rightarrow 0$ and
+\begin{align}
+\frac{rm}{n} &=m \log n - m \log \lambda + o(n)\frac{m}{n} \nonumber \\
+ m \log n - \frac{rm}{n}&\rightarrow m \log \lambda \nonumber
+\end{align}
+we have
 \begin{align}
 \log \left(n^m\left(1-\frac{m}{n}\right)^r \right)
-&\geq m \log n - rm/n. \nonumber
+&\geq m \log n - \frac{rm}{n} - \frac{rm}{n^2} \rightarrow \log \lambda^m. \nonumber
 \end{align}
@@
 
-Now we put together the pieces.
-To begin,
-\begin{align}
-{ n \choose m } (1-\frac{m}{n})^r \rightarrow \lambda^m /m! \nonumber
-\end{align}
-so
+Now we put the pieces back together.
+The most recent limit implies \cref{eqn:lim}.
+By \cref{eqn:lim} and \cref{eqn:p0},
 \begin{align}
@@
 
-The result holds for
-\begin{align}
-p_0(r,n-m) \rightarrow e^{-\lambda} \nonumber
-\end{align}
+Notice $p_0(r,n-m)$ also goes to $e^{-\lambda}$
 since $m$ is fixed and $(n-m)e^{r/(n-m)} \rightarrow \lambda$.
-
-Finally,
-\begin{align}
-p_m(r,n) &= {n \choose m} (1-\frac{m}{n})^r p_0(r, n-m) \nonumber \\
-&\rightarrow \frac{\lambda^m}{ m!} e^{-\lambda} \nonumber
-\end{align}
-so we have that $N_n \rightarrow \textrm{Pois}(\lambda)$ as claimed.
+Finally, the most recent limit and the equation of $p_m(r,n)$ imply
+\begin{align}
+p_m(r,n) 
+&\rightarrow \frac{\lambda^m}{ m!} e^{-\lambda} \nonumber.
+\end{align}
+$N_n$ approaches a Poisson distribution with mean $\lambda$ as claimed.
 
@@
 
+We use \cref{thm:pois} to find the distribution of the cover time variable $\cov$.
 Set $r = n \log n + nx$.
@@
 
-Consider the cover time variable $\cov$.
-Since $\cov \leq m$ if and only if the first $m$ steps
-of the random walk visit all $n$ vertices, then by \cref{thm:pois},
-\begin{align}
-\pr(\cov \leq r) &\rightarrow e^{-e^{-x}} \nonumber
-\end{align}
-and
-\begin{align}
+Using the fact that $\cov \leq m$ if and only if the first $m$ steps
+of the random walk visit all $n$ vertices
+and $ne^{-r/n} \rightarrow e^{-x}$ as the assumption of \cref{thm:pois},
+\begin{align}
+\pr(\cov \leq r) &\rightarrow e^{-e^{-x}} \nonumber \\
 \pr(\cov - n \log n\leq nx) &\rightarrow e^{-e^{-x}}. \nonumber
@@
 
-\section{Simulation}
+\subsection{Computation}
+\todo{example of probability of birthday cover time in x=2190 vs x=1825 steps}
+
+\todo{simulate cover time a thousand times on complete graph with n = 365}
 

### 2019-04-28 paper.tex
yay empirical!

@@
 \usepackage{cite}
+\usepackage{listings}
+\usepackage[toc, page]{appendix}
 
@@
 There are many connections between electrical networks
-and random walks \cite{DS84}.
+and random walks \cite{Bo98}.
 Physical properties like voltage, current, and resistance
@@
 \end{align}
-We can probabilistically verify that $v_x = \sum_y \pr_{x,y} v_y$
+We can verify that $v_x = \sum_y \pr_{x,y} v_y$
 using first step analysis on the probability of reaching $a$ before $b$.
@@
 \subsection{Outline}
+
+Rely on \cite{BH94}
+Always possible to find cover time but it gets hard as the graph gets bigger
+Structure helps:
+Complete graph,
+Line graph,
+Simple cycle (extended line graph)
+
+In lieu of structure, we want to work with arbitrary graphs
+Rely on \cite{DS84} for commute time relationship
+Rely on \cite{LP17}
+Matthews method is intuitive approach that uses same ideas as complete graph
+Matthews method applied to binary tree with commute time relationship
+Use \cite{AF14}
+Explore the idea of a spanning tree and use it to bound time with commute identity
+
+So far we've only worked with expected time
+\cite{Du11}
+Explore what happens for the variable and it's distribution
 
@@
 \begin{align}
-\tcov &= 1 + \frac{1}{3}\textrm{a} + \frac{2}{3}\textrm{b} \nonumber \\
-\textrm{a} &= 1 + \frac{1}{3}\textrm{a} + \frac{2}{3}\textrm{c} \nonumber \\
-\textrm{b} &= 1 + \frac{1}{2}\textrm{b} + \frac{1}{2}\textrm{e} \nonumber \\
-\textrm{c} &= 1 + 1\textrm{e} \nonumber\\
-\textrm{d} &= 1 + \frac{1}{3}\textrm{a} + \frac{1}{3}\textrm{e} + \frac{1}{3}\textrm{f} \nonumber \\
-\textrm{e} &= 1 + \frac{1}{3}\textrm{c} + \frac{1}{3}\textrm{e} + \frac{1}{3}\dot 0\nonumber \\
-\textrm{f} &= 1 + \frac{1}{2}\textrm{g} + \frac{1}{2}\dot 0\nonumber \\
-\textrm{g} &= 1 + \frac{2}{3}\textrm{f} + \frac{1}{3}\dot 0\nonumber
+&\tcov = 1 + \frac{1}{3}\textrm{a} + \frac{2}{3}\textrm{b}
+&\textrm{a} = 1 + \frac{1}{3}\textrm{a} + \frac{2}{3}\textrm{c} \nonumber \\
+&\textrm{b} = 1 + \frac{1}{2}\textrm{b} + \frac{1}{2}\textrm{e}
+&\textrm{c} = 1 + 1\textrm{e} \nonumber \\
+&\textrm{d} = 1 + \frac{1}{3}\textrm{a} + \frac{1}{3}\textrm{e} + \frac{1}{3}\textrm{f}
+&\textrm{e} = 1 + \frac{1}{3}\textrm{c} + \frac{1}{3}\textrm{e} + \frac{1}{3}\dot 0\nonumber \\
+&\textrm{f} = 1 + \frac{1}{2}\textrm{g} + \frac{1}{2}\dot 0
+&\textrm{g} = 1 + \frac{2}{3}\textrm{f} + \frac{1}{3}\dot 0\nonumber \\
 \end{align}
@@
 \subsection{Commute Time Identity} \label{sec:commute}
-We use the electrical network analysis in \cref{sec:electric} to 
+\cite{DS84} We use the electrical network analysis in \cref{sec:electric} to 
 prove the commute time identity so we may use it to help us bound
@@
 
-\section{Cover Time Distribution}
+\section{Cover Time Distributions}
 \subsection{Complete Graph}
@@
 \pr(\cov \leq r) &\rightarrow e^{-e^{-x}} \nonumber \\
-\pr(\cov - n \log n\leq nx) &\rightarrow e^{-e^{-x}}. \nonumber
-\end{align}
-
-\subsection{Computation}
-\todo{example of probability of birthday cover time in x=2190 vs x=1825 steps}
-
-\todo{simulate cover time a thousand times on complete graph with n = 365}
-
-\cite{Bo98}
-\cite{Gr10}
+\pr(\cov - n \log n\leq nx) &\rightarrow e^{-e^{-x}}. \label{eqn:dist}
+\end{align}
+
+\subsection{The Birthday Problem}
+Consider a complete graph (with self-edges) and 365 vertices.
+We may think of the cover time variable of this graph as the number of people
+until every birthday is represented.
+We call this the birthday problem.
+
+We use \cref{eqn:dist} to calculate the probability
+that all birthdays are represented in populations of 
+size $r=2190$ and $r=1825$, respectively.
+The number of vertices $n$ is 365 so $n\log n = 2153$.
+It follows that
+\begin{align}
+\pr(\cov \leq 2190) &= \pr \left(\frac{\cov - 2153}{365} \leq
+\frac{37}{365}\right) \nonumber \\
+&\approx e^{-e^{-.10137}} \approx 0.40511 \nonumber
+\end{align}
+but 
+\begin{align}
+\pr(\cov \leq 1825) &= \pr \left(\frac{\cov - 2153}{365} \leq
+\frac{328}{365}\right) \nonumber \\
+&\approx e^{-e^{-.8.9863}} \approx 0.08576. \nonumber
+\end{align}
+
+There appears to be a critical stage where it quickly becomes very likely
+that all birthdays have been represented.
+\cref{fig:birthday} shows the cumulative distribution of the birthday problem.
+
+\begin{figure}[ht]
+\centering
+\begin{tikzpicture}[scale=.5]
+\node (graph) at (0,0) {\includegraphics[scale=.25, height=10cm]{birthdays}};
+\node (title) at (1, 10) {Cover Times of the Birthday Problem (1000 trials)};
+\node[rotate=90] (ylabel) at (-13,2) {$\pr(\cov \leq r)$};
+\node (xlabel) at (0,-9) {$r$};
+\end{tikzpicture}
+\caption{The cumulative distribution of the birthday problem.
+The red line denotes the empirical distribution from 1000 trials.
+The blue line denotes the distribution from \cref{eqn:dist}.}\label{fig:birthday}
+\end{figure}
+
+%\cite{Gr10}
 
@@
 
+\newpage
+\begin{appendices}
+\subsection{Birthday Problem}
+\lstinputlisting{computation.R}
+\end{appendices}
+
 \end{document}

### 2019-04-28 computation.R

@@ -1,0 +1,40 @@
+# R. Teal Witter
+# Math 710 Spring 2019
+# Cover Time of Birthdays
+library(tidyverse)
+library(ggplot2)
+
+trials <- 1000         # Number of trials
+n <- 365               # Number of 'vertices' to cover
+cover_times <- c()
+for (i in 1:trials) {
+  x <- 0
+  birthdays <- 1:n # Unvisited birthdays
+  # Count number of people until every birthday is covered
+  while (length(birthdays) > 0) {
+    birthday <- sample(1:n, 1, replace=TRUE)      # Uniform birthdays
+    birthdays <- birthdays[birthdays != birthday] # Remove birthday
+    x <- x+1                                      # Count steps
+  }
+  cover_times[i] <- x
+}
+
+cover_times2 <- data.frame(cover_times)
+
+cover_times3 <- cover_times2%>% # Append percentiles
+  mutate(percentile=ecdf(cover_times)(cover_times))
+
+cdf <- function(r) { # Analytical result of cover time CDF
+  x <- (r - n * log(n)) / n
+  return (exp(-exp(-x)))
+}
+
+cdf(2190) # Probability all birthdays represented with 2190 people
+cdf(1825) # Probability all birthdays represented with 1825 people
+
+cover_times3 %>% # Graph of birthday cover times
+  ggplot() + theme_classic()+
+  geom_line(aes(x=cover_times3$cover_times, y=cover_times3$percentile),
+            color="red", alpha=.5, size=3) +
+  stat_function(fun = cdf, color="blue", alpha=1, size=1) +
+  ylab("") + xlab("")

### 2019-04-29 paper.tex
abstract, outline and general intro

@@
 
-\abstract{\todo{abstract}}
+\abstract{
+The cover time of a graph is the time it takes for a random walk to
+visit all of its vertices.
+We provide a detailed overview for a variety of cover time topics:
+We begin by investigating the cover time of small and structured graphs but
+quickly need a more robust strategy for larger, unstructured ones.
+We apply more general probablistic arguments and an important electrical
+network relationship to identify bounds.
+Finally, we describe the limiting distribution of the cover time of
+complete graphs with self-edges and apply our analysis to an intuitive example.
+}
 
@@
 
-\todo{write general introduction to cover times}
-"white screen" problem
-numerous applications
-many mathematical tools
-
-\subsection{Motivation}
-\todo{write about applications}
-universal travel sequences
-graph connectivity
-protocol testing
-birthday problem
-coupon collectors
+We begin by describing two intuitive examples of cover time problems.
+Consider a coupon collector who opens a single box of cereal everyday.
+In each box, is one of $n$ distinct coupons.
+How many days until our collector has collected at least one of every coupon?
+(The coupon collector's problem corresponds to the cover time of the complete
+graph with self-edges.)
+
+Next consider a similar scenario called the birthday problem.
+How many people would we need to ensure that every day of the year
+(excluding February 29) is represented as a birthday?
+A lower bound is certainly 365 but it turns out that there is no upper bound.
+
+Other applications of cover times include universal travel sequences,
+graph connectivity algorithms, and protocol testing.
+
+In this paper, we use a variety of strategies like first step analysis
+and draw on several related topics such as electrical networks to rigorously
+investigate cover times.
 
 \subsection{Definitions}
-We consider an undirected, connected graph $G$ without self loops or multi-edges.
+We consider an undirected, connected graph $G$ without self- or multi-edges.
 Let $V(G)$ be the set of vertices and let $E(G)$ be the set of edges on $G$.
 Then $n$ is the number of vertices $|V(G)|$.
-We say $i\sim j$ for $i$ and $j$ in the vertex set $V(G)$ if $(i,j)$ in $E(G)$.
+We say $i\sim j$ for $i$ and $j$ in the vertex set $V(G)$ if $(i,j)$ is in $E(G)$.
 Assume that each vertex is accessible from every other vertex.
-That is, there is a set of edges from any $x$ to any $y$.
+That is, there is a set of edges connecting any $x$ to any $y$.
 %Without loss of generality, we label the vertices $\{1, 2, 3, ..., n\}$.
 
-Let $C_{i,j}$ be the non-negative weight of the edge between vertices $i$ and $j$.
+Let $C_{i,j}=C_{j,i}$ be the non-negative weight of the edge between vertices $i$ and $j$.
 We will mostly consider unweighted graphs
-with $C_{i,j} = 1$ if $i \sim j$ and $C_{i,j} = 0$ otherwise.
+such that $C_{i,j} = 1$ if $i \sim j$ and $C_{i,j} = 0$ otherwise.
 
@@
 Call $X_t$ the vertex that the walk is on at time $t$.
-The random walker begins at vertex $X_0$.
-At each step, the walker at vertex $i$ moves to neighboring vertex
-$j$ with probability $c(i,j)/c(i)$.
+The random walk begins at vertex $X_0$.
+At each step, the walk at vertex $i$ moves to neighboring vertex
+$j$ with probability $C(i,j)/C(i)$.
 
@@
 Probabilistically, of course $v_a = 1$ and $v_b=0$.
-Voltage is a harmonic function so the voltage at every vertex $x$ in 
-$V(G) \textbackslash \{a,b\}$ is determined by the boundary values
-(at $a$ and $b$).
+The voltage at every vertex $x$ in  $V(G) \textbackslash \{a,b\}$
+is determined by the boundary values (at $a$ and $b$).
 
@@
 
-Rely on \cite{BH94}
-Always possible to find cover time but it gets hard as the graph gets bigger
-Structure helps:
-Complete graph,
-Line graph,
-Simple cycle (extended line graph)
-
-In lieu of structure, we want to work with arbitrary graphs
-Rely on \cite{DS84} for commute time relationship
-Rely on \cite{LP17}
-Matthews method is intuitive approach that uses same ideas as complete graph
-Matthews method applied to binary tree with commute time relationship
-Use \cite{AF14}
-Explore the idea of a spanning tree and use it to bound time with commute identity
-
-So far we've only worked with expected time
-\cite{Du11}
-Explore what happens for the variable and it's distribution
-
-\todo{outline of each section and subsections}
-
-\section{Cover Times of Structured Graphs}
-
-\subsection{Small Example}
+We begin in \cref{sec:small_example}.
+(\cref{sec:structured_graphs} primarily relies on \cite{BH94}.)
+We see that it is always possible to exactly calculate the cover time
+of graph but it is in general very difficult to do so.
+For the remainder of this section, we investigate
+structured graphs that are exceptions to the rule:
+the complete graph, line graphs, and simple cycles.
+
+\cref{sec:bounds} deals with the large or unstructured graphs 
+for which we must use bounds.
+We begin by establishing an important identity between
+commute times and effective resistance in \cref{sec:commute}.
+(Our electrical network analysis is an extension of \cite{DS84}
+and we use \cite{LP17} for the next two subsections.)
+We take our strategy for finding the cover time of the complete graph
+from \cref{sec:complete} and apply it to general graphs in \cref{sec:matthews}.
+In \cref{sec:binary}, we use both the commute time identity and the Matthews Method
+to bound the cover time of a binary tree.
+In \cref{sec:spanning}, we follow \cite{AF14} and use the idea of a spanning tree
+as well as the commute time identity to develop another bound for general graphs.
+
+Up until \cref{sec:dist}, we have only considered the expected cover time.
+We now delve into the distribution of the cover time of a complete graph.
+We draw on \cite{Du11} and find that the cover time variable approaches a Poisson
+distribution.
+In \cref{sec:birthday}, we apply \cref{sec:complete_dist} to the birthday problem.
+(The R code for our computations and \cref{fig:birthday} can be found in \cref{app:birthday}.)
+
+\section{Cover Times of Structured Graphs}\label{sec:structured_graphs}
+
+\subsection{Small Example}\label{sec:small_example}
 In general, it is always possible to find the exact cover time
@@
 
-\subsection{Complete Graph \label{sec:complete}}
+\subsection{Complete Graph}\label{sec:complete}
 We call the graph with an edge between each pair of vertices the
@@
 The difference between the coupon collecting problem and the complete graph
-is that we now have self-edges.
-Before, we had to leave our current vertex at each step.
+is that we have self-edges
+whereas before we had to leave our current vertex at each step.
 Now, we can stay in the same vertex (provided our collector found the same coupon
@@
 
-\subsection{Line Graph}
+\subsection{Line Graph}\label{sec:line_graph}
 A line graph is a set of vertices connected in a line.
@@
 
-\subsection{Simple Cycle}
+\subsection{Simple Cycle}\label{sec:simple_cycle}
 
@@
 
-\section{Bounds}
+\section{Bounds}\label{sec:bounds}
 
@@
 
-\subsection{Matthews Method}
+\subsection{Matthews Method}\label{sec:matthews}
 We have seen that it is in general very hard
@@
 
-\subsection{Matthews Method on Binary Trees}
+\subsection{Matthews Method on Binary Trees}\label{sec:binary}
 
@@
 
-\subsection{Spanning Tree Argument}
+\subsection{Spanning Tree Argument}\label{sec:spanning}
 \cite{AF14}
@@
 
-\section{Cover Time Distributions}
-\subsection{Complete Graph}
+\section{Cover Time Distributions}\label{sec:dist}
+\subsection{Complete Graph}\label{sec:complete_dist}
 \cite{Du11}
@@
 
-\subsection{The Birthday Problem}
+\subsection{The Birthday Problem}\label{sec:birthday}
 Consider a complete graph (with self-edges) and 365 vertices.
@@
 
-There appears to be a critical stage where it quickly becomes very likely
+There appears to be a critical threshold where it quickly becomes very likely
 that all birthdays have been represented.
-\cref{fig:birthday} shows the cumulative distribution of the birthday problem.
+\cref{fig:birthday} verifies our intuition.
 
@@
 \begin{appendices}
-\subsection{Birthday Problem}
+\subsection{Birthday Problem}\label{app:birthday}
 \lstinputlisting{computation.R}

### 2019-04-29 paper.tex
minor

@@
 \abstract{
-The cover time of a graph is the time it takes for a random walk to
-visit all of its vertices.
-We provide a detailed overview for a variety of cover time topics:
+The cover time of a graph is the number of steps of a
+discrete random walk until every vertex has been visited at leastonce.
+This senior work provides a detailed overview
+of a variety of cover time topics.
 We begin by investigating the cover time of small and structured graphs but
-quickly need a more robust strategy for larger, unstructured ones.
+quickly find that we need
+require a less precise strategy for larger, unstructured ones.
 We apply more general probablistic arguments and an important electrical
-network relationship to identify bounds.
+network relationship to identify bounds for arbitrary graphs.
 Finally, we describe the limiting distribution of the cover time of
-complete graphs with self-edges and apply our analysis to an intuitive example.
+complete graphs with self-edges.
 }

### 2019-04-29 computation.R

@@ -34,7 +34,7 @@ cdf(1825) # Probability all birthdays represented with 1825 people
 
 cover_times3 %>% # Graph of birthday cover times
   ggplot() + theme_classic()+
+  stat_function(fun = cdf, color="blue", alpha=.5, size=2) +
   geom_line(aes(x=cover_times3$cover_times, y=cover_times3$percentile),
-            color="red", alpha=.5, size=3) +
-  stat_function(fun = cdf, color="blue", alpha=1, size=1) +
+            color="red", alpha=.5, size=2) +
   ylab("") + xlab("")

### 2019-04-30 paper.tex
dots and indices

@@
 \begin{align}
-\tcov&= \E[X_1+X_2+X_3+\ldots+X_{n+1}] = \sum_{i=1}^n \E[X_i] \nonumber
+\tcov&= \E[X_1+X_2+X_3+\cdots+X_{n+1}] = \sum_{i=1}^n \E[X_i] \nonumber
 \end{align}
@@
 This is because there are $n-i$ unvisited vertices and a total of $n-1$ adjacent vertices.
-It follows that $\E[X_i] = (ln-1)(n-i)$.
+It follows that $\E[X_i] = (n-1)(n-i)$.
 Then
 \begin{align}
-\tcov&=   \sum_{i=1}^n \frac{n-1}{n-i} \nonumber \\
-&=  (n-1) \left(\frac{1}{n-1}+\frac{1}{n-2}+\ldots+1\right). \nonumber
+\tcov&=   \sum_{i=1}^{n-1} \frac{n-1}{n-i} \nonumber \\
+&=  (n-1) \left(\frac{1}{n-1}+\frac{1}{n-2}+\cdots+1\right). \nonumber
 \end{align}
@@
 \begin{align}
-\tcov&=  r \left(\frac{1}{r}+\frac{1}{r-1}+\ldots+1\right). \nonumber
+\tcov&=  r \left(\frac{1}{r}+\frac{1}{r-1}+\cdots+1\right). \nonumber
 \end{align}
@@
 \begin{align}
-\tcov&= 2(n-1) \left(\frac{1}{n-1}+\frac{1}{n-2}+\ldots+1\right). \nonumber
+\tcov&= 2(n-1) \left(\frac{1}{n-1}+\frac{1}{n-2}+\cdots+1\right). \nonumber
 \end{align}
@@
 \begin{align}
-(e_i - e_1) &= (i-1) e_1 - 2[1+2+\ldots+i-1] \nonumber \\
+(e_i - e_1) &= (i-1) e_1 - 2[1+2+\cdots+i-1] \nonumber \\
 e_i &= i(N-1) - 2 \frac{(i-1)i}{2} \nonumber\\
@@
 \begin{align}
-\E_0[T_N] &= \E_0[T_1] + \E_1[T_2] + \ldots + \E_{i}[T_{i+1}] + \ldots + \E_{N-1}[T_N]. \nonumber
+\E_0[T_N] &= \E_0[T_1] + \E_1[T_2] + \cdots + \E_{i}[T_{i+1}] + \cdots + \E_{N-1}[T_N]. \nonumber
 \end{align}
@@
 \begin{align}
-\E_0[T_N] &= 1 + 3 + \ldots + 2i - 1 + \ldots + 2(N-1) -1 \nonumber \\
+\E_0[T_N] &= 1 + 3 + \cdots + 2i - 1 + \cdots + 2(N-1) -1 \nonumber \\
 &= N^2 \nonumber
@@
 
-Let $\{a, a+1, \dots, b-1, b\}$ 
+Let $\{a, a+1, \ldots, b-1, b\}$ 
 denote the set of vertices we have visited.
@@
 \begin{align}
-\tcov &= \E[T_n] = \E[(T_2 - T_1) + (T_3 - T_2) + \dots + 
-(T_k - T_{k-1}) + \dots + (T_n - T_{n-1})] \nonumber
+\tcov &= \E[T_n] = \E[(T_2 - T_1) + (T_3 - T_2) + \cdots + 
+(T_k - T_{k-1}) + \cdots + (T_n - T_{n-1})] \nonumber
 \end{align}
@@
 \begin{align}
-\tcov &=  (\E[T_2] - \E[T_1]) + \dots +
-(\E[T_{k+1}] - \E[T_{k}]) + \dots + (\E[T_n] - \E[T_{n-1}]) \nonumber\\
-&= 1 + 2 + \dots + k-1 + \dots + n-1  = \frac{1}{2}n(n-1). \nonumber
+\tcov &=  (\E[T_2] - \E[T_1]) + \cdots +
+(\E[T_{k+1}] - \E[T_{k}]) + \cdots + (\E[T_n] - \E[T_{n-1}]) \nonumber\\
+&= 1 + 2 + \cdots + k-1 + \cdots + n-1  = \frac{1}{2}n(n-1). \nonumber
 \end{align}
@@
 \begin{align}
-\tcov &\leq \hit \left(1 + \frac{1}{2} + \frac{1}{3} + \ldots + \frac{1}{n-1} \right). \nonumber
+\tcov &\leq \hit \left(1 + \frac{1}{2} + \frac{1}{3} + \cdots + \frac{1}{n-1} \right). \nonumber
 \end{align}
@@
 \begin{proof}
-Without loss of generality, label the vertices $\{1, 2, \ldots, n\}$.
+Without loss of generality, label the vertices $\{1, 2, \dots, n\}$.
 We may assume that the walk started at vertex $n$.
@@
 \tcov &= \E_n[{T_{n-1}}]  \nonumber \\
-&= \E_n[T_1 + (T_2 - T_1) + \ldots + 
-(T_k - T_{k-1}) + \ldots + (T_{n-1} - T_{n-2})] . \nonumber
+&= \E_n[T_1 + (T_2 - T_1) + \cdots + 
+(T_k - T_{k-1}) + \cdots + (T_{n-1} - T_{n-2})] . \nonumber
 \end{align}
@@
 Now consider the $k^{th}$ term of the sum for $1 < k \leq n-1$.
-By conditional expectation,
-
+By total expectation,
 \begin{align}
@@
 \begin{align}
-\tcov \leq \hit \left( 1+ \frac{1}{2} + \ldots + \frac{1}{k} 
-+ \ldots + \frac{1}{n-1} \right). \nonumber
+\tcov \leq \hit \left( 1+ \frac{1}{2} + \cdots + \frac{1}{k} 
++ \cdots + \frac{1}{n-1} \right). \nonumber
 \end{align}
@@
 \begin{align}
-\tcov &\geq \tmina \left(1 + \frac{1}{2} + \frac{1}{3} + \ldots +
+\tcov &\geq \tmina \left(1 + \frac{1}{2} + \frac{1}{3} + \cdots +
 \frac{1}{|A| -1} \right). \nonumber
@@
 
-Let $T_k$ be the first time that vertices $\sigma_1, \sigma_2, \ldots, \sigma_k$
+Let $T_k$ be the first time that vertices $\sigma_1, \sigma_2, \cdots, \sigma_k$
 have all been visited.
@@
 \begin{align}
-\tcov &\geq \E_x[T_1 + (T_2 - T_1) + \ldots + 
-(T_k - T_{k-1}) + \ldots + (T_{|A|} - T_{|A|-1})] . \nonumber
+\tcov &\geq \E_x[T_1 + (T_2 - T_1) + \cdots + 
+(T_k - T_{k-1}) + \cdots + (T_{|A|} - T_{|A|-1})] . \nonumber
 \end{align}
@@
 Now consider the $k^{th}$ term of the sum for $k > 1$.
-By conditional expectation,
+By total expectation,
 \begin{align}
@@
 \begin{align}
-\tcov &\geq \tmina \left( 1 - \frac{1}{|A|}+ \frac{1}{2} + \ldots + \frac{1}{k} 
-+ \ldots + \frac{1}{|A|-1} + \frac{1}{|A|}\right). \nonumber \\
-&= \tmina \left( 1 + \frac{1}{2} + \ldots + \frac{1}{k} 
-+ \ldots + \frac{1}{|A|-1} \right). \nonumber
+\tcov &\geq \tmina \left( 1 - \frac{1}{|A|}+ \frac{1}{2} + \cdots + \frac{1}{k} 
++ \cdots + \frac{1}{|A|-1} + \frac{1}{|A|}\right). \nonumber \\
+&= \tmina \left( 1 + \frac{1}{2} + \cdots + \frac{1}{k} 
++ \cdots + \frac{1}{|A|-1} \right). \nonumber
 \end{align}
@@
 from the root and no children if it is a leaf (distance $k$ from the root).
-There are $n = 1 + 2 + 4 + \ldots + 2^k = 2^{k+1} - 1$ vertices.
+There are $n = 1 + 2 + 4 + \cdots + 2^k = 2^{k+1} - 1$ vertices.
 
@@
 \begin{align}
-\tcov &\leq 2(n-1)k\left(1 + \frac{1}{2} + \ldots + \frac{1}{n} \right) \nonumber \\
+\tcov &\leq 2(n-1)k\left(1 + \frac{1}{2} + \cdots + \frac{1}{n} \right) \nonumber \\
 &\approx (2 - \frac{2}{n}) \cdot n k \log n \approx (2 - \frac{2}{n}) n k \log 2^{k+1} -1 \nonumber \\
@@
 \begin{align}
-\tcov &\geq 2 (n-1)(k-h+1)\left(1 + \frac{1}{2} + \ldots + \frac{1}{2^h -1} \right) \nonumber \\
+\tcov &\geq 2 (n-1)(k-h+1)\left(1 + \frac{1}{2} + \cdots + \frac{1}{2^h -1} \right) \nonumber \\
 &\approx (2 + o(1)) \cdot n (k-h) h \log 2 \nonumber.
@@
 \begin{align}
-p_0(r,n) &= {n \choose 0} 1^r - {n \choose 1} (1-1/n)^r + \ldots \nonumber\\
+p_0(r,n) &= {n \choose 0} 1^r - {n \choose 1} (1-1/n)^r + \cdots \nonumber\\
 &= \sum_{k=0}^n (-1)^k {n \choose k} (1-k/n)^r. \label{eqn:p0}
@@
 \begin{align}
-\log(1-t) &= 0 - t - t^2/2 -t^3/3 - \ldots \nonumber\\
-&\geq -t -t^2/2(1 + 1/2 + 1/4 + \ldots) = -t - t^2 \nonumber
+\log(1-t) &= 0 - t - t^2/2 -t^3/3 - \cdots \nonumber\\
+&\geq -t -t^2/2(1 + 1/2 + 1/4 + \cdots) = -t - t^2 \nonumber
 \end{align}

### 2019-05-07 paper.tex
talk :)

@@
 \DeclareMathOperator{\Var}{\mathrm{Var}}         % variance
-\DeclareMathOperator{\I}{\mathbb{1}}         % variance
-\DeclareMathOperator{\pr}{\mathrm{P}}		     % expected value
+\DeclareMathOperator{\I}{\mathbb{1}}             % probability
+\DeclareMathOperator{\pr}{\mathrm{P}}		     % probability 
 \DeclareMathOperator{\cov}{\uptau_\textrm{cov}}  % cover time variable
@@
 \abstract{
-The cover time of a graph is the number of steps of a
-discrete random walk until every vertex has been visited at leastonce.
-This senior work provides a detailed overview
-of a variety of cover time topics.
+The cover time of a graph is the number of steps a 
+discrete random walk takes to visit vertex at least once.
 We begin by investigating the cover time of small and structured graphs but
-quickly find that we need
-require a less precise strategy for larger, unstructured ones.
-We apply more general probablistic arguments and an important electrical
-network relationship to identify bounds for arbitrary graphs.
+quickly find that our precise strategy fails
+for larger, unstructured ones.
+To bound the cover time on arbitrary graphs,
+we apply more general probablistic arguments and an important electrical
+network identity.
 Finally, we describe the limiting distribution of the cover time of
-complete graphs with self-edges.
+complete graphs with self-edges and apply our analysis to an intuitive example.
 }
@@
 \newpage
-\section{Introduction and Background}
-
-We begin by describing two intuitive examples of cover time problems.
-Consider a coupon collector who opens a single box of cereal everyday.
-In each box, is one of $n$ distinct coupons.
-How many days until our collector has collected at least one of every coupon?
-(The coupon collector's problem corresponds to the cover time of the complete
-graph with self-edges.)
-
-Next consider a similar scenario called the birthday problem.
+\section{Introduction and Background}\label{sec:intro}
+
+To introduce the concept of a cover time, we begin by describing two intuitive examples.
+Consider a coupon collector who receives one of $r$ distinct coupons
+in the mail everyday.
+For example if $r=3$, the collector may receive coupon 1 today, coupon 3 tomorrow,
+coupon 1 (again) the next day, and finally coupon 2 the following day.
+For arbirtrary $r$, we ask how many days until our 
+collector has collected at least one of every coupon?
+(To solve the coupon collector problem we will frame it in terms 
+of the complete graph with self-edges.)
+
+Next consider a particular case of coupon collecting called the birthday problem.
 How many people would we need to ensure that every day of the year
 (excluding February 29) is represented as a birthday?
-A lower bound is certainly 365 but it turns out that there is no upper bound.
+A lower bound is certainly 365 but there is no upper bound.
 
@@
 \subsection{Definitions}
-We consider an undirected, connected graph $G$ without self- or multi-edges.
+We consider an undirected, connected graph $G$ without multi-edges.
 Let $V(G)$ be the set of vertices and let $E(G)$ be the set of edges on $G$.
@@
 That is, there is a set of edges connecting any $x$ to any $y$.
-%Without loss of generality, we label the vertices $\{1, 2, 3, ..., n\}$.
 
@@
 			\path[->] (m) edge (b);
-			\path[->] (a) edge[loop above] (a);
+			\path[->] (a) edge[loop above, distance=6mm] (a);
 			\path[->] (a) edge (c);
@@
 			\path[->] (e) edge[bend left] (c);
-			\path[->] (e) edge[loop above] (e);
+			\path[->] (e) edge[loop above, distance=6mm] (e);
 			\path[->] (f) edge[bend left] (g);
@@
 &\textrm{f} = 1 + \frac{1}{2}\textrm{g} + \frac{1}{2}\dot 0
-&\textrm{g} = 1 + \frac{2}{3}\textrm{f} + \frac{1}{3}\dot 0\nonumber \\
+&\textrm{g} = 1 + \frac{2}{3}\textrm{f} + \frac{1}{3}\dot 0\nonumber
 \end{align}
@@
 \begin{align}
-\tcov&= \E[X_1+X_2+X_3+\cdots+X_{n+1}] = \sum_{i=1}^n \E[X_i] \nonumber
+\tcov&= \E[X_1+X_2+X_3+\cdots+X_{n-1}] = \sum_{i=1}^{n-1} \E[X_i] \nonumber
 \end{align}
@@
 This is because there are $n-i$ unvisited vertices and a total of $n-1$ adjacent vertices.
-It follows that $\E[X_i] = (n-1)(n-i)$.
+It follows that $\E[X_i] = (n-1)/(n-i)$.
 Then
@@
 A natural interpretation of the cover time on a complete graph is 
-the so-called coupon collecting problem.
-There are $r$ different coupons that are randomly packaged in cereal boxes.
-An avid fan buys a box of cereal every day.
-We want to know how many days until the fan has collected each coupon.
+the coupon collector problem we introduced in \cref{sec:intro}.
+There are $r$ distinct coupons one of which arrives in the mail everyday.
+We want to know how many days until the collector has collected each coupon.
 The strategy is to think of every coupon as a vertex on the complete graph.
 We then move from vertex to vertex with uniform probability.
-The difference between the coupon collecting problem and the complete graph
-is that we have self-edges
+The difference between the coupon collector problem and the complete graph
+is that we now have self-edges
 whereas before we had to leave our current vertex at each step.
-Now, we can stay in the same vertex (provided our collector found the same coupon
+That is, we can stay in the same vertex (if the collector receives the same coupon
 two days in a row).
@@
 \sum_{i=1}^k \E_n[T_k - T_{k-1} | L(k) = \sigma_i]
-P(L_k = \sigma_i). \nonumber 
+\pr(L_k = \sigma_i). \nonumber 
 \end{align}
@@
 \E_n[T_k - T_{k-1} | L(k) = \sigma_k]
-P(L_k = \sigma_k). \nonumber 
+\pr(L_k = \sigma_k). \nonumber 
 \end{align}
@@
 \begin{align}
-P(A_i) = (1-1/n)^r \nonumber
+\pr(A_i) = (1-1/n)^r \nonumber
 \end{align}
@@
 ne^{-r/n} &= n e ^{- \log n - x} \nonumber \\
-&= n e {- \log n} e^ {- x} = e^{-x}.\nonumber
+&= n e^{- \log n} e^ {- x} = e^{-x}.\nonumber
 \end{align}

### 2019-05-07 talk.tex
talk :)

\documentclass[12pt]{beamer}

\usepackage{tikz}
\usepackage{graphicx}
\usepackage[T1]{fontenc}
\usepackage{amsmath}
\usepackage{multicol}
\usetikzlibrary{graphs, graphs.standard}

\DeclareMathOperator{\E}{\textrm{E}}		     % expected value
\DeclareMathOperator{\pr}{\mathrm{P}}		     % probability

\title{Cover Times of Random Walks}
\author{R. Teal Witter}
\date{May 9, 2019}

\begin{document}

\frame{\titlepage}

\AtBeginSection[]
{
  \begin{frame}<beamer>
    \frametitle{Overview}
    \tableofcontents[currentsection]
  \end{frame}
}

\section{Introduction}

\begin{frame} \only<1>{\frametitle{A Graph}}

\only<2->{\frametitle{Random Walks}}

\centering
\begin{center}
	\begin{tikzpicture}[scale=.9] [
        > = stealth, % arrow head style
        shorten > = 1pt, % don't touch arrow head to node
        %auto,
        node distance = 3cm, % distance between nodes
        semithick % line style
    ]

		\tikzstyle{edge}=[draw,line width = .5pt,-,black!100]

		\node (m) at (0,0) {
			\begin{tikzpicture}[scale = 3]
			    \tikzstyle{edge}=[draw,line width = .5pt,-,black!100]
			    \tikzstyle{current}=[draw,circle,fill=black,scale=.5]
			    \tikzstyle{visited}=[draw,circle,fill=white,scale=.5]
			    \draw[edge] (0,0) -- (0,1);
			    \draw[edge] (0,0) -- (1,0);
			    \draw[edge] (0,1) -- (1,0);
			    \draw[edge] (0,1) -- (1,1);
			    \draw[edge] (1,1) -- (1,0);
			    \node (bl) at (0,0) {};
			    \node[current] (tl) at (0,1) {};
			    \only<1>{\node[current] (2) at (1,1) {};}
		        \only<1>{\node[current] (3) at (1,0) {};}
		        \only<1>{\node[current] (4) at (0,0) {};}
			    \node (br) at (1,0) {};
			    \node (tr) at (1,1) {};;
			\end{tikzpicture}
		};
		\pause
		\pause
		\node (a) at (4,3) {
			\begin{tikzpicture}[scale = 1]
			    \tikzstyle{edge}=[draw,line width = .5pt,-,black!100]
			    \tikzstyle{current}=[draw,circle,fill=black,scale=.5]
			    \tikzstyle{visited}=[draw,circle,fill=white,scale=.5]
			    \draw[edge] (0,0) -- (0,1);
			    \draw[edge] (0,0) -- (1,0);
			    \draw[edge] (0,1) -- (1,0);
			    \draw[edge] (0,1) -- (1,1);
			    \draw[edge] (1,1) -- (1,0);
			    \node (bl) at (0,0) {};
			    \node[current] (br) at (1,1) {};
			    \node (tr) at (1,1) {};;
			\end{tikzpicture}
		};
		\node (b) at (4,0) {
			\begin{tikzpicture}[scale = 1]
			    \tikzstyle{edge}=[draw,line width = .5pt,-,black!100]
			    \tikzstyle{current}=[draw,circle,fill=black,scale=.5]
			    \tikzstyle{visited}=[draw,circle,fill=white,scale=.5]
			    \draw[edge] (0,0) -- (0,1);
			    \draw[edge] (0,0) -- (1,0);
			    \draw[edge] (0,1) -- (1,0);
			    \draw[edge] (0,1) -- (1,1);
			    \draw[edge] (1,1) -- (1,0);
			    \node (bl) at (0,0) {};
			    \node (br) at (1,0) {};
			    \node[current] (tr) at (1,0) {};;
			\end{tikzpicture}
		};
	    \node (c) at (4,-3) {
			\begin{tikzpicture}[scale = 1]
			    \tikzstyle{edge}=[draw,line width = .5pt,-,black!100]
			    \tikzstyle{current}=[draw,circle,fill=black,scale=.5]
			    \tikzstyle{visited}=[draw,circle,fill=white,scale=.5]
			    \draw[edge] (0,0) -- (0,1);
			    \draw[edge] (0,0) -- (1,0);
			    \draw[edge] (0,1) -- (1,0);
			    \draw[edge] (0,1) -- (1,1);
			    \draw[edge] (1,1) -- (1,0);
			    \node (bl) at (0,0) {};
			    \node[current] (tr) at (0,0) {};;
			\end{tikzpicture}
		};
		\path[->] (m) edge (a);
		\path[->] (m) edge (b);
		\path[->] (m) edge (c);
		\pause
		\path[->] (m) edge node[above] {$\frac{1}{3}$} (a);	
	    \path[->] (m) edge node[below] {$\frac{1}{3}$} (b); 
	    \path[->] (m) edge node[below] {$\frac{1}{3}$} (c); 
	\end{tikzpicture}
\end{center}
\end{frame}

\begin{frame}{Cover Times}
\centering
How many steps does a random walk take to visit every vertex?
\end{frame}

\begin{frame}{Coupon Collector}
\centering
A collector receives one of $n$ possible coupons in the mail everyday.
How long until all $n$ coupons have been collected?
\end{frame}

\begin{frame}{Birthday Problem}
\centering
How many people do we need for each birthday (excluding February 29)
to be represented?
\end{frame}

\section{Expected Cover Time of a Small Graph}

\begin{frame}{A Small Graph}
\centering
\begin{center}
	\begin{tikzpicture}[scale=.9] [
        > = stealth, % arrow head style
        shorten > = 1pt, % don't touch arrow head to node
        %auto,
        node distance = 3cm, % distance between nodes
        semithick % line style
    ]

		\tikzstyle{edge}=[draw,line width = .5pt,-,black!100]

		\node (m) at (-1.2,1.75) {
			\begin{tikzpicture}[scale = 3]
			    \tikzstyle{edge}=[draw,line width = .5pt,-,black!100]
			    \tikzstyle{current}=[draw,circle,fill=black,scale=.5]
			    \tikzstyle{visited}=[draw,circle,fill=white,scale=.5]
			    \draw[edge] (0,0) -- (0,1);
			    \draw[edge] (0,0) -- (1,0);
			    \draw[edge] (0,1) -- (1,0);
			    \draw[edge] (0,1) -- (1,1);
			    \draw[edge] (1,1) -- (1,0);
			    \node (l) at (.5, 1.1) {$t_{cov}$};
			    \node (bl) at (0,0) {};
			    \node[current] (tl) at (0,1) {};
			    \node (br) at (1,0) {};
			    \node (tr) at (1,1) {};;
			\end{tikzpicture}
		};
		\pause

		\node (a) at (2,3) {
			\begin{tikzpicture}[scale = 1]
			    \tikzstyle{edge}=[draw,line width = .5pt,-,black!100]
			    \tikzstyle{current}=[draw,circle,fill=black,scale=.5]
			    \tikzstyle{visited}=[draw,circle,fill=white,scale=.5]
			    \draw[edge] (0,0) -- (0,1);
			    \draw[edge] (0,0) -- (1,0);
			    \draw[edge] (0,1) -- (1,0);
			    \draw[edge] (0,1) -- (1,1);
			    \draw[edge] (1,1) -- (1,0);
			    \node (l) at (.5, 1.3) {a};
			    \node (bl) at (0,0) {};
			    \node[visited] (tl) at (0,1) {};
			    \node[current] (br) at (1,0) {};
			    \node (tr) at (1,1) {};;
			\end{tikzpicture}
		};
		\node (b) at (2,0) {
			\begin{tikzpicture}[scale = 1]
			    \tikzstyle{edge}=[draw,line width = .5pt,-,black!100]
			    \tikzstyle{current}=[draw,circle,fill=black,scale=.5]
			    \tikzstyle{visited}=[draw,circle,fill=white,scale=.5]
			    \draw[edge] (0,0) -- (0,1);
			    \draw[edge] (0,0) -- (1,0);
			    \draw[edge] (0,1) -- (1,0);
			    \draw[edge] (0,1) -- (1,1);
			    \draw[edge] (1,1) -- (1,0);
			    \node (l) at (.5, -.3) {b};
			    \node (bl) at (0,0) {};
			    \node[visited] (tl) at (0,1) {};
			    \node (br) at (1,0) {};
			    \node[current] (tr) at (1,1) {};;
			\end{tikzpicture}
		};
		\path[->] (m) edge (a);
		\path[->] (m) edge (b);
		\pause
		\node (c) at (4,3) {
			\begin{tikzpicture}[scale = 1]
			    \tikzstyle{edge}=[draw,line width = .5pt,-,black!100]
			    \tikzstyle{current}=[draw,circle,fill=black,scale=.5]
			    \tikzstyle{visited}=[draw,circle,fill=white,scale=.5]
			    \draw[edge] (0,0) -- (0,1);
			    \draw[edge] (0,0) -- (1,0);
			    \draw[edge] (0,1) -- (1,0);
			    \draw[edge] (0,1) -- (1,1);
			    \draw[edge] (1,1) -- (1,0);
			    \node (l) at (.5, 1.3) {c};
			    \node (bl) at (0,0) {};
			    \node[visited] (tl) at (0,1) {};
			    \node[visited] (br) at (1,0) {};
			    \node[current] (tr) at (1,1) {};;
			\end{tikzpicture}
		};
		\node (d) at (4,0) {
			\begin{tikzpicture}[scale = 1]
			    \tikzstyle{edge}=[draw,line width = .5pt,-,black!100]
			    \tikzstyle{current}=[draw,circle,fill=black,scale=.5]
			    \tikzstyle{visited}=[draw,circle,fill=white,scale=.5]
			    \draw[edge] (0,0) -- (0,1);
			    \draw[edge] (0,0) -- (1,0);
			    \draw[edge] (0,1) -- (1,0);
			    \draw[edge] (0,1) -- (1,1);
			    \draw[edge] (1,1) -- (1,0);
			    \node (l) at (.5, -.3) {d};
			    \node (bl) at (0,0) {};
			    \node[current] (tl) at (0,1) {};
			    \node (br) at (1,0) {};
			    \node[visited] (tr) at (1,1) {};;
			\end{tikzpicture}
		};
		\node (e) at (6,3) {
			\begin{tikzpicture}[scale = 1]
			    \tikzstyle{edge}=[draw,line width = .5pt,-,black!100]
			    \tikzstyle{current}=[draw,circle,fill=black,scale=.5]
			    \tikzstyle{visited}=[draw,circle,fill=white,scale=.5]
			    \draw[edge] (0,0) -- (0,1);
			    \draw[edge] (0,0) -- (1,0);
			    \draw[edge] (0,1) -- (1,0);
			    \draw[edge] (0,1) -- (1,1);
			    \draw[edge] (1,1) -- (1,0);
			    \node (l) at (.5, 1.3) {e};
			    \node (bl) at (0,0) {};
			    \node[current] (tl) at (0,1) {};
			    \node[visited] (br) at (1,0) {};
			    \node[visited] (tr) at (1,1) {};;
			\end{tikzpicture}
		};		
		\path[->] (a) edge[loop above, distance=6mm] (a);
		\path[->] (a) edge (c);
		\path[->] (b) edge[bend left] (d);
		\path[->] (b) edge (e);
		\pause
		\node (f) at (6, 0) {
			\begin{tikzpicture}[scale = 1]
			    \tikzstyle{edge}=[draw,line width = .5pt,-,black!100]
			    \tikzstyle{current}=[draw,circle,fill=black,scale=.5]
			    \tikzstyle{visited}=[draw,circle,fill=white,scale=.5]
			    \draw[edge] (0,0) -- (0,1);
			    \draw[edge] (0,0) -- (1,0);
			    \draw[edge] (0,1) -- (1,0);
			    \draw[edge] (0,1) -- (1,1);
			    \draw[edge] (1,1) -- (1,0);
			    \node (l) at (.5, -.3) {f};
			    \node[current] (bl) at (0,0) {};
			    \node[visited] (tl) at (0,1) {};
			    \node (br) at (1,0) {};
			    \node[visited] (tr) at (1,1) {};;
			\end{tikzpicture}
		};
		\node (done) at (8, 3) {
			\begin{tikzpicture}[scale = 1]
			    \tikzstyle{edge}=[draw,line width = .5pt,-,black!100]
			    \tikzstyle{current}=[draw,circle,fill=black,scale=.5]
			    \tikzstyle{visited}=[draw,circle,fill=white,scale=.5]
			    \draw[edge] (0,0) -- (0,1);
			    \draw[edge] (0,0) -- (1,0);
			    \draw[edge] (0,1) -- (1,0);
			    \draw[edge] (0,1) -- (1,1);
			    \draw[edge] (1,1) -- (1,0);
			    \node (l) at (.5, 1.3) {0};
			    \node[visited] (bl) at (0,0) {};
			    \node[visited] (tl) at (0,1) {};
			    \node[visited] (br) at (1,0) {};
			    \node[visited] (tr) at (1,1) {};;
			\end{tikzpicture}
		};
		\node (g) at (8, 0) {
			\begin{tikzpicture}[scale = 1]
			    \tikzstyle{edge}=[draw,line width = .5pt,-,black!100]
			    \tikzstyle{current}=[draw,circle,fill=black,scale=.5]
			    \tikzstyle{visited}=[draw,circle,fill=white,scale=.5]
			    \draw[edge] (0,0) -- (0,1);
			    \draw[edge] (0,0) -- (1,0);
			    \draw[edge] (0,1) -- (1,0);
			    \draw[edge] (0,1) -- (1,1);
			    \draw[edge] (1,1) -- (1,0);
			    \node (l) at (.5, -.3) {g};
			    \node[visited] (bl) at (0,0) {};
			    \node[current] (tl) at (0,1) {};
			    \node (br) at (1,0) {};
			    \node[visited] (tr) at (1,1) {};;
			\end{tikzpicture}
		};
		\path[->] (c) edge[bend left] (e);
		\path[->] (d) edge (e);
		\path[->] (d) edge[bend left] (b);
		\path[->] (d) edge (f);
		\path[->] (e) edge[bend left] (c);
		\path[->] (e) edge[loop above, distance=6mm] (e);
		\path[->] (f) edge[bend left] (g);
		\path[->] (g) edge[bend left] (f);
		\path[->] (e) edge (done);
		\path[->] (f) edge (done);
		\path[->] (g) edge (done);
	\end{tikzpicture}
\end{center}
\end{frame}

\begin{frame}{A Small Graph}
\small
\begin{align}
\E[t_{cov}] &= 1 + \frac{1}{3}\textrm{a} + \frac{2}{3}\textrm{b} 
\only<2->{= \frac{43}{6}}\nonumber \\
\textrm{a} &= 1 + \frac{1}{3}\textrm{a} + \frac{2}{3}\textrm{c} \nonumber \\
\textrm{b} &= 1 + \frac{1}{2}\textrm{b} + \frac{1}{2}\textrm{e} \nonumber \\
\textrm{c} &= 1 + 1\textrm{e} \nonumber \\
\textrm{d} &= 1 + \frac{1}{3}\textrm{a} + \frac{1}{3}\textrm{e} + \frac{1}{3}\textrm{f} \nonumber \\
\textrm{e} &= 1 + \frac{1}{3}\textrm{c} + \frac{1}{3}\textrm{e} + \frac{1}{3}\dot 0\nonumber \\
\textrm{f} &= 1 + \frac{1}{2}\textrm{g} + \frac{1}{2}\dot 0 \nonumber \\
\textrm{g} &= 1 + \frac{2}{3}\textrm{f} + \frac{1}{3}\dot 0\nonumber
\end{align}
\end{frame}

\section{Expected Cover Time of a Complete Graph with Self-edges}

\begin{frame}{Complete Graph with Self-edges}
Let $X_i$ be the number of steps from $i-1$ to $i$ distinct vertices.
\only<2-> {
\begin{align}
\E[t_{cov}] &= \E[X_1+X_2+X_3+\cdots+X_{n}] \nonumber
\end{align}
}

\only<3-> {$X_i \sim \textrm{Geom}(\frac{n-i+1}{n})$}
\only<4-> {so $\E[X_i] = \frac{n}{n-i+1}$}
\only<5-> {and
\begin{align}
\E[t_{cov}] &= n\left(\frac{1}{n}+\frac{1}{n-1}+\cdots+1\right) \nonumber
\end{align}
}
\end{frame}

\begin{frame}{Coupon Collector}
\centering
A collector receives one of $n$ possible coupons in the mail everyday.
How long until all coupons have been collected?
\bigskip

On average, we need about $n \log n$ days.
\end{frame}

\begin{frame}{Birthday Problem}
\centering
How many people do we need for each birthday (excluding February 29)
to be represented?
\bigskip

On average, we need about 2365 people.
\end{frame}

\section{Expected Cover Time of a General Graph}

\begin{frame}{Matthews Method}
\begin{theorem}
Consider a random walk on an arbitrary connected graph with $n$ vertices. Then
\end{theorem}
\begin{align}
\E[t_{cov}] &\leq t_{hit} \left(1 + \frac{1}{2} + \frac{1}{3} + \cdots + \frac{1}{n-1} \right). \nonumber
\end{align}
\end{frame}

\begin{frame}{Matthews Method Proof}
\only<1-3>{Let $\sigma$ be a uniform permutation of unvisited vertices from (worst-case) vertex $n$.}

\only<2-3>{Let $T_k$ be the first time vertices 
$\sigma_1, \sigma_2, \ldots, \sigma_k$ have all been visited.}
\only<3>{
\begin{align}
\E[t_{cov}] &= \E_n[{T_{n-1}}]  \nonumber \\
&= \E_n[T_1 + (T_2 - T_1) + \cdots + (T_{n-1} - T_{n-2})] . \nonumber
\end{align}
}

\only<4-> {Let $L(k)$ be the final vertex to be visited among 
$\sigma_1, \sigma_2, \ldots, \sigma_k$ before the first time they are
all visited.}
\only<5-> {
\begin{align}
\E_n[T_k - T_{k-1}] &=
\sum_{i=1}^k \E_n[T_k - T_{k-1} | L(k) = \sigma_i]
\pr(L_k = \sigma_i). \nonumber
\only<6->{\\&= 0 +
\E_n[T_k - T_{k-1} | L(k) = \sigma_k]
\pr(L_k = \sigma_k). \nonumber 
}
\only<7->{\\&\leq t_{hit} \frac{1}{k} \nonumber }
\end{align}
}
\end{frame}

\section{Cover Time Distribution of the a Complete Graph with Self-edges}

\begin{frame}{Poisson Distribution}
After $r$ steps of a random walk, let $A_i$ be the probability that
vertex $i$ is unvisited.
\begin{align}
\pr(A_i) = (1-1/n)^r \nonumber
\end{align}
\pause
Let $N_n$ be the number of unvisited vertices.
\begin{align}
\E[N_n] &= n(1-1/n)^r. \nonumber  \\
&=n[(1-1/n)^n]^{r/n} = n e^{r/n} \nonumber
\end{align}
\pause
I promise that 
\begin{align}
N_n/n &\xrightarrow{p} \E[N_n/n] \nonumber
\end{align}

\end{frame}

\begin{frame}{Poisson Distribution}
Let the number of unvisited vertices be $r = n \log n + nx$ (trust me).
\begin{align}
N_n &= ne^{-r/n} = ne^{-\log n - x} = n n^{-1} e^{-x} \rightarrow  e^{-x} \nonumber
\end{align}
\begin{theorem}
If $ne^{-r/n} \rightarrow \lambda \in [0, \infty)$, then the number of unvisited
vertices approaches a Poisson distribution with mean $\lambda$.
\end{theorem}
\end{frame}

\begin{frame}{Poisson Distribution}
Uppertail of a Poisson with mean $\lambda$
\begin{align}
\pr(N_n > 0) &\rightarrow 1 - e^\lambda \nonumber
\end{align}
\pause
The first time $N_n=0$ is $t_{cov}$
\begin{align}
\pr(t_{cov} \leq r) &\rightarrow e^{-e^{-x}} \nonumber \\
\pr(t_{cov} - n \log n\leq nx) &\rightarrow e^{-e^{-x}} \nonumber
\end{align}
\end{frame}

\begin{frame}{Birthday Problem}

\end{frame}

\end{document}

### 2019-05-07 talk.tex
minor

@@
 \frame{\titlepage}
+
+\begin{frame}{Overview}
+\tableofcontents
+\end{frame}
 
@@
 			    \draw[edge] (1,1) -- (1,0);
-			    \node (l) at (.5, 1.1) {$t_{cov}$};
+%			    \node (l) at (.5, 1.1) {$t_{cov}$};
 			    \node (bl) at (0,0) {};
@@
 \textrm{d} &= 1 + \frac{1}{3}\textrm{a} + \frac{1}{3}\textrm{e} + \frac{1}{3}\textrm{f} \nonumber \\
-\textrm{e} &= 1 + \frac{1}{3}\textrm{c} + \frac{1}{3}\textrm{e} + \frac{1}{3}\dot 0\nonumber \\
-\textrm{f} &= 1 + \frac{1}{2}\textrm{g} + \frac{1}{2}\dot 0 \nonumber \\
-\textrm{g} &= 1 + \frac{2}{3}\textrm{f} + \frac{1}{3}\dot 0\nonumber
+\textrm{e} &= 1 + \frac{1}{3}\textrm{c} + \frac{1}{3}\textrm{e} + \frac{1}{3} 0\nonumber \\
+\textrm{f} &= 1 + \frac{1}{2}\textrm{g} + \frac{1}{2} 0 \nonumber \\
+\textrm{g} &= 1 + \frac{2}{3}\textrm{f} + \frac{1}{3} 0\nonumber
 \end{align}
@@
 \begin{frame}{Matthews Method Proof}
-\only<1-3>{Let $\sigma$ be a uniform permutation of unvisited vertices from (worst-case) vertex $n$.}
+Let $\sigma$ be a uniform permutation of unvisited vertices from (worst-case) vertex $n$.
+\pause
 
-\only<2-3>{Let $T_k$ be the first time vertices 
-$\sigma_1, \sigma_2, \ldots, \sigma_k$ have all been visited.}
-\only<3>{
+Let $T_k$ be the first time vertices 
+$\sigma_1, \sigma_2, \ldots, \sigma_k$ have all been visited.
+\pause
 \begin{align}
-\E[t_{cov}] &= \E_n[{T_{n-1}}]  \nonumber \\
+\E[t_{cov}] &\leq \E_n[{T_{n-1}}]  \nonumber \\
 &= \E_n[T_1 + (T_2 - T_1) + \cdots + (T_{n-1} - T_{n-2})] . \nonumber
 \end{align}
-}
 
-\only<4-> {Let $L(k)$ be the final vertex to be visited among 
+\end{frame}
+\begin{frame}{Matthews Method Proof}
+
+Let $L(k)$ be the final vertex to be visited among 
 $\sigma_1, \sigma_2, \ldots, \sigma_k$ before the first time they are
-all visited.}
-\only<5-> {
+all visited.
+\pause
 \begin{align}
@@
 \pr(L_k = \sigma_i). \nonumber
-\only<6->{\\&= 0 +
+\only<3->{\\&= 0 +
 \E_n[T_k - T_{k-1} | L(k) = \sigma_k]
@@
 }
-\only<7->{\\&\leq t_{hit} \frac{1}{k} \nonumber }
+\only<4->{\\&\leq t_{hit} \frac{1}{k} \nonumber }
 \end{align}
-}
 \end{frame}
@@
 \begin{frame}{Poisson Distribution}
-Let the number of unvisited vertices be $r = n \log n + nx$ (trust me).
 \begin{align}
+r &= n \log n + nx \nonumber \\
 N_n &= ne^{-r/n} = ne^{-\log n - x} = n n^{-1} e^{-x} \rightarrow  e^{-x} \nonumber
@@
 \end{theorem}
-\end{frame}
-
-\begin{frame}{Poisson Distribution}
-Uppertail of a Poisson with mean $\lambda$
+\pause
 \begin{align}
-\pr(N_n > 0) &\rightarrow 1 - e^\lambda \nonumber
-\end{align}
-\pause
-The first time $N_n=0$ is $t_{cov}$
-\begin{align}
-\pr(t_{cov} \leq r) &\rightarrow e^{-e^{-x}} \nonumber \\
+\pr(N_n=0) = \pr(t_{cov} \leq r) &\rightarrow e^{-e^{-x}} \nonumber \\
 \pr(t_{cov} - n \log n\leq nx) &\rightarrow e^{-e^{-x}} \nonumber
@@
 \begin{frame}{Birthday Problem}
+What is the probability all birthdays are covered in a town of 1825?
+How about a town of 2190?
+\pause
+\begin{align}
+\pr(t_{cov} \leq 1825) &= \pr \left(\frac{t_{cov} - 2153}{365} \leq
+\frac{328}{365}\right) \nonumber \\
+&\approx e^{-e^{-0.89863}} \approx 0.08576. \nonumber
+\only<3->{
+\\\pr(t_{cov} \leq 2190) &= \pr \left(\frac{t_{cov} - 2153}{365} \leq
+\frac{37}{365}\right) \nonumber \\
+&\approx e^{-e^{-0.10137}} \approx 0.40511 \nonumber
+}
+\end{align}
 
@@
 
+\begin{frame}{Birthday Problem}
+\begin{tikzpicture}[scale=.37]
+\node (graph) at (0,0) {\includegraphics[scale=.1, height=7cm]{birthdays}};
+\node (title) at (1, 10) {Cover Times of the Birthday Problem (1000 trials)};
+\node[rotate=90] (ylabel) at (-13,2) {$\pr(t_{cov} \leq r)$};
+\node (xlabel) at (0,-9) {$r$};
+\end{tikzpicture}
+\end{frame}
+
+\begin{frame}{Thank you!}
+\begin{thebibliography}{9}
+
+\bibitem{AF14}
+	Aldous, D. and J. Fill.
+	2014.
+	\textit{Reversible Markov Chains and Random Walks on Graphs}.
+
+\bibitem{BH94}
+	Blom, G., L. Holst and D. Sandell.
+	\textit{Problems and Snapshots from the World of Probability},
+	Springer Science \& Business Media, 1994.
+
+\bibitem{DS84}
+	Doyle, P. G. and J. L. Snell.
+	1984.
+	\textit{Random Walks and Electric Networks},
+	Mathematical Association of America.
+
+\bibitem{LP08}
+	Levin, D. A. and Y. Peres.
+	2017.
+	\textit{Markov Chains and Mixing Times},
+	Vol. 107,
+	American Mathematical Society.
+
+\end{thebibliography}
+\end{frame}
+
 \end{document}

### 2019-05-08 computation.R
minor edits

@@ -33,7 +33,7 @@ cdf(2190) # Probability all birthdays represented with 2190 people
 cdf(1825) # Probability all birthdays represented with 1825 people
 
 cover_times3 %>% # Graph of birthday cover times
-  ggplot() + theme_classic()+
+  ggplot() + theme_classic() +
   stat_function(fun = cdf, color="blue", alpha=.5, size=2) +
   geom_line(aes(x=cover_times3$cover_times, y=cover_times3$percentile),
             color="red", alpha=.5, size=2) +

### 2019-05-09 paper.tex
minor
minor edits
some of Bill's edits

@@
 Next consider a particular case of coupon collecting called the birthday problem.
-How many people would we need to ensure that every day of the year
-(excluding February 29) is represented as a birthday?
-A lower bound is certainly 365 but there is no upper bound.
+Assuming all 365 days of the year, excluding February 29, are equally likely,
+how many people would we need to ensure each birthday is represented
+by at least one person?
+A lower bound is certainly 365 but it is possible to get an arbitrarily
+large population without covering each birthday.
 
@@
 Then $n$ is the number of vertices $|V(G)|$.
-We say $i\sim j$ for $i$ and $j$ in the vertex set $V(G)$ if $(i,j)$ is in $E(G)$.
+We say $i\sim j$ for $i$ and $j$ in the vertex set $V(G)$ if $(i,j)$ 
+is in $E(G)$.
 Assume that each vertex is accessible from every other vertex.
-That is, there is a set of edges connecting any $x$ to any $y$.
-
-Let $C_{i,j}=C_{j,i}$ be the non-negative weight of the edge between vertices $i$ and $j$.
-We will mostly consider unweighted graphs
-such that $C_{i,j} = 1$ if $i \sim j$ and $C_{i,j} = 0$ otherwise.
+That is, for $x$ and $y$ there exists a path
+$x=v_0 \sim v_1 \sim \cdots \sim v_n = y$.
+
+Let $C_{i,j}=C_{j,i}$ be a non-negative weight assinged to the edge
+between vertices $i$ and $j$.
+We will mostly consider unweighted graphs,
+meaning $C_{i,j} = 1$ if $i \sim j$ and $C_{i,j} = 0$ otherwise.
 
@@
 \end{align}
-In the unweighted case, $C_i$ is the degree of vertex $i$.
+In the unweighted case, $C_i$ is simply the degree of vertex $i$.
 
@@
 
-Let $T_{j}$ be the number of steps until the first visit to $j$.
+Let $T_{j}$ be the number of steps until the first visit to $j$
+after time time $t=0$.
 Formally,
@@
 \end{align}
-Let the hitting time $\hit$ be the maximum expected time between two vertices on $G$.
-Note that $\E_i[T_j] = \E[T_j | X_0 = i]$.
+Let $\E_i[T_j] = \E[T_j | X_0 = i]$.
+This is the expected time of the first visit to $j$ given
+that the random walk started in vertex $i$.
+Then $\E_j[T_j]$ is the return time to $j$.
+Now define the hitting time $\hit$ for the graph
+be the maximum expected time between two vertices on $G$.
+
 Formally, 
@@
 (\cref{sec:structured_graphs} primarily relies on \cite{BH94}.)
-We see that it is always possible to exactly calculate the cover time
-of graph but it is in general very difficult to do so.
+We see that while in principle it is always possible to exactly 
+calculate the cover time
+of graph, it is in general very difficult to do so.
 For the remainder of this section, we investigate
-structured graphs that are exceptions to the rule:
+structured graphs for which exact cover time analysis is tractable:
 the complete graph, line graphs, and simple cycles.
@@
 \begin{align}
-\tcov&= \E[X_1+X_2+X_3+\cdots+X_{n-1}] = \sum_{i=1}^{n-1} \E[X_i] \nonumber
+\tcov&= \E[X_1+X_2+X_3+\cdots+X_{n}] = \sum_{i=1}^{n} \E[X_i] \nonumber
 \end{align}
@@
 The random variable $X_i$ takes value $k$ when $k-1$ steps lead us to
-already visited vertices and the $k^{th}$ step is to a previously unvisited vertex.
+already visited vertices and the $k^{th}$ step is 
+to a previously unvisited vertex.
 Then $X_i$ is certainly geometric and $\E[X_i] = 1/p_i$.
@@
 We now find the probability $p_i$ that 
-we go to a previously unvisited vertex is $(n-i)/(n-1)$.
-This is because there are $n-i$ unvisited vertices and a total of $n-1$ adjacent vertices.
-It follows that $\E[X_i] = (n-1)/(n-i)$.
+we go to a previously unvisited vertex is $(n-i+1)/(n-1)$.
+This is because there are $n-i+1$ unvisited 
+vertices and a total of $n-1$ adjacent vertices.
+It follows that $\E[X_i] = (n-1)/(n-i+1)$.
 Then
 \begin{align}
-\tcov&=   \sum_{i=1}^{n-1} \frac{n-1}{n-i} \nonumber \\
+\tcov&=   \sum_{i=1}^{n} \frac{n-1}{n-i+1} \nonumber \\
 &=  (n-1) \left(\frac{1}{n-1}+\frac{1}{n-2}+\cdots+1\right). \nonumber
@@
 denote the set of vertices we have visited.
-Since the walk is on a line, we can $[a,b]$ for the range
+Since the walk is on a line, we can write $[a,b]$ for the range
 of the walk where $a$ is the smallest 
@@
 \begin{align}
-\tcov &= \E[T_n] = \E[(T_2 - T_1) + (T_3 - T_2) + \cdots + 
+\tcov &= \E_0[T_n] = \E[(T_2 - T_1) + (T_3 - T_2) + \cdots + 
 (T_k - T_{k-1}) + \cdots + (T_n - T_{n-1})] \nonumber
@@
 By a similar argument, $1/\pi_a$ is the expected return time to $a$.
-
-Thus the expected time from $a$ to $b$ and back is
-the expected number of returns to $a$ before we reach $b$ times
-the expected number of steps for each return to $a$.
-The commute time identity follows
+If we condition on reaching $b$ before turning to $a$,
+\begin{align}
+\frac{1}{\pi_a} &= \E_a[T_a] =
+\E_a[T_a|T_b < T_a] \pr(T_b<T_a) +
+\E_a[T_a|T_a < T_b] \pr(T_a<T_b) \nonumber.
+\end{align}
+
+Considering the cases that we either reach $b$ or not before
+returning to $a$,
+\begin{align}
+\E_a[T_b] + \E_b[T_a] &= 
+\E_a[T_a | T_b < T_a] + 
+\E_a[T_a | T_a < T_b] (\frac{1}{\pr(T_b<T_a)} - 1) \nonumber.
+\end{align}
+Observe that $1/\pr(T_b<T_a)-1 = (1-\pr(T_b<T_a))/\pr(T_b<T_a)$, 
+which simplifies to $\pr(T_a<T_b)/\pr(T_b<T_a)$.
+Multiplying by the probability we reach $b$ before returning to $a$,
+\begin{align}
+\E_a[T_a|T_b < T_a] \pr(T_b<T_a) + \E_a[T_a|T_a<T_b] \pr(T_a<T_b)=\frac{1}{\pi_a} \nonumber
+\end{align}
+and the commute identity follows
 \begin{align}
@@
 \frac{37}{365}\right) \nonumber \\
-&\approx e^{-e^{-.10137}} \approx 0.40511 \nonumber
+&\approx e^{-e^{-0.10137}} \approx 0.40511 \nonumber
 \end{align}
@@
 \pr(\cov \leq 1825) &= \pr \left(\frac{\cov - 2153}{365} \leq
-\frac{328}{365}\right) \nonumber \\
-&\approx e^{-e^{-.8.9863}} \approx 0.08576. \nonumber
+\frac{-328}{365}\right) \nonumber \\
+&\approx e^{-e^{-0.89863}} \approx 0.08576. \nonumber
 \end{align}

### 2019-05-09 talk.tex
minor edits
some of Bill's edits

@@
 \DeclareMathOperator{\pr}{\mathrm{P}}		     % probability 
+\DeclareMathOperator{\cov}{t_{cov}}	             % cover time
 
@@
 \author{R. Teal Witter}
+\institute{Middlebury College}
 \date{May 9, 2019}
@@
 			    \draw[edge] (1,1) -- (1,0);
-%			    \node (l) at (.5, 1.1) {$t_{cov}$};
+%			    \node (l) at (.5, 1.1) {$\cov$};
 			    \node (bl) at (0,0) {};
@@
 \begin{align}
-\E[t_{cov}] &= 1 + \frac{1}{3}\textrm{a} + \frac{2}{3}\textrm{b} 
+\E[\cov] &= 1 + \frac{1}{3}\textrm{a} + \frac{2}{3}\textrm{b} 
 \only<2->{= \frac{43}{6}}\nonumber \\
@@
 \begin{align}
-\E[t_{cov}] &= \E[X_1+X_2+X_3+\cdots+X_{n}] \nonumber
+\E[\cov] &= \E[X_1+X_2+X_3+\cdots+X_{n}] \nonumber
 \end{align}
@@
 \begin{align}
-\E[t_{cov}] &= n\left(\frac{1}{n}+\frac{1}{n-1}+\cdots+1\right) \nonumber
+\E[\cov] &= n\left(\frac{1}{n}+\frac{1}{n-1}+\cdots+1\right) \nonumber
 \end{align}
@@
 \begin{align}
-\E[t_{cov}] &\leq t_{hit} \left(1 + \frac{1}{2} + \frac{1}{3} + \cdots + \frac{1}{n-1} \right). \nonumber
+\E[\cov] &\leq t_{hit} \left(1 + \frac{1}{2} + \frac{1}{3} + \cdots + \frac{1}{n-1} \right). \nonumber
 \end{align}
@@
 \begin{align}
-\E[t_{cov}] &\leq \E_n[{T_{n-1}}]  \nonumber \\
-&= \E_n[T_1 + (T_2 - T_1) + \cdots + (T_{n-1} - T_{n-2})] . \nonumber
+\E[\cov] &\leq \E_n[{T_{n-1}}]  \nonumber \\
+&\leq \E_n[T_1 + (T_2 - T_1) + \cdots + (T_{n-1} - T_{n-2})] . \nonumber
 \end{align}
@@
 
-\begin{frame}{Poisson Distribution}
-After $r$ steps of a random walk, let $A_i$ be the probability that
+\begin{frame}{Cover Time Distribution}
+After $r$ steps of a random walk, let $A_i$ be the event that
 vertex $i$ is unvisited.
 \begin{align}
-\pr(A_i) = (1-1/n)^r \nonumber
+\pr(A_i) = \pr(\textrm{not visited in one step})^r = (1-1/n)^r \nonumber
 \end{align}
@@
 \begin{align}
-\E[N_n] &= n(1-1/n)^r. \nonumber  \\
-&=n[(1-1/n)^n]^{r/n} = n e^{r/n} \nonumber
-\end{align}
-\pause
-I promise that 
-\begin{align}
-N_n/n &\xrightarrow{p} \E[N_n/n] \nonumber
+\E[N_n] &= \sum_{i=1}^n \pr(A_i) = n(1-1/n)^r \nonumber  \\
+&=n[(1-1/n)^n]^{r/n} \sim n e^{-r/n} \nonumber
 \end{align}
@@
 
-\begin{frame}{Poisson Distribution}
+\begin{frame}{Cover Time Distribution}
+Introduce $x$ and set $r = n \log n + nx$.
 \begin{align}
-r &= n \log n + nx \nonumber \\
-N_n &= ne^{-r/n} = ne^{-\log n - x} = n n^{-1} e^{-x} \rightarrow  e^{-x} \nonumber
+N_n &\sim ne^{-r/n} = ne^{-\log n - x} = n n^{-1} e^{-x} \rightarrow  e^{-x} \nonumber
 \end{align}
@@
 \begin{align}
-\pr(N_n=0) = \pr(t_{cov} \leq r) &\rightarrow e^{-e^{-x}} \nonumber \\
-\pr(t_{cov} - n \log n\leq nx) &\rightarrow e^{-e^{-x}} \nonumber
+\pr(N_n=0) = \pr(\cov \leq r)
+= \pr(\cov - n \log n\leq nx)
+\rightarrow e^{-e^{-x}} \nonumber
 \end{align}
@@
 \begin{align}
-\pr(t_{cov} \leq 1825) &= \pr \left(\frac{t_{cov} - 2153}{365} \leq
-\frac{328}{365}\right) \nonumber \\
-&\approx e^{-e^{-0.89863}} \approx 0.08576. \nonumber
+\pr(\cov \leq 1825) &= \pr \left(\frac{\cov - 2153}{365} \leq
+\frac{-328}{365}\right) \nonumber \\
+&\approx e^{-e^{-0.89863}} \approx 0.08576 \nonumber
 \only<3->{
-\\\pr(t_{cov} \leq 2190) &= \pr \left(\frac{t_{cov} - 2153}{365} \leq
+\\\pr(\cov \leq 2190) &= \pr \left(\frac{\cov - 2153}{365} \leq
 \frac{37}{365}\right) \nonumber \\
@@
 \node (title) at (1, 10) {Cover Times of the Birthday Problem (1000 trials)};
-\node[rotate=90] (ylabel) at (-13,2) {$\pr(t_{cov} \leq r)$};
+\node[rotate=90] (ylabel) at (-13,2) {$\pr(\cov \leq r)$};
 \node (xlabel) at (0,-9) {$r$};

### 2019-05-11 paper.tex
bill's comments

@@
 grows exponentially with the number of vertices.
-
+\begin{comment}
 \begin{figure}[ht]
@@
 			};
+			\end{comment}
 			\begin{comment}
@@
 			\end{comment}
+			\begin{comment}
 			\path[->] (m) edge (a);
@@
 \end{figure}
+\end{comment}
+
+\begin{figure}[ht]
+	\centering
+		\begin{tikzpicture} [
+            > = stealth, % arrow head style
+            shorten > = 1pt, % don't touch arrow head to node
+            %auto,
+            node distance = 3cm, % distance between nodes
+            semithick % line style
+        ]
+
+			\tikzstyle{edge}=[draw,line width = .5pt,-,black!100]
+
+			\node (A) at (-1.2,2.5) {
+				\begin{tikzpicture}[scale = 3]
+				    \tikzstyle{edge}=[draw,line width = .5pt,-,black!100]
+				    \tikzstyle{current}=[draw,circle,fill=black,scale=.5]
+				    \tikzstyle{visited}=[draw,circle,fill=white,scale=.5]
+				    \draw[edge] (0,0) -- (0,1);
+				    \draw[edge] (0,0) -- (1,0);
+				    \draw[edge] (0,1) -- (1,0);
+				    \draw[edge] (0,1) -- (1,1);
+				    \draw[edge] (1,1) -- (1,0);
+				    \node (l) at (.5, 1.1) {A};
+				    \node (bl) at (0,0) {};
+				    \node (tl) at (0,1) {};
+				    \node (br) at (1,0) {};
+				    \node[current] (tr) at (1,1) {};
+				\end{tikzpicture}
+			};
+			\node (B) at (2,3.5) {
+				\begin{tikzpicture}[scale = 1]
+				    \tikzstyle{edge}=[draw,line width = .5pt,-,black!100]
+				    \tikzstyle{current}=[draw,circle,fill=black,scale=.5]
+				    \tikzstyle{visited}=[draw,circle,fill=white,scale=.5]
+				    \draw[edge] (0,0) -- (0,1);
+				    \draw[edge] (0,0) -- (1,0);
+				    \draw[edge] (0,1) -- (1,0);
+				    \draw[edge] (0,1) -- (1,1);
+				    \draw[edge] (1,1) -- (1,0);
+				    \node (l) at (.5, 1.3) {B};
+				    \node (bl) at (0,0) {};
+				    \node[current] (tl) at (0,1) {};
+				    \node (br) at (1,0) {};
+				    \node[visited] (tr) at (1,1) {};;
+				\end{tikzpicture}
+			};
+			\node (C) at (2,1) {
+				\begin{tikzpicture}[scale = 1]
+				    \tikzstyle{edge}=[draw,line width = .5pt,-,black!100]
+				    \tikzstyle{current}=[draw,circle,fill=black,scale=.5]
+				    \tikzstyle{visited}=[draw,circle,fill=white,scale=.5]
+				    \draw[edge] (0,0) -- (0,1);
+				    \draw[edge] (0,0) -- (1,0);
+				    \draw[edge] (0,1) -- (1,0);
+				    \draw[edge] (0,1) -- (1,1);
+				    \draw[edge] (1,1) -- (1,0);
+				    \node (l) at (.5, -.3) {C};
+				    \node (bl) at (0,0) {};
+				    \node[visited] (tl) at (0,1) {};
+				    \node (br) at (1,0) {};
+				    \node[current] (tr) at (1,1) {};;
+				\end{tikzpicture}
+			};
+			\node (D) at (4,3.5) {
+				\begin{tikzpicture}[scale = 1]
+				    \tikzstyle{edge}=[draw,line width = .5pt,-,black!100]
+				    \tikzstyle{current}=[draw,circle,fill=black,scale=.5]
+				    \tikzstyle{visited}=[draw,circle,fill=white,scale=.5]
+				    \draw[edge] (0,0) -- (0,1);
+				    \draw[edge] (0,0) -- (1,0);
+				    \draw[edge] (0,1) -- (1,0);
+				    \draw[edge] (0,1) -- (1,1);
+				    \draw[edge] (1,1) -- (1,0);
+				    \node (l) at (.5, 1.3) {D};
+				    \node[current] (bl) at (0,0) {};
+				    \node[visited] (tl) at (0,1) {};
+				    \node (br) at (1,0) {};
+				    \node[visited] (tr) at (1,1) {};;
+				\end{tikzpicture}
+			};
+			\node (E) at (4,1) {
+				\begin{tikzpicture}[scale = 1]
+				    \tikzstyle{edge}=[draw,line width = .5pt,-,black!100]
+				    \tikzstyle{current}=[draw,circle,fill=black,scale=.5]
+				    \tikzstyle{visited}=[draw,circle,fill=white,scale=.5]
+				    \draw[edge] (0,0) -- (0,1);
+				    \draw[edge] (0,0) -- (1,0);
+				    \draw[edge] (0,1) -- (1,0);
+				    \draw[edge] (0,1) -- (1,1);
+				    \draw[edge] (1,1) -- (1,0);
+				    \node (l) at (.5, -.3) {E};
+				    \node (bl) at (0,0) {};
+				    \node[current] (tl) at (0,1) {};
+				    \node[visited] (br) at (1,0) {};
+				    \node[visited] (tr) at (1,1) {};;
+				\end{tikzpicture}
+			};
+			\node (F) at (6,3.5) {
+				\begin{tikzpicture}[scale = 1]
+				    \tikzstyle{edge}=[draw,line width = .5pt,-,black!100]
+				    \tikzstyle{current}=[draw,circle,fill=black,scale=.5]
+				    \tikzstyle{visited}=[draw,circle,fill=white,scale=.5]
+				    \draw[edge] (0,0) -- (0,1);
+				    \draw[edge] (0,0) -- (1,0);
+				    \draw[edge] (0,1) -- (1,0);
+				    \draw[edge] (0,1) -- (1,1);
+				    \draw[edge] (1,1) -- (1,0);
+				    \node (l) at (.5, 1.3) {F};
+				    \node[visited] (bl) at (0,0) {};
+				    \node[current] (tl) at (0,1) {};
+				    \node (br) at (1,0) {};
+				    \node[visited] (tr) at (1,1) {};;
+				\end{tikzpicture}
+			};		
+			\node (G) at (6, 1) {
+				\begin{tikzpicture}[scale = 1]
+				    \tikzstyle{edge}=[draw,line width = .5pt,-,black!100]
+				    \tikzstyle{current}=[draw,circle,fill=black,scale=.5]
+				    \tikzstyle{visited}=[draw,circle,fill=white,scale=.5]
+				    \draw[edge] (0,0) -- (0,1);
+				    \draw[edge] (0,0) -- (1,0);
+				    \draw[edge] (0,1) -- (1,0);
+				    \draw[edge] (0,1) -- (1,1);
+				    \draw[edge] (1,1) -- (1,0);
+				    \node (l) at (.5, -.3) {G};
+				    \node (bl) at (0,0) {};
+				    \node[visited] (tl) at (0,1) {};
+				    \node[visited] (br) at (1,0) {};
+				    \node[current] (tr) at (1,1) {};;
+				\end{tikzpicture}
+			};
+			\node (H) at (9.2, 2.5) {
+				\begin{tikzpicture}[scale = 3]
+				    \tikzstyle{edge}=[draw,line width = .5pt,-,black!100]
+				    \tikzstyle{current}=[draw,circle,fill=black,scale=.5]
+				    \tikzstyle{visited}=[draw,circle,fill=white,scale=.5]
+				    \draw[edge] (0,0) -- (0,1);
+				    \draw[edge] (0,0) -- (1,0);
+				    \draw[edge] (0,1) -- (1,0);
+				    \draw[edge] (0,1) -- (1,1);
+				    \draw[edge] (1,1) -- (1,0);
+				    \node (l) at (.5, 1.1) {H};
+				    \node[visited] (bl) at (0,0) {};
+				    \node[visited] (tl) at (0,1) {};
+				    \node[visited] (br) at (1,0) {};
+				    \node[visited] (tr) at (1,1) {};;
+				\end{tikzpicture}
+			};
+			\path[->] (A) edge (B);
+			\path[<->] (B) edge (C);
+			\path[->] (B) edge (D);
+			\path[->] (B) edge (E);
+			\path[->] (C) edge (E);
+			\path[<->] (D) edge (F);
+			\path[->] (D) edge[bend left, distance=12mm] (H);
+			\path[<->] (E) edge (G);
+			\path[->] (E) edge[bend right, distance=15mm] (H);
+			\path[->] (E) edge[loop above, distance=5mm] (E);
+			\path[->] (F) edge (H);
+			\path[->] (G) edge (H);
+	\end{tikzpicture}
+	\caption{First step analysis applied to a small graph with $n=4$.}\label{fig:example}
+\end{figure}
 
@@
 of equations:
+\begin{comment}
 \begin{align}
@@
 \end{align}
-
-With a little linear algebra, we find that $\tcov = 43/6$.
+\end{comment}
+\begin{align}
+\tcov = &\textrm{A} = 1 + \textrm{B}
+&\textrm{B} = 1 + \frac{1}{2}\textrm{C} + \frac{1}{2}\textrm{D} \nonumber \\
+&\textrm{C} = 1 + \frac{1}{2}\textrm{B} + \frac{1}{2}\textrm{E}
+&\textrm{D} = 1 + \frac{1}{2}\textrm{F} + \frac{1}{2}\textrm{H} \nonumber \\
+&\textrm{E} = 1 + \frac{1}{3}\textrm{E} + \frac{1}{3}\textrm{G} + \frac{1}{3}\textrm{H}
+&\textrm{F} = 1 + \frac{1}{2}\textrm{D} + \frac{1}{2}\textrm{F} \nonumber \\
+&\textrm{G} = 1 + \frac{1}{2}\textrm{E} + \frac{1}{2}\textrm{H}
+&\textrm{H} = 0\nonumber
+\end{align}
+
+With a little linear algebra, we find that $\tcov = 43/5$.
+We leave it as an exercise to the reader to verify that the time
+to visit all vertices from the other starting vertex is $43/6$.
 
@@
 \begin{align}
-\tcov &= \E_0[T_n] = \E[(T_2 - T_1) + (T_3 - T_2) + \cdots + 
+\tcov &= \E[T_n] = \E[(T_2 - T_1) + (T_3 - T_2) + \cdots + 
 (T_k - T_{k-1}) + \cdots + (T_n - T_{n-1})] \nonumber
@@
 
-Considering the cases that we either reach $b$ or not before
-returning to $a$,
+The expected commute time between $a$ and $b$ is the
+expected return time to $a$ given we reach $b$ plus
+the expected return time to $a$ given we do not reach $b$ times
+the number of times we return to $a$ before the success when
+we reach $b$.
+Formally, we write
 \begin{align}
@@
 \begin{proof}
-Without loss of generality, label the vertices $\{1, 2, \dots, n\}$.
-We may assume that the walk started at vertex $n$.
+Without loss of generality, label the vertices $\{1, 2, \dots, n\}$
+such that $n$ is the vertex from which it takes the most steps to cover
+the remaining vertices.
 Let $\sigma$ be a uniform permutation of the unvisited $n-1$ vertices.
@@
 \tcov &= \E_n[{T_{n-1}}]  \nonumber \\
-&= \E_n[T_1 + (T_2 - T_1) + \cdots + 
+&\leq \E_n[T_1 + (T_2 - T_1) + \cdots + 
 (T_k - T_{k-1}) + \cdots + (T_{n-1} - T_{n-2})] . \nonumber
@@
 for $A \subseteq V(G)$.
-When the hitting time is large between any two vertices in $A$,
-the time to visit all of $A$ is a good lower bound on the cover time
-of $V(G)$.
+The Matthews lower bound will always hold.
+However, we can tighten the bound by picking $A$ such
+that the hitting time is large between any pair of vertices.
+We use large in a relative sense and 
+offer an illustrative example in \cref{sec:binary}.
 
@@
 \end{align}
-Note that effective resistance adds in series so $\Rxy = i$ where $i$
+Note that resistance adds in series so 
+effective resistance is just the sum of the resistances along a path.
+Then $\Rxy = i$ where $i$
 is the length of the single path between $x$ and $y$.
@@
 \tcov &\leq 2(n-1)k\left(1 + \frac{1}{2} + \cdots + \frac{1}{n} \right) \nonumber \\
-&\approx (2 - \frac{2}{n}) \cdot n k \log n \approx (2 - \frac{2}{n}) n k \log 2^{k+1} -1 \nonumber \\
-&\approx (2  + o(1)) \cdot n k^2 \log 2 \nonumber
+&\sim (2 - \frac{2}{n}) \cdot n k \log n 
+\sim(2 - \frac{2}{n}) n k \log 2^{k+1} -1 \nonumber \\
+&\sim(2  + o(1)) \cdot n k^2 \log 2 \nonumber
 \end{align}
@@
 \tcov &\geq 2 (n-1)(k-h+1)\left(1 + \frac{1}{2} + \cdots + \frac{1}{2^h -1} \right) \nonumber \\
-&\approx (2 + o(1)) \cdot n (k-h) h \log 2 \nonumber.
+&\geq (2 + o(1)) \cdot n (k-h) h \log 2 \nonumber.
 \end{align}
@@
 We now consider $\Rxy$ the effective resistance between vertices $x$ and $y$.
+Recall that $C$ is the sum of the conductances of every vertex in our graph.
 
@@
 
-The expected time of this particular path on the original graph is certainly less than
-or equal to the cover time. That is,
+The expected time of this particular path on the original graph is certainly 
+greater than or equal to the cover time. That is,
 \begin{align}
@@
 That is, $\I_m = 1$ if vertex $m$ is unvisited 0 otherwise.
-We already know $\E[N_n]$ so we want to find $\E[N_n^2]$,
+We first find $\E[N_n^2]$
 \begin{align}
@@
 \end{align}
-
 The second equality holds since we distribute terms.
 The third equality holds since the mean of an indicator for event $A_m$
-is the probability of $A_m$.
-Putting both terms together, we find the variance
+is the probability of $A_m$ and both events must occur for
+us to have a nonzero term.
+Then we find $\E[N_n]^2$
+\begin{align}
+\E[N_n]^2 &= \E \left[ \left(\sum_{m=1}^n \I_m \right)
+\left( \sum_{k=1}^n \I_k \right) \right] =
+\sum_{1 \leq k, m \leq n} \pr(A_k) \pr(A_m).
+\nonumber
+\end{align}
+
+Putting both together, we find the variance
 \begin{align}
@@
 
-Thus we conclude that $N_n/n \rightarrow \E[N_n/n] = e^{-c}$ in probability.
+Thus we conclude that $N_n/n \rightarrow e^{-c}$.
 
@@
 \begin{align}
-ne^{-r/n} &= n e ^{- \log n - x} \nonumber \\
-&= n e^{- \log n} e^ {- x} = e^{-x}.\nonumber
+ne^{-r/n} &= n e ^{- \log n - x} = n n ^{-1} e^ {- x} = e^{-x}.\nonumber
 \end{align}
@@
 \begin{align}
-\pr(\cov \leq r) &\rightarrow e^{-e^{-x}} \nonumber \\
-\pr(\cov - n \log n\leq nx) &\rightarrow e^{-e^{-x}}. \label{eqn:dist}
+P(N_n=0) = \pr(\cov \leq r) = \pr(\cov - n \log n\leq nx) 
+&\rightarrow e^{-e^{-x}}. \label{eqn:dist}
 \end{align}

### 2019-05-14 paper.tex
final proofread

@@
 The cover time of a graph is the number of steps a 
-discrete random walk takes to visit vertex at least once.
+discrete random walk takes to visit every vertex at least once.
 We begin by investigating the cover time of small and structured graphs but
@@
 A lower bound is certainly 365 but it is possible to get an arbitrarily
-large population without covering each birthday.
+large population without `covering' every birthday.
 
@@
 
-Define the weight of vertex $i$ 
+Define the weight of vertex $i$ as
 \begin{align}
@@
 that the random walk started in vertex $i$.
-Then $\E_j[T_j]$ is the return time to $j$.
+Then $\E_j[T_j]$ is the return time to $j$
+since $t$ is strictly positive.
 Now define the hitting time $\hit$ for the graph
 be the maximum expected time between two vertices on $G$.
-
 Formally, 
@@
 as $1/ C_{x,y}$.
+(We will soon justify the electrical network interpretation of
+a random walk using Ohm's Law.)
 
@@
 \end{align}
-Then $\pi \pr = \pi$ where $\pr$ is the matrix of transition probabilities.
-It follows that $\pi$ is indeed the stationary distribution of $(X_t)$.
+In the language of Markov Chains,
+$\pi \pr = \pi$ where $\pr$ is the matrix of transition probabilities.
+It follows that $\pi$ is the stationary distribution of $(X_t)$.
+The takeaway for the reader unfamiliar with Markov Chains is that
+$\pi_y$ is indeed the long term proportion of time spent in vertex $y$.
 
@@
 Set the voltage to be 1 at $a$ and 0 at $b$.
-We may think of voltage as the probability we get to $a$ before $b$.
-Probabilistically, of course $v_a = 1$ and $v_b=0$.
+We may think of voltage as the probability we get to $a$ before $b$:
+$v_a$ the probability we get to $a$ before $b$ from $a$
+is 1 and $v_b$ the probability we get to $a$ before $b$ from $b$ is 0.
 The voltage at every vertex $x$ in  $V(G) \textbackslash \{a,b\}$
@@
 
-The current between two vertices is the product of the
+By Ohm's Law, the current between two vertices is the product of the
 difference in their voltages and the conductance of their edge.
@@
 Kirchoff's Current Law says that the sum of current on any vertex is 0.
-Probabilistically, of course every time we enter a vertex we must also leave it.
+Probabilistically: every time we enter a vertex we must also leave it.
 Using Kirchoff's Current Law and the definition of current,
@@
 We can verify that $v_x = \sum_y \pr_{x,y} v_y$
-using first step analysis on the probability of reaching $a$ before $b$.
+using total probability on the likelihood of reaching $a$ before $b$ from $x$.
 
@@
 \cref{sec:bounds} deals with the large or unstructured graphs 
-for which we must use bounds.
+for which we must use cover time bounds.
 We begin by establishing an important identity between
@@
 
-Up until \cref{sec:dist}, we have only considered the expected cover time.
-We now delve into the distribution of the cover time of a complete graph.
+Up until \cref{sec:dist}, we only consider expected cover time.
+We now delve into the distribution of the cover time on a complete graph with self-edges.
 We draw on \cite{Du11} and find that the cover time variable approaches a Poisson
@@
 \cref{fig:example} shows our small graph and the first step analysis
-for the random walk $(X_t)$ started from the top left vertex.
+for the random walk $(X_t)$ started from the top right vertex.
 The black circle indicates the current vertex of the random walk
@@
 We leave it as an exercise to the reader to verify that the time
-to visit all vertices from the other starting vertex is $43/6$.
+to visit all vertices from the other (i.e. symmetrically distinct) vertex is $43/6$.
 
@@
 The rest of this section deals with particularly symmetric graphs
-for which it is possible to find a solution for an arbitrary $n$.
+for which it is possible to find a solution for an arbitrary number of vertices $n$.
 However, we must rely on cover time bounds for the vast majority of cases.
@@
 	\end{tikzpicture}
-    \caption{The complete graph with six vertices (and ten edges).}\label{fig:complete}	
+    \caption{The complete graph with six vertices (and 15 edges).}\label{fig:complete}	
 \end{figure}
@@
 Let $X_i$ be the random variable that represents the number of steps to go
-from $i-1$ to $i$ unique vertices (excluding the current vertex).
+from $i-1$ to $i$ distinct vertices.
 
@@
 It follows that $\E[X_i] = (n-1)/(n-i+1)$.
+Since we start at a vertex, $\E[X_i]=0$.
 Then
 \begin{align}
-\tcov&=   \sum_{i=1}^{n} \frac{n-1}{n-i+1} \nonumber \\
+\tcov&=   0+\sum_{i=2}^{n} \frac{n-1}{n-i+1} \nonumber \\
 &=  (n-1) \left(\frac{1}{n-1}+\frac{1}{n-2}+\cdots+1\right). \nonumber
@@
 whereas before we had to leave our current vertex at each step.
-That is, we can stay in the same vertex (if the collector receives the same coupon
-two days in a row).
+That is, we can now stay in the same vertex (provided the collector 
+receives the same coupon two days in a row).
 We apply our approach to the complete graph and substitute the $r$ possible coupons
@@
 \begin{align}
-\tcov&=  r \left(\frac{1}{r}+\frac{1}{r-1}+\cdots+1\right). \nonumber
+\tcov&=  r \left(\frac{1}{r-1}+\frac{1}{r-2}+\cdots+1\right). \nonumber
 \end{align}
@@
 
-We will begin by considering the time $(X_t)$ takes to
+We will begin by considering the time a random walk takes to
 visit either one of the endpoints from vertex $i$.
-
 From $X_t=i$, we move with equal probability to $i+1$
@@
 \begin{align}
-\E_{i}[T_{i+1}] &= 1 + \frac{1}{2}(\E_{i-1}[T_i]+\E_i[T_{i+1}]) \nonumber \\
+\E_{i}[T_{i+1}] &= 1 + \frac{1}{2}(\E_{i-1}[T_i]+\E_i[T_{i+1}]) +\frac{1}{2}0 \nonumber \\
  &= 2 + \E_{i-1}[T_{i}]. \nonumber
@@
 \begin{align}
-\E_0[T_N] &= 1 + 3 + \cdots + 2i - 1 + \cdots + 2(N-1) -1 \nonumber \\
-&= N^2 \nonumber
-\end{align}
-
-Then, by \cref{thm:line}, for the random walk from state $i$ on the line graph,
+\E_0[T_N] &= 1 + 3 + \cdots + 2i - 1 + \cdots + 2(N-1) -1 = N^2 \nonumber
+\end{align}
+
+By \cref{thm:line}, for the random walk from state $i$ on the line graph,
 \begin{align}
@@
 The cover time $\tcov$ of the simple cycle is the expected number of steps 
-until we visit $n$ distinct integers.
+until we visit $n$ distinct integers on the number line.
 
@@
 
-\section{Bounds}\label{sec:bounds}
+\section{Cover Time Bounds}\label{sec:bounds}
 
@@
 Recall $\sum_y P_{a,y} v_y$ is the probability we reach $a$ before $b$
-so 1 minus that is the probability we reach $b$ before returning to $a$.
+so the complement is the probability we reach $b$ before returning to $a$.
 
@@
 
-Recall that $\pi_a$ is the probability that $(X_t) = a$.
+Recall that $\pi_a$ is the stationary probability that $(X_t) = a$.
 By a similar argument, $1/\pi_a$ is the expected return time to $a$.
@@
 The expected commute time between $a$ and $b$ is the
-expected return time to $a$ given we reach $b$ plus
-the expected return time to $a$ given we do not reach $b$ times
-the number of times we return to $a$ before the success when
-we reach $b$.
-Formally, we write
+random sum expectation,
 \begin{align}
@@
 \begin{align}
-E_a[T_b] + E_b[T_a] = \frac{1}{\pi_a}\frac{1}{\pr_a(T_b < T_a)} = \Reff C.
+E_a[T_b] + E_b[T_a] = \frac{1}{\pi_a \pr_a(T_b < T_a)} = \Reff C.
 \label{eqn:commute}
@@
 Our goal is to bound the cover time in terms of the hitting time.
-
 Consider the first term of the sum.
@@
 we visit $\sigma_k$ last is $1/k$.
-Formally, $P(L_k = \sigma_k) = 1/k$.
-
-Finally, we find the expected time between $T_{k-1}$ and $T_{k}$
+Now we find the expected time between $T_{k-1}$ and $T_{k}$
 given that last vertex we visit is $\sigma_k$.
@@
 However, we can tighten the bound by picking $A$ such
-that the hitting time is large between any pair of vertices.
-We use large in a relative sense and 
+that the hitting time is large between any pair of vertices in $A$.
+We use `large' in a relative sense and 
 offer an illustrative example in \cref{sec:binary}.
@@
 \begin{proof}
-Without loss of generality, label the vertices $\{1, 2, \ldots, n\}$.
-We may assume that the walk started at vertex $x \in A$.
+Without loss of generality, label the vertices $\{1, 2, \ldots, x\}$
+such that $x=|A|$ and vertex $x$ is the vertex from which it takes the
+most steps to cover the other vertices.
 Let $\sigma$ be a uniform permutation of the vertices in $A$.
@@
 Our goal is to bound the cover time in terms of $\tmina$.
-
 Consider the first term of the sum.
@@
 Since $\sigma$ is a random permutation, $P(L_k = \sigma_k) = 1/k$.
-
 Now find the expected time between $T_{k-1}$ and $T_{k}$
@@
 We now use the Matthews Lower Bound.
-Choose a set $A \subseteq V(G)$ with a large hitting time between any
+We want to choose a set $A \subseteq V(G)$ with a large hitting time between any
 pair of vertices.
@@
 
-A spanning tree $\T$ is a subset of a graph with all edges
+A spanning tree $\T$ is a subset of a graph with all vertices 
 in $V(G)$ connected by the minimum number of edges in $E(G)$.
@@
 a Poisson distribution with mean $c$.
-We can use this to intuite our conclusion: the proportion of visits to each vertex
+We can use this to intuite our latest result: the proportion of visits to each vertex
 approaches $e^{-c}$.
@@
 
-Define $p_m(r,n)$ as the probability that exactly $m$ vertices are unvisited
+Define $p_m(r,n)$ as the probability that exactly $m$ of $n$ vertices are unvisited
 when $r$ steps have been taken.
@@
 {n \choose m} \left(1-\frac{m}{n}\right)^r &\leq \frac{n^m}{m!} e^{mr/n} 
-= \frac{(n e^{r/n})^m} {m!} \nonumber \\
-&\rightarrow \frac{\lambda ^m} {m!}. \nonumber
+= \frac{(n e^{r/n})^m} {m!}
+\rightarrow \frac{\lambda ^m} {m!}. \label{eqn:up_lim}
 \end{align}
@@
 We use the Taylor series of $\log(1-t)$ for $0 \leq t \leq 1/2$
-to bound the rest.
-Notice that
+to bound the rest,
 \begin{align}
@@
 &= m \log n + r \log\left(1-\frac{m}{n}\right) \nonumber \\
-& \geq m \log n - r\frac{m}{n} - r\frac{m}{n^2}. \nonumber
+& \geq m \log n - r\frac{m}{n} - r\left(\frac{m}{n}\right)^2. \nonumber
 \end{align}
@@
 \log n + -r/n &= \log \lambda + o(n) \nonumber \\
-r &= n \log n - n \log \lambda + o(n). \nonumber
+r &= n \log n - n \log \lambda +  o(n)n. \nonumber
 \end{align}
@@
 \begin{align}
-\frac{rm}{n} &=m \log n - m \log \lambda + o(n)\frac{m}{n} \nonumber \\
+\frac{rm}{n} &=m \log n - m \log \lambda +  o(n)m \nonumber \\
  m \log n - \frac{rm}{n}&\rightarrow m \log \lambda \nonumber
@@
 Now we put the pieces back together.
-The most recent limit implies \cref{eqn:lim}.
+The most recent limit and \cref{eqn:up_lim} imply \cref{eqn:lim}.
 By \cref{eqn:lim} and \cref{eqn:p0},
@@
 since $m$ is fixed and $(n-m)e^{r/(n-m)} \rightarrow \lambda$.
-Finally, the most recent limit and the equation of $p_m(r,n)$ imply
+Finally, the most recent limit and the equation for $p_m(r,n)$ imply
 \begin{align}
@@
 \end{align}
-$N_n$ approaches a Poisson distribution with mean $\lambda$ as claimed.
+Thus $N_n$ approaches a Poisson distribution with mean $\lambda$ as claimed.
 
@@
 
-\subsection{The Birthday Problem}\label{sec:birthday}
+\subsection{Birthday Problem}\label{sec:birthday}
 Consider a complete graph (with self-edges) and 365 vertices.
@@
 that all birthdays are represented in populations of 
-size $r=2190$ and $r=1825$, respectively.
+size $r=1825$ and $r=2190$, respectively.
 The number of vertices $n$ is 365 so $n\log n = 2153$.
@@
 \begin{align}
+\pr(\cov \leq 1825) &= \pr \left(\frac{\cov - 2153}{365} \leq
+\frac{-328}{365}\right) \nonumber \\
+&\approx e^{-e^{-0.89863}} \approx 0.08576 \nonumber
+\end{align}
+but
+\begin{align}
 \pr(\cov \leq 2190) &= \pr \left(\frac{\cov - 2153}{365} \leq
 \frac{37}{365}\right) \nonumber \\
-&\approx e^{-e^{-0.10137}} \approx 0.40511 \nonumber
-\end{align}
-but 
-\begin{align}
-\pr(\cov \leq 1825) &= \pr \left(\frac{\cov - 2153}{365} \leq
-\frac{-328}{365}\right) \nonumber \\
-&\approx e^{-e^{-0.89863}} \approx 0.08576. \nonumber
+&\approx e^{-e^{-0.10137}} \approx 0.40511. \nonumber
 \end{align}
@@
 
-\newpage
+\clearpage
 \bibliography{mybib}{}

### 2019-09-01 paper.tex
integrate Bill's feedback

@@
 
-Let $C_{i,j}=C_{j,i}$ be a non-negative weight assinged to the edge
+Let $C_{i,j}=C_{j,i}$ be a non-negative weight assigned to the edge
 between vertices $i$ and $j$.
@@
 \end{align}
-Let the cover time variable $\cov$ be the first time all vertices have been
+Let the cover time random variable $\cov$ be the first time all vertices have been
 visited by the random walk $(X_t)$.
@@
 between vertices $x$ and $y$, $C_x$ is the sum
-of all $C_{x,y}$ where $x \sim y$, and the probability $\pr_{x,y}$
+of all $C_{x,y}$ where $x$ and $y$ share an edge,
+and the probability $\pr_{x,y}$
 that we go from $x$ to $y$ is $C_{x,y}/C_x$.
@@
 walk on the vertices of our graph.
-Define the proportion $\pi_x$ of time we spend in $x$
-as $C_x/C$ where $C=\sum_y C_y$.
-
-We verify that $\pi$ is the stationary distribution
-of $(X_t)$.
-To begin,
+Define $\pi_x$ as $C_x/C$ where $C=\sum_y C_y$.
+We will show that $\pi$, the vector of $\pi_i$ where $i$
+runs over all vertices, is the stationary distribution of the random walk.
+Then $\pi_x$ must be the long term proportion of time spent in vertex $x$.
+We first use our definitions to show that $\pi$ satisfies detailed balance,
 \begin{align}
@@
 \end{align}
-Dividing by $C$ gives $\pi_x \pr_{x,y} = \pi_y \pr_{y,x}$.
-(So $\pi$ satisfies detailed balance.)
+Dividing by $C$ gives $\pi_x \pr_{x,y} = \pi_y \pr_{y,x}$,
+or detailed balance.
+We next use detailed balance to show that $\pi$ is the stationary distribution.
 Summing over $x$,
 \begin{align}
-\sum_x \pi_x \pr_{x,y} = \pi_y . \nonumber
-\end{align}
-In the language of Markov Chains,
-$\pi \pr = \pi$ where $\pr$ is the matrix of transition probabilities.
-It follows that $\pi$ is the stationary distribution of $(X_t)$.
-The takeaway for the reader unfamiliar with Markov Chains is that
-$\pi_y$ is indeed the long term proportion of time spent in vertex $y$.
+\sum_x \pi_x \pr_{x,y} = \sum_x \pi_y \pr_{y,x} = \pi_y \sum_x \pr_{y,x}
+= \pi_y . \nonumber
+\end{align}
+(We get the last equality because we know that when leaving vertex $y$
+the random walk goes with probability 1 to some vertex $x$.)
+We rely on \cite{Ka14} to show that 
+$\pi \pr = \pi$ where $\pr$ is the matrix of transition probabilities
+and how it follows that $\pi$ is the stationary distribution of the random walk.
+Then $\pi_x$ is indeed the long term proportion of time spent in vertex $x$.
 
 We now introduce voltage, current, and effective resistance.
-Consider $a$ and $b$ in $V(G)$.
-Set the voltage to be 1 at $a$ and 0 at $b$.
-We may think of voltage as the probability we get to $a$ before $b$:
-$v_a$ the probability we get to $a$ before $b$ from $a$
-is 1 and $v_b$ the probability we get to $a$ before $b$ from $b$ is 0.
-The voltage at every vertex $x$ in  $V(G) \textbackslash \{a,b\}$
-is determined by the boundary values (at $a$ and $b$).
+Consider arbitrary $a$ and $b$ in $V(G)$.
+This is equivalent to setting the voltage to be 1 at $a$ and 0 at $b$.
+We may think of voltage $v_x$ as the probability starting
+from $a$ we get to $x$ before $b$.
+(We have not proved this yet but we will by the end of this subsection.)
+With this interpretation
+it makes sense that $v_a$, the probability we get to $a$ before $b$, is 1
+(we are already at $a$) 
+and $v_b$, the probability we get to $b$ before $a$, is 0
+(we are again already in $a$).
+We do not prove this but
+the voltage at every vertex $x$ in  $V(G) \textbackslash \{a,b\}$
+is determined by the boundary values at $a$ and $b$.
 
@@
 Kirchoff's Current Law says that the sum of current on any vertex is 0.
-Probabilistically: every time we enter a vertex we must also leave it.
+Probabilistically, every time we enter a vertex we must also leave it.
 Using Kirchoff's Current Law and the definition of current,
-we justify the probabilistic interpretation of voltage
+we justify the probabilistic interpretation of voltage as follows
 \begin{align}
@@
 \end{align}
-We can verify that $v_x = \sum_y \pr_{x,y} v_y$
+It follows that $v_x = \sum_y \pr_{x,y} v_y$
 using total probability on the likelihood of reaching $a$ before $b$ from $x$.
@@
 
-We begin in \cref{sec:small_example}.
-(\cref{sec:structured_graphs} primarily relies on \cite{BH94}.)
+\cref{sec:structured_graphs} primarily relies on \cite{BH94}.
 We see that while in principle it is always possible to exactly 
@@
 We now delve into the distribution of the cover time on a complete graph with self-edges.
-We draw on \cite{Du11} and find that the cover time variable approaches a Poisson
-distribution.
+We draw on \cite{Du11} and find that the cover time random variable
+approaches a Poisson distribution as the number of vertices goes to infinity.
 In \cref{sec:birthday}, we apply \cref{sec:complete_dist} to the birthday problem.
@@
 \subsection{Small Example}\label{sec:small_example}
-In general, it is always possible to find the exact cover time
+In principle, it is always possible to find the exact cover time
 of a graph using first step analysis.
@@
 vertex and $2^{n-1}$ possible combinations of visited and unvisited vertices
-for each one.
+for each other one.
 Of course, some cases are inaccessible by a random walk.
@@
 Note that a complete graph with $n$ vertices has ${n \choose 2}$ edges.
+(We exclude self-edges.)
 
@@
 It follows that $\E[X_i] = (n-1)/(n-i+1)$.
-Since we start at a vertex, $\E[X_i]=0$.
+Since we start at a vertex, $\E[X_1]=0$.
 Then
@@
 \end{align}
-
-Another more subtle application of the cover time on a complete graph
-is the cover time on an $n$-star.
 
@@
 
+Another more subtle application of the cover time on a complete graph
+is the cover time on an $n$-star.
 An $n$-star is a graph with one central vertex and $n-1$ adjacent vertices each with a single
@@
 In particular, we have already seen that $e_0=e_N=0$ and it
-naturally follows that $e_1=e_{N_1}$.
+naturally follows that $e_1=e_{N-1}$.
 We use these observations to find $e_1$:
@@
 \cref{thm:line} follows from \cref{eq:line} and the observation that any
-line graph can be shifted so that the left endpoint
+line graph with $N+1$ vertices can be relabeled so that the left endpoint
 is at $0$ and the right endpoint is at $N$.
@@
 \end{align}
-
 where $\E_{i}[T_{i+1}]$ is the expected time from state $i$ to $i+1$.
@@
 \subsection{Commute Time Identity} \label{sec:commute}
-\cite{DS84} We use the electrical network analysis in \cref{sec:electric} to 
+The commute time between vertices $a$ and $b$ is the expected 
+number of steps for a random walk starting in $a$ to visit $b$
+and then return to $a$.
+Following \cite{DS84}, we use the electrical network analysis in \cref{sec:electric} to 
 prove the commute time identity so we may use it to help us bound
@@
 the expected time from $n$ to $\sigma_1$ is less than or equal to $\hit$.
-Formally for $s$ an arbitrary state such that $1\leq s \leq n-1$,
+Formally, for $s$ an arbitrary state such that $1\leq s \leq n-1$,
 $\E_n[T_1] = \E_n[T_s] \leq \hit$.
@@
 	\end{tikzpicture}
-	\caption{A binary tree with $k=3$ and $n=15$.}\label{fig:binary}
+	\caption{A binary tree with $k=3$ has $n=15$.}\label{fig:binary}
 \end{figure}
 
-\cite{LP17}
-Consider an unweighted binary tree as in \cref{fig:binary} with a single root $\rho$.
+Following \cite{LP17},
+consider an unweighted, balanced binary tree as in \cref{fig:binary}
+with a single root $\rho$ and $k$ levels.
 A vertex has two children if it is distance less than $k$
-from the root and no children if it is a leaf (distance $k$ from the root).
+from the root and no children if it is a leaf at distance $k$ from the root.
 There are $n = 1 + 2 + 4 + \cdots + 2^k = 2^{k+1} - 1$ vertices.
@@
 Then $\Rxy = i$ where $i$
-is the length of the single path between $x$ and $y$.
+is the length of the unique path between $x$ and $y$.
 
@@
 \subsection{Spanning Tree Argument}\label{sec:spanning}
-\cite{AF14}
-We introduce the concept of a spanning tree to create
+Following \cite{AF14}, 
+we introduce the concept of a spanning tree to create
 another upper bound for the cover time of a random walk.
@@
 
-A spanning tree $\T$ is a subset of a graph with all vertices 
-in $V(G)$ connected by the minimum number of edges in $E(G)$.
-\cref{fig:span} is an example where the bold edges indicate the edges in $E(\T)$
+A tree is a connected graph with no cycles (i.e. there is exactly one path
+between every pair of points.)
+A spanning tree $\T$ for a connected graph $G$ is a tree with $V(\T) = V(G)$
+and $E(\T) \leq E(G)$.
+\cref{fig:span} shows an example spanning tree
+where the bold edges indicate the edges in $E(\T)$
 and the light edges indicate the edges in $E(G)$ but not $E(\T)$.
-For the connected graphs we consider, the minimum number of edges
-needed to connect all vertices is $n-1$.
-Formally, $V(\T) = V(G)$ and $E(\T) \subseteq E(G)$
-such that $|E(\T)| = n-1$ and $\T$ is connected.
+A consequence of the definition is that 
+$|E(\T)| = n-1$.
 
@@
 \end{align}
-The second equality holds since we distribute terms.
-The third equality holds since the mean of an indicator for event $A_m$
-is the probability of $A_m$ and both events must occur for
-us to have a nonzero term.
+The second equality holds because we distribute terms.
+The third equality holds because $\I_m \I_k = \I_{m \cap k}$
+and the expectation of an indicator random variable is the event's probability.
 Then we find $\E[N_n]^2$
@@
 &= \sum_{1 \leq k, m \leq n} \pr(A_k \cap A_m) - P(A_k)P(A_m) \nonumber \\
-&= n(n-1) \{ \pr(A_k \cap A_m) - P(A_k)P(A_m) \} + 
-n \{ \pr(A_k \cap A_m) - P(A_k)P(A_m) \} \nonumber \\
-&= n(n-1) \{ (1-2/n)^r - (1-1/n)^{2r} \} + 
-n \{ (1-1/n)^r  - (1-1/n)^{2r} \}. \nonumber
+&= n(n-1) \left[ \pr(A_k \cap A_m) - P(A_k)P(A_m) \right] + 
+n \left[ \pr(A_k \cap A_m) - P(A_k)P(A_m) \right] \nonumber \\
+&= n(n-1) \left[ (1-2/n)^r - (1-1/n)^{2r} \right] + 
+n \left[ (1-1/n)^r  - (1-1/n)^{2r} \right]. \nonumber
 \end{align}
@@
 
-Thus we conclude that $N_n/n \rightarrow e^{-c}$.
+Thus we conclude that $N_n/n$ converges in probability to $e^{-c}$.
 
@@
 a Poisson distribution with mean $c$.
-We can use this to intuite our latest result: the proportion of visits to each vertex
+We can use this to intuite our latest result: the proportion of unvisited vertices
 approaches $e^{-c}$.
@@
 \begin{proof}
-Observe that the probability that there are $k$ unvisited vertices is
+Observe that the chance a particular set of $k$ vertices are unvisited is
 \begin{align}
@@
 
-If we consider the locations of the unvisited vertices,
+If we consider the location of the $m$ unvisited vertices,
+and multiply probability that those $m$ vertices are unvisited
+and the rest are visited,
 \begin{align}
@@
 \left( \frac{n^m}{n^m} \right) \nonumber\\
-&\geq n^m (1 - \frac{m}{n})^r (1- \frac{m}{n})^m  \frac{1}{m!}. \nonumber
+&\geq n^m \left(1 - \frac{m}{n}\right)^r \left(1- \frac{m}{n}\right)^m
+\frac{1}{m!}. \nonumber
 \end{align}
@@
 and $1/m!$ is constant.
-We use the Taylor series of $\log(1-t)$ for $0 \leq t \leq 1/2$
-to bound the rest,
+We use the Taylor series to bound the rest.
+(The following equality is valid for $-1 \leq t \leq 1$
+but we only need $0 \leq t \leq 1$ because $m/n \rightarrow 0$
+and $m,n$ are counts of vertices with $m\leq n$.)
+We apply
 \begin{align}
@@
 \end{align}
-and so we have
+to
 \begin{align}
@@
 
-We use our assumption that $ne^{r/n} \rightarrow \lambda$
+We use our assumption that $ne^{-r/n} \rightarrow \lambda$
 to solve for $r$
 \begin{align}
-e^{\log n + -r/n} &\rightarrow e^{\log \lambda} \nonumber\\
-\log n + -r/n &= \log \lambda + o(n) \nonumber \\
-r &= n \log n - n \log \lambda +  o(n)n. \nonumber
-\end{align}
+ne^{-r/n} &\rightarrow \lambda \nonumber\\
+\log n - \frac{r}{n} &\rightarrow \log \lambda \nonumber\\
+\frac{(n\log n - n\log\lambda) - r}{n} &\rightarrow 0 \nonumber
+\end{align}
+then
+\begin{align}
+r = (n\log n - n \log \lambda) + o(n) \nonumber.
+\end{align}
+%\begin{align}
+%e^{\log n + -r/n} &\rightarrow e^{\log \lambda} \nonumber\\
+%\log n + -r/n &= \log \lambda + o(n) \nonumber \\
+%r &= n \log n - n \log \lambda +  o(n)n. \nonumber
+%\end{align}
 Since $r (m/n)^2 \rightarrow 0$ and
@@
 \begin{align}
-p_0(r,n) \rightarrow \sum_{k=0}^\infty \lambda^k /k! = e^{-\lambda}. \nonumber
+p_0(r,n) \rightarrow \sum_{k=0}^\infty (-1)^k \lambda^k /k! = e^{-\lambda}. \nonumber
 \end{align}
@@
 of the random walk visit all $n$ vertices
-and $ne^{-r/n} \rightarrow e^{-x}$ as the assumption of \cref{thm:pois},
+and $ne^{-r/n} \rightarrow e^{-x}$ as the assumption of \cref{thm:pois}
+(with $e^x$ in the role of $\lambda$),
 \begin{align}
@@
 \node (graph) at (0,0) {\includegraphics[scale=.25, height=10cm]{birthdays}};
-\node (title) at (1, 10) {Cover Times of the Birthday Problem (1000 trials)};
-\node[rotate=90] (ylabel) at (-13,2) {$\pr(\cov \leq r)$};
+\node (title) at (1, 12) {Cover Times of the Birthday Problem (1000 trials)};
+\node[rotate=90] (ylabel) at (-15,2) {$\pr(\cov \leq r)$};
 \node (xlabel) at (0,-9) {$r$};
 \end{tikzpicture}
-\caption{The cumulative distribution of the birthday problem.
-The red line denotes the empirical distribution from 1000 trials.
-The blue line denotes the distribution from \cref{eqn:dist}.}\label{fig:birthday}
+\caption{The cumulative distribution of the birthday problem. The red line denotes the
+empirical distribution from 1000 trials. The blue line denotes the distribution from
+\cref{eqn:dist}. (Our code to generate the figure appears in 
+\cref{app:birthday}.)}\label{fig:birthday}
 \end{figure}
@@
 \newpage
-\begin{appendices}
-\subsection{Birthday Problem}\label{app:birthday}
+\section{Appendix}
+\subsection{Birthday Problem R Code}\label{app:birthday}
 \lstinputlisting{computation.R}
-\end{appendices}
 

### 2019-09-01 computation.R

@@ -1,5 +1,4 @@
 # R. Teal Witter
-# Math 710 Spring 2019
 # Cover Time of Birthdays
 library(tidyverse)
 library(ggplot2)
@@ -12,29 +11,54 @@ for (i in 1:trials) {
   birthdays <- 1:n # Unvisited birthdays
   # Count number of people until every birthday is covered
   while (length(birthdays) > 0) {
-    birthday <- sample(1:n, 1, replace=TRUE)      # Uniform birthdays
-    birthdays <- birthdays[birthdays != birthday] # Remove birthday
-    x <- x+1                                      # Count steps
+    # Uniform birthdays
+    birthday <- sample(1:n, 1, replace=TRUE)      
+    # Remove birthday
+    birthdays <- birthdays[birthdays != birthday] 
+    # Count steps
+    x <- x+1                                      
   }
   cover_times[i] <- x
 }
 
-cover_times2 <- data.frame(cover_times)
-
-cover_times3 <- cover_times2%>% # Append percentiles
+# Append percentiles
+cover_times_analyzed <- data.frame(cover_times) %>% 
   mutate(percentile=ecdf(cover_times)(cover_times))
 
-cdf <- function(r) { # Analytical result of cover time CDF
+# Analytical result of cover time CDF
+cdf <- function(r) {
   x <- (r - n * log(n)) / n
   return (exp(-exp(-x)))
 }
 
+# Start of x axis
+start_x <- min(cover_times_analyzed$cover_times)
+
 cdf(2190) # Probability all birthdays represented with 2190 people
 cdf(1825) # Probability all birthdays represented with 1825 people
 
-cover_times3 %>% # Graph of birthday cover times
+# Figure of birthday cover times
+cover_times_analyzed %>% 
   ggplot() + theme_classic() +
+  # Analytical cover times
   stat_function(fun = cdf, color="blue", alpha=.5, size=2) +
-  geom_line(aes(x=cover_times3$cover_times, y=cover_times3$percentile),
+  # Empirical cover times
+  geom_line(aes(x=cover_times_analyzed$cover_times,
+                y=cover_times_analyzed$percentile),
             color="red", alpha=.5, size=2) +
-  ylab("") + xlab("")
+  ylab("") + xlab("") +
+  # Dashed lines to indicate points of interest
+  geom_segment(aes(x=2190, y=cdf(2190), xend=2190, yend=0),
+               linetype="dashed") +
[…]

### 2019-09-02 paper.tex
minor edit
clarify theorem assumption

@@
 \subsection{Complete Graph}\label{sec:complete_dist}
-\cite{Du11}
-We consider the distribution of the cover time of a random walk
-on the complete graph with self edges.
+Following \cite{Du11},
+we consider the distribution of the cover time of a random walk
+on the complete graph with self-edges.
 Call $r$ the number of steps since we began the random walk.
@@
 \begin{theorem}\label{thm:pois}
-If $ne^{-r/n} \rightarrow \lambda \in [0, \infty)$, then the number of unvisited
+If $ne^{-r/n} \rightarrow \lambda \in [0, \infty)$ as $n \rightarrow \infty$,
+then the number of unvisited
 vertices approaches a Poisson distribution with mean $\lambda$.
